### 2018-02-06 main.tex

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage{times}

\usepackage[
backend=biber,
style=apa,
citestyle=authoryear 
]{biblatex}

\usepackage{csquotes}

\addbibresource{}

\title{\vspace{.5cm }
  \LARGE{If you see something, say something (to others):} \\
  \large{The effects of socially-contingent corrections on spreads of misinformation on social networks}
  }

\author{Hyunjin Song}
\date{\today}

%\doublespacing

\begin{document}

\maketitle

\section{Introduction}

Research on political misinformation and motivated reasoning generally suggests that fact-checking (or corrections) on false information has only limited effects due to inherent tendency of humans to directionally process the (politically) relevant information. However, a small line of research suggests that the effect of political fact-checking on social network may be socially contingent.

\section{Theoretical framework}

\end{document}

### 2018-02-06 main.tex
Update on Overleaf.

@@
 
-\addbibresource{}
+\addbibresource{abm_misinformation_lit.bib}
 
@@
 
+There has been an explosive interest among public and academics alike on how people directionally process and maintain factually false (or at least factually dubious) information (\cite{LEWANDOWSKY_JARMC2017}), and further, how corrections to such false information is received under various scenarios (\cites{LEWANDOWSKY_JARMC2017}; \cites{thorson_2016}).
 Research on political misinformation and motivated reasoning generally suggests that fact-checking (or corrections) on false information has only limited effects due to inherent tendency of humans to directionally process the (politically) relevant information.

### 2018-02-06 main.tex
Update on Overleaf.

--- 2018-02-06 main.tex
@@
-\documentclass[12pt]{article}
+\documentclass[man, 12pt, a4paper]{apa6}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage[margin=2.5cm]{geometry}
-\usepackage{setspace}
+\usepackage[american]{babel}
+\usepackage{csquotes}
+\usepackage{amsmath}
+\usepackage{microtype}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{url}
 \usepackage{times}
 
-\usepackage[
-backend=biber,
-style=apa,
-citestyle=authoryear 
-]{biblatex}
+% Biblatex
+\usepackage[backend = biber, style = apa, citestyle = authoryear, uniquename = false, natbib = true]{biblatex}
+\usepackage[colorlinks=true]{hyperref}
 
-\usepackage{csquotes}
+\addbibresource{abm_misinformation_lit.bib}
+\DeclareLanguageMapping{american}{american-apa}
 
-\addbibresource{}
-
-\title{\vspace{.5cm }
-  \LARGE{If you see something, say something (to others):} \\
-  \large{The effects of socially-contingent corrections on spreads of misinformation on social networks}
-  }
+\title{If you see something, say something (to others): A spread of misinformation and socially-contingent corrections within social networks}
+\shorttitle{The socially-contingent corrections}
 
 \author{Hyunjin Song}
-\date{\today}
 
-%\doublespacing
+\affiliation{Department of Communication, University of Vienna, Austria}
+
+\abstract{Citizens across the worlds are experiencing major changes in their news environment with the development of digital media.
+As the citizens' news consumption is increasingly driven by online sources, the propagation of misinformation and so-called "fake news" on those platforms become an increasing concern for the public and policy makers.
+Yet what we know about the spread of misinformation and fake news is largely based on anecdotal evidence despite increasing academic interest and research effort on this topic.
+Our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, combining a macro supply factor and individuals' cognitive basis of adopting misinformation into a more integrated, dynamic system model perspective.
+We review individuals' cognitive basis of adopting such misinformation, focusing motivated reasoning and accuracy motivations, as well as the trust in media, as the underlying basis of exposure to and adoption of misinformation at an individual level.
+Next, adopting a well-known class of an epidemic model of virus infection and recovery, we combine micro and macro dynamics into comprehensive, integrated model of misinformation diffusion on social networks.
+Relying on Agent-based simulations, we further explore various boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.}
+
+%\keywords{}
+\authornote{Draft in progress. Please do not cite without permission. Please direct any questions and inquires to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
 
@@
 \maketitle
+Citizens across the worlds are experiencing major changes in their news environment with the development of digital media.
+One of the most dramatic changes in the news environment involves the role social networking sites (SNS) such as Facebook and Twitter play as news outlets.
+As the citizens' news consumption is increasingly driven by online sources, the propagation of misinformation and so-called "fake news" on those platforms become an increasing concern for the public and policy makers.
+There are abundant, yet still sketchy, evidence of viral spread of misinformation and "fake news" that potentially affecting millions of citizens across the globe.
+Yet what we know about the spread of misinformation and fake news is largely based on anecdotal evidence despite increasing academic interest and research effort on this topic.
+Our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, combining a macro supply factor and individuals' cognitive basis of adopting misinformation into a more integrated, dynamic system model perspective.
+Following Allcott and Gentzkow's (2017) definition, we define misinformation and fake news as "distorted signals uncorrelated with the truth" (p.
+212).
+Based on this definition, we further discuss the supply logic of misinformation and "fake news" at the system-level.
+Next, we review individuals' cognitive basis of adopting such misinformation, focusing motivated reasoning and accuracy motivations, as well as the trust in media, as the underlying basis of exposure to and adoption of misinformation at an individual level.
+Lastly, adopting a well-known class of an epidemic model of virus infection and recovery, we combine micro and macro dynamics into comprehensive, integrated model of misinformation diffusion on social networks.
+Relying on Agent-based simulations, we further explore various boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.
 
-\section{Introduction}
-
-Research on political misinformation and motivated reasoning generally suggests that fact-checking (or corrections) on false information has only limited effects due to inherent tendency of humans to directionally process the (politically) relevant information.
+There has been an explosive interest among public and academics alike on how people directionally process and maintain factually false (or at least factually dubious) information \parencite{LEWANDOWSKY_JARMC2017, garrett2016driving}.
+Further, these studies have generated a valuable insights of how corrections to such false information is received under various scenarios \parencite{LEWANDOWSKY_JARMC2017, thorson_2016}.
+Largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework, a general consensus among research on political misinformation is that fact-checking messages on false information (or corrections thereof) have only limited effects due to inherent tendency of humans to directionally process (politically) relevant information \parencite{thorson_2016}.
+Yet a small body of literature suggests more complex pictures, suggesting that citizens can indeed adhere factual information despite of partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013}.
 However, a small line of research suggests that the effect of political fact-checking on social network may be socially contingent.
@@
 
+\printbibliography
 \end{document}

### 2018-02-06 main.tex
Update on Overleaf.

--- 2018-02-06 main.tex
@@
-\documentclass[12pt]{article}
+\documentclass[man, 12pt, a4paper]{apa6}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage[margin=2.5cm]{geometry}
-\usepackage{setspace}
+\usepackage[american]{babel}
+\usepackage{csquotes}
+\usepackage{amsmath}
+\usepackage{microtype}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{url}
 \usepackage{times}
 
-\usepackage[
-backend=biber,
-style=apa,
-citestyle=authoryear 
-]{biblatex}
-
-\usepackage{csquotes}
-
-\addbibresource{}
-
-\title{\vspace{.5cm }
-  \LARGE{If you see something, say something (to others):} \\
-  \large{The effects of socially-contingent corrections on spreads of misinformation on social networks}
+%% You can pass in your own texcount params, e.g. -chinese to turn on Chinese mode, or -char to do a character count instead (which does NOT include spaces!)
+%%% http://app.uio.no/ifi/texcount/documentation.html
+\newcommand{\detailtexcount}{%
+  \immediate\write18{texcount -merge -sum -incbib -dir \jobname.tex > \jobname.wcdetail }%
+  \verbatiminput{\jobname.wcdetail}%
 }
 
+\newcommand{\quickwordcount}{%
+  \immediate\write18{texcount -1 -sum -merge \jobname.tex > \jobname-words.sum }%
+  \input{\jobname-words.sum} words%
+}
+
+\newcommand{\quickcharcount}{%
+  \immediate\write18{texcount -1 -sum -merge -char \jobname.tex > \jobname-chars.sum }%
+  \input{\jobname-chars.sum} characters (not including spaces)%
+}
+
+% Biblatex
+\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,uniquename=false]{biblatex}
+\usepackage[colorlinks=true]{hyperref}
+
+\addbibresource{abm_misinformation_lit.bib}
+\DeclareLanguageMapping{american}{american-apa}
+
+\title{If you see something, say something (to others): A spread of misinformation and socially-contingent corrections within social networks}
+\shorttitle{The socially-contingent corrections}
+
 \author{Hyunjin Song}
-\date{\today}
 
-%\doublespacing
+\affiliation{Department of Communication, University of Vienna, Austria}
+
+\abstract{As the citizens' news consumption is increasingly driven by online sources, the propagation of misinformation and so-called \enquote{fake news} on those platforms become an increasing concern for the public and policy makers.
+Yet what we know about the spread of misinformation and fake news is largely based on anecdotal evidence despite increasing academic interest and research effort on this topic.
+Our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, combining a macro social contextual factor and individuals' cognitive basis of adopting misinformation into a more integrated, dynamic system model perspective.
+We first review existing evidence concerning individuals' cognitive basis of adopting such misinformation, focusing motivated reasoning and accuracy motivations, and social context of which exposure to misinformation and its corrections are received.
+Next, adopting a well-known class of an epidemic model of virus infection and recovery, we combine this micro and macro dynamics into comprehensive, integrated model of misinformation diffusion on social networks, focusing on the distinction between simple vs.
+complex contagion.
+Relying on Agent-based simulations, we further explore various boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.}
+
+\authornote{Hyunjin (Jin) Song is currently an assistant professor ("Universitätsassistent, post-doc") in the Department of Communication at the University of Vienna, and also a member of the Vienna Computational Communication Science Lab.}
+
+\note{Word count: \quickwordcount \\
+      \textbf{Draft in progress. Please do not cite without permission.} Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
 
 \begin{document}
+\maketitle
+Citizens across the worlds are experiencing major changes in their news environment with the development of digital media.
+One of the most dramatic changes in the news environment involves the role social networking sites (SNS) such as Facebook and Twitter play as a primary source of news outlets.
+Not only citizens' news consumption is increasingly driven by online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination by sharing news contents in social media \parencite[e.g.,][]{weeks2013dissemination}.
 
-\maketitle
+Along with these trends, the propagation of rumors, misinformation, and so-called \enquote{Fake news} on those platforms become an increasing concern for the public and policy makers \parencite{allcott2017social}.
+There are abundant, yet still fragmentary, evidence of viral spreads of unsubstantiated, often factually dubious (mis)information and "fake news" that potentially affecting millions of citizens across the globe, as evidenced in recent 2016 U.S.
+presidential election \parencite{guess2018selective, giglietto2016fakes, allcott2017social} and in Brexit votes \parencite{nyt_2017}.
+While neither the wide circulation of factually dubious information nor individuals' ressentiments towards corrective messages that are attitudinally incongruent to their priors are not new, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{Fake news} -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social,LEWANDOWSKY_JARMC2017}.
+Despite growing interest and continued research effort to better understand the nature and exact mechanisms of such a propagation, what we know about the spread of misinformation and fake news on online social networks is yet largely based on limited evidence due to its complex nature of the problem.
 
-\section{Introduction}
+Relatedly, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive and affective mechanisms \parencite{LEWANDOWSKY_JARMC2017, garrett2016driving, weeks2015emotions}.
+These studies have generated a valuable insights of how individuals maintain false beliefs, and how corrections to such false beliefs is received and processed under various scenarios \parencite{LEWANDOWSKY_JARMC2017, thorson_2016}.
+A mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that fact-checking messages on false information (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process (politically) relevant information \parencite{thorson_2016, nyhan2010corrections, taber2006}.
+Yet at the same time, studies also find that, under certain situations, citizens \emph{indeed} can adhere factual information based on correction messages in spite of partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013, weeks2015emotions}.
 
-Research on political misinformation and motivated reasoning generally suggests that fact-checking (or corrections) on false information has only limited effects due to inherent tendency of humans to directionally process the (politically) relevant information.
-However, a small line of research suggests that the effect of political fact-checking on social network may be socially contingent.
+Against this backdrop, our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, focusing on one's \emph{social} contexts in which such exposure to (mis)information and corrective messages are received and processed.
+We argue while \emph{exposure} to (mis)information is likely to follow a simple contagion process, \emph{changes} in one's beliefs regarding such (mis)information -- which ultimately \emph{the} goal of corrective messages -- is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where such changes require multiple sources of affirmation and reinforcement compared to simple contagion process.
+As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, and we argue that vast of prior studies have not considered this possibility to date \parencite[for a notable exception, see][]{margolin2017}.
+
+In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking messages.
+We advance our dynamic system model perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which an exposure to misinformation and corrections are received.
+Based on a well-known class of an epidemic model of virus infection and recovery, we propose an integrated model of misinformation diffusion and socially-contingent corrections on social networks, with a special focus on the differences between simple contagion of misinformation and complex contagion of corrections.
+Relying on Agent-based simulations, we further explore various boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.
 
@@
 
+Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define misinformation and fake news as \enquote{distorted signals uncorrelated with the truth} (p.
+212).
+Based on this definition, we ....
+
+\printbibliography
 \end{document}

### 2018-02-06 manuscript_1.0.tex
Update on Overleaf.

--- 2018-02-06 main.tex
@@
 We argue while \emph{exposure} to (mis)information is likely to follow a simple contagion process, \emph{changes} in one's beliefs regarding such (mis)information -- which ultimately \emph{the} goal of corrective messages -- is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where such changes require multiple sources of affirmation and reinforcement compared to simple contagion process.
-As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, and we argue that vast of prior studies have not considered this possibility to date \parencite[for a notable exception, see][]{margolin2017}.
+As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, and we argue that vast of prior studies have not considered this possibility to date \parencite[yet for a notable exception, see][]{margolin2017}.
 
 In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking messages.
-We advance our dynamic system model perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which an exposure to misinformation and corrections are received.
+We advance our dynamic system perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which an exposure to misinformation and corrections are received.
 Based on a well-known class of an epidemic model of virus infection and recovery, we propose an integrated model of misinformation diffusion and socially-contingent corrections on social networks, with a special focus on the differences between simple contagion of misinformation and complex contagion of corrections.
-Relying on Agent-based simulations, we further explore various boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.
+Relying on Agent-based simulations, we further explore boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.
 

### 2018-02-07 manuscript_1.0.tex
Update on Overleaf.
cleanup

@@
+% declare documents and packages
 \documentclass[man, 12pt, a4paper]{apa6}
@@
 \usepackage{times}
+\usepackage{endnotes}
+% this command put all footnotes to endnote at the end of the paper
+\let\footnote\endnote
 
-%% You can pass in your own texcount params, e.g. -chinese to turn on Chinese mode, or -char to do a character count instead (which does NOT include spaces!)
-%%% http://app.uio.no/ifi/texcount/documentation.html
+% for word counts
 \newcommand{\detailtexcount}{%
@@
 }
-
 \newcommand{\quickwordcount}{%
@@
 }
-
 \newcommand{\quickcharcount}{%
@@
 \usepackage[colorlinks=true]{hyperref}
+\usepackage{xcolor}
+\hypersetup{
+    colorlinks,
+    linkcolor={red!50!black},
+    citecolor={blue!50!black},
+    urlcolor={blue!80!black}
+}
 
@@
 \title{If you see something, say something (to others): A spread of misinformation and socially-contingent corrections within social networks}
-\shorttitle{The socially-contingent corrections}
+\shorttitle{Socially-contingent corrections}
 
@@
 \abstract{As the citizens' news consumption is increasingly driven by online sources, the propagation of misinformation and so-called \enquote{fake news} on those platforms become an increasing concern for the public and policy makers.
-Yet what we know about the spread of misinformation and fake news is largely based on anecdotal evidence despite increasing academic interest and research effort on this topic.
 Our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, combining a macro social contextual factor and individuals' cognitive basis of adopting misinformation into a more integrated, dynamic system model perspective.
-We first review existing evidence concerning individuals' cognitive basis of adopting such misinformation, focusing motivated reasoning and accuracy motivations, and social context of which exposure to misinformation and its corrections are received.
-Next, adopting a well-known class of an epidemic model of virus infection and recovery, we combine this micro and macro dynamics into comprehensive, integrated model of misinformation diffusion on social networks, focusing on the distinction between simple vs.
-complex contagion.
+We first review existing evidence concerning individuals' cognitive basis of adopting such misinformation, and social context of which exposure to misinformation and its corrections are received.
+Next, adopting a well-known class of an epidemic model of virus infection and recovery, we combine this micro and macro dynamics into comprehensive, integrated model of misinformation diffusion on social networks.
+We do so by focusing on the distinction between simple contagion of misinformation vs.
+complex contagion of adopting corrective messages.
 Relying on Agent-based simulations, we further explore various boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.}
@@
 \note{Word count: \quickwordcount \\
-      \textbf{Draft in progress. Please do not cite without permission.} Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
+	  Draft date: \today \\
+      \textbf{Draft in progress. Please do not cite without permission.} \\
+      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
 
@@
 \maketitle
-Citizens across the worlds are experiencing major changes in their news environment with the development of digital media.
-One of the most dramatic changes in the news environment involves the role social networking sites (SNS) such as Facebook and Twitter play as a primary source of news outlets.
-Not only citizens' news consumption is increasingly driven by online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination by sharing news contents in social media \parencite[e.g.,][]{weeks2013dissemination}.
+	Citizens across the worlds are experiencing major changes in their news environments with the development of digital media.
+One of the most dramatic changes in the news environment in recent decades involves the role social networking sites (SNS) such as Facebook and Twitter play as a primary source of news outlets.
+Not only citizens' news consumptions are increasingly driven by such online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination on those platforms by sharing news contents with their peers \parencite[e.g.,][]{weeks2013dissemination, lee2017people}.
 
-Along with these trends, the propagation of rumors, misinformation, and so-called \enquote{Fake news} on those platforms become an increasing concern for the public and policy makers \parencite{allcott2017social}.
-There are abundant, yet still fragmentary, evidence of viral spreads of unsubstantiated, often factually dubious (mis)information and "fake news" that potentially affecting millions of citizens across the globe, as evidenced in recent 2016 U.S.
+	An effective deliberation among public is regarded as a keystone of thriving democracies, and modern political systems squarely depend  on  informed  decisions of citizens in that regard \parencite{carpini1996, stromback2005search}.
+Yet, a propagation of rumors, misinformation, and so-called \enquote{Fake news} on those platforms becomes an increasing concern for the public and policy makers alike \parencite{allcott2017social}.
+There are abundant, yet still fragmentary, evidence of viral spreads of unsubstantiated, often factually dubious (mis)information that potentially affecting millions of citizens across the globe -- as evidenced in recent 2016 U.S.
 presidential election \parencite{guess2018selective, giglietto2016fakes, allcott2017social} and in Brexit votes \parencite{nyt_2017}.
-While neither the wide circulation of factually dubious information nor individuals' ressentiments towards corrective messages that are attitudinally incongruent to their priors are not new, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{Fake news} -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social,LEWANDOWSKY_JARMC2017}.
-Despite growing interest and continued research effort to better understand the nature and exact mechanisms of such a propagation, what we know about the spread of misinformation and fake news on online social networks is yet largely based on limited evidence due to its complex nature of the problem.
+While a wide circulation of factually dubious information is not entirely new to politics, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{Fake news} phenomenon -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social, LEWANDOWSKY_JARMC2017}.
+Either based on unsubstantiated rumors or based on factually wrong beliefs, many of the misinformed behave differently than those who are accurately informed \parencite{kuklinski2000misinformation,Garrett_Weeks_2013}.
+They often disagree about basic facts about many political and public issues \parencite[e.g.,][]{nisbet2015partisan}, and continue to believe and rely on such false information when evaluating political matters \parencite{nyhan2010corrections,thorson_2016}.
 
-Relatedly, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive and affective mechanisms \parencite{LEWANDOWSKY_JARMC2017, garrett2016driving, weeks2015emotions}.
-These studies have generated a valuable insights of how individuals maintain false beliefs, and how corrections to such false beliefs is received and processed under various scenarios \parencite{LEWANDOWSKY_JARMC2017, thorson_2016}.
-A mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that fact-checking messages on false information (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process (politically) relevant information \parencite{thorson_2016, nyhan2010corrections, taber2006}.
-Yet at the same time, studies also find that, under certain situations, citizens \emph{indeed} can adhere factual information based on correction messages in spite of partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013, weeks2015emotions}.
+	Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive and affective mechanisms \parencite{LEWANDOWSKY_JARMC2017, Lewandowsky_2012PSPI, kuklinski2000misinformation, garrett2016driving, weeks2015emotions}.
+These studies have generated a valuable insights of how individuals maintain false beliefs, and how corrections to such false beliefs are received and processed under various scenarios \parencite{LEWANDOWSKY_JARMC2017, thorson_2016}.
+However, despite growing interest and continued research effort to better understand the nature and its exact mechanism, what we know about the spread of misinformation and fake news on online social networks is largely based on limited evidence due to its complex nature of the problem.
 
-Against this backdrop, our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, focusing on one's \emph{social} contexts in which such exposure to (mis)information and corrective messages are received and processed.
-We argue while \emph{exposure} to (mis)information is likely to follow a simple contagion process, \emph{changes} in one's beliefs regarding such (mis)information -- which ultimately \emph{the} goal of corrective messages -- is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where such changes require multiple sources of affirmation and reinforcement compared to simple contagion process.
-As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, and we argue that vast of prior studies have not considered this possibility to date \parencite[yet for a notable exception, see][]{margolin2017}.
+	Against this backdrop, our goal in this contribution is to offer a more systematic assessment of underlying mechanisms of misinformation spreading and its correction, focusing on one's \emph{social contexts} in which such (mis)information and corrective messages are received and processed.
+We argue that while \emph{exposure} to (mis)information is likely to follow a simple contagion process, \emph{changes} in one's beliefs regarding such (mis)information -- which ultimately \emph{the} goal of corrective messages -- is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where such changes require multiple sources of affirmation and reinforcement compared to simple contagion process.
+As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, yet the vast majority of prior studies have not considered this possibility to date \parencite{margolin2017}.
 
-In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking messages.
+	In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking (i.e., corrective) messages.
 We advance our dynamic system perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which an exposure to misinformation and corrections are received.
@@
 
-\section{Theoretical framework}
+\section{A Psychology of Fake News, Misperceptions, and Corrections}
 
-Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define misinformation and fake news as \enquote{distorted signals uncorrelated with the truth} (p.
+     Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define \emph{Fake news} as \enquote{distorted signals uncorrelated with the truth} (p.
 212).
-Based on this definition, we ....
+This encompasses several related concepts, such as misinformation, rumors, and disinformation.
+Literature on this topic generally maintain loosely defined, but at the same time highly interrelated, definitions of those related terms.
+For instance, (political) rumors are often defined as \enquote{unsubstantiated claims about candidates and issues that are often false} \parencite[p.
+401]{weeks2014electoral}.
+Similarly, misinformation (or misperceptions) are defined as factual information (or beliefs) \enquote{that are false or contradict the best available evidence in the public domain} \parencite[p.
+128]{flynn2017nature}.
+In relation to this, \emph{dis}information campaigns often denote organized, strategic efforts that trying to sway public opinion using rumors and misinformation \parencite{Garrett2017distraction, Lewandowsky_2012PSPI}.
+Understood in this way, fake news often exclude unintentional reporting mistakes, parodies and satires, or unverifiable conspiracy theories \parencite{allcott2017social}.
+While term \emph{fake news} often than not additionally entail specific pseudo-journalistic styles that mimic legitimate news sources to intentionally deceiving audiences \parencite{jana_sophie_fn}, we use term \enquote{fake news} somewhat loosely, denoting any type of misinformation -- information that is not supported by best-available evidence -- that is deliberatively circulated among publics.\footnote{	Often, the term \emph{fake news} is used as derogatory, rhetorical label to attack political opponents.
+While such use of the term as a \emph{label} is an important conceptual dimension to consider, this aspects of \emph{fake news} is beyond the scope of this manuscript.
+See \citeauthor{jana_sophie_fn} (\citeyear{jana_sophie_fn}) instead for a detailed conceptualization involving this distinction.}
+
+      Literature on misinformation and its persistence often converges to the observation that publics' exposure to and acceptance of misinformation are largely driven by one's motivated consistency needs.
+That is, people are more often than not likely to be disproportionately drawn by information that conforms to their partisan priors \parencite{guess2018selective, weeks2014electoral}, and also more likely to accept and endorse such messages \parencite{kunda1990,nyhan2010corrections}.
+A mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that citizens tend to evaluate attitudinally congruent information as more convincing and valid \emph{regardless of its truth-value}, while inconsistent information is likely to be perceived as weak and therefore likely to be rejected \parencite{taber2006,weeks2015emotions}.
+Therefore, it is perhaps not surprising to find that most of the prior studies based on motivated reasoning framework document that fact-checking messages (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process (politically) relevant information \parencite{thorson_2016, taber2006,flynn2017nature}.
+Or worse, often such corrective messages may backfire \parencite[i.e., more likely to increase than lower the endorsement of false beliefs:][]{nyhan2010corrections}.
+
+      Another line of studies focusing on an individual-level cognitive processing and memory suggests that while attitudinally-congruent misinformation creates automatic and strong affective responses (therefore more easily remembered and readily available in their memory), corrections rarely produce such responses, and therefore requires more resources to recall and incorporate into relevant judgments \parencite{thorson_2016, Lewandowsky_2012PSPI}.
+Also, since misinformations tend to form a coherent mental model of an relevant event based on their partisan schema or based on stereotypes \parencite[e.g.,][]{garrett2013undermining}, people tend to fill any gaps caused by corrections (that invalidates some parts of the mental model) with flawed but attitudinally congruent (mis)information available in memory \parencite{Lewandowsky_2012PSPI}, especially when correction messages does not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}.
+Studies also find that this effect is much likely when initial misinformation is more readily accessible due to fluency bias in one's cognitive processing \parencite{lazer2017combating, Lewandowsky_2012PSPI}, when individuals can generate (counter-arguing) reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}, and most importantly, \emph{even when they remember such information is factually incorrect} \parencite{Lewandowsky_2012PSPI}.
+Due to asymmetrical nature in one's cognitive processing fluency, people have to rely on more deliberative process to recall attitudinally inconsistent correction messages (which requires significant  resources), whereas misinformation is more easily processed and automatically activated.
+Therefore, even in the face of corrections, the effect of misperceptions linger and continue to exert influence on subsequent judgments via spontaneous (i.e., automatic) affective process \parencite[e.g.,][]{thorson_2016}.
+
+      However, other studies also find that, under certain situations, citizens \emph{indeed} can adhere factual information based on correction messages despite of their perpetual partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013, weeks2015emotions}.
+Notably, \citeauthor{Wood2018}'s (\citeyear{Wood2018}) series of experiments document that
 
 \printbibliography
+\newpage
+\begingroup
+\parindent 0pt
+\parskip 2ex
+\def\enotesize{\normalsize}
+\theendnotes
+\endgroup
 \end{document}

### 2018-02-07 dev/helper-functions.R
update on get.summary.stats

@@ -232,16 +232,16 @@ print.plots.pdf <- function(netsim,
 ## function to get mean and 95% CIs as a data.frame
 ## param: 'netsim' a object class netsim
 ## param: 'qvals' a vector of length 2, quantiles to probe level of CIs
-get.summary.stats <- function(netsim, qvals = c(0.025, 0.975)) {
+get.summary.stats <- function(netsim, qvals = c(0.025, 0.5, 0.975)) {
   col.names <- colnames(as.data.frame(netsim))[-1]
 
-  dat.mean <- as.data.frame(netsim, out = "mean")
+  dat.mean <- as.data.frame(netsim, out = "qnt", qval = qvals[2]) ## median
   colnames(dat.mean) <- c("time", paste(col.names, "mean", sep = "."))
 
-  dat.llci <- as.data.frame(netsim, out = "qnt", qval = qvals[1])
+  dat.llci <- as.data.frame(netsim, out = "qnt", qval = qvals[1]) ## 95% lower
   colnames(dat.llci) <- c("time", paste(col.names, "llci", sep = "."))
 
-  dat.ulci <- as.data.frame(netsim, out = "qnt", qval = qvals[2])
+  dat.ulci <- as.data.frame(netsim, out = "qnt", qval = qvals[3]) ## 95% upper
   colnames(dat.ulci) <- c("time", paste(col.names, "ulci", sep = "."))
 
   modelDT <- Reduce(function(x, y) merge(x, y, by = "time"), list(dat.mean,

### 2018-02-07 manuscript_1.0.tex

@@
 \usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,uniquename=false]{biblatex}
-\usepackage[colorlinks=true]{hyperref}
+\usepackage[colorlinks=false]{hyperref}
 \usepackage{xcolor}
@@
 
-\note{Word count: \quickwordcount \\
-	  Draft date: \today \\
-      \textbf{Draft in progress. Please do not cite without permission.} \\
-      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
+\note{%Word count: \quickwordcount \\
+      \textbf{Draft in progress. Please do not cite without permission.} Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
 

### 2018-02-08 manuscript_1.0.tex
interm update on draft

--- 2018-02-07 manuscript_1.0.tex
@@
 \usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,uniquename=false]{biblatex}
+% make in-text citations clickable
 \usepackage[colorlinks=true]{hyperref}
+% this removes annoying colors for clickable in-text citation entries 
 \usepackage{xcolor}
@@
 
-\title{If you see something, say something (to others): A spread of misinformation and socially-contingent corrections within social networks}
+\title{If you see something, then say something to others: A simple contagion of misinformation and a complex contagion of socially-contingent corrections}
 \shorttitle{Socially-contingent corrections}
@@
 
-\note{Word count: \quickwordcount \\
+\note{%Word count: \quickwordcount \\
     Draft date: \today \\
@@
 presidential election \parencite{guess2018selective, giglietto2016fakes, allcott2017social} and in Brexit votes \parencite{nyt_2017}.
-While a wide circulation of factually dubious information is not entirely new to politics, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{Fake news} phenomenon -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social, LEWANDOWSKY_JARMC2017}.
+While a wide circulation of factually dubious information is not entirely new to politics, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{Fake news} phenomenon -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social}.
 Either based on unsubstantiated rumors or based on factually wrong beliefs, many of the misinformed behave differently than those who are accurately informed \parencite{kuklinski2000misinformation,Garrett_Weeks_2013}.
@@
 
-	Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive and affective mechanisms \parencite{LEWANDOWSKY_JARMC2017, Lewandowsky_2012PSPI, kuklinski2000misinformation, garrett2016driving, weeks2015emotions}.
-These studies have generated a valuable insights of how individuals maintain false beliefs, and how corrections to such false beliefs are received and processed under various scenarios \parencite{LEWANDOWSKY_JARMC2017, thorson_2016}.
+  Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive and affective mechanisms \parencite{Lewandowsky_2012PSPI, kuklinski2000misinformation, garrett2016driving, weeks2015emotions}.
+These studies have generated a valuable insights of how individuals maintain false beliefs, and how corrections to such false beliefs are received and processed under various scenarios \parencite{Lewandowsky_2012PSPI, thorson_2016}.
 However, despite growing interest and continued research effort to better understand the nature and its exact mechanism, what we know about the spread of misinformation and fake news on online social networks is largely based on limited evidence due to its complex nature of the problem.
@@
 We argue that while \emph{exposure} to (mis)information is likely to follow a simple contagion process, \emph{changes} in one's beliefs regarding such (mis)information -- which ultimately \emph{the} goal of corrective messages -- is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where such changes require multiple sources of affirmation and reinforcement compared to simple contagion process.
-As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, yet the vast majority of prior studies have not considered this possibility to date \parencite{margolin2017}.
+As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, yet the vast majority of prior studies have not considered this possibility \parencite{margolin2017, bode2017see}.
 
-	In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking (i.e., corrective) messages.
+  In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking (i.e., correction) messages.
 We advance our dynamic system perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which an exposure to misinformation and corrections are received.
@@
 Therefore, it is perhaps not surprising to find that most of the prior studies based on motivated reasoning framework document that fact-checking messages (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process (politically) relevant information \parencite{thorson_2016, taber2006,flynn2017nature}.
-Or worse, often such corrective messages may backfire \parencite[i.e., more likely to increase than lower the endorsement of false beliefs:][]{nyhan2010corrections}.
+Even worse, corrective messages may backfire, may induce higher level of endorsements of false beliefs than actually lower them \parencites[e.g.,][]{nyhan2010corrections}[but see][]{Wood2018}.
 
-      Another line of studies focusing on an individual-level cognitive processing and memory suggests that while attitudinally-congruent misinformation creates automatic and strong affective responses (therefore more easily remembered and readily available in their memory), corrections rarely produce such responses, and therefore requires more resources to recall and incorporate into relevant judgments \parencite{thorson_2016, Lewandowsky_2012PSPI}.
-Also, since misinformations tend to form a coherent mental model of an relevant event based on their partisan schema or based on stereotypes \parencite[e.g.,][]{garrett2013undermining}, people tend to fill any gaps caused by corrections (that invalidates some parts of the mental model) with flawed but attitudinally congruent (mis)information available in memory \parencite{Lewandowsky_2012PSPI}, especially when correction messages does not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}.
-Studies also find that this effect is much likely when initial misinformation is more readily accessible due to fluency bias in one's cognitive processing \parencite{lazer2017combating, Lewandowsky_2012PSPI}, when individuals can generate (counter-arguing) reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}, and most importantly, \emph{even when they remember such information is factually incorrect} \parencite{Lewandowsky_2012PSPI}.
-Due to asymmetrical nature in one's cognitive processing fluency, people have to rely on more deliberative process to recall attitudinally inconsistent correction messages (which requires significant  resources), whereas misinformation is more easily processed and automatically activated.
-Therefore, even in the face of corrections, the effect of misperceptions linger and continue to exert influence on subsequent judgments via spontaneous (i.e., automatic) affective process \parencite[e.g.,][]{thorson_2016}.
+      Another line of studies based on a dual process theory of human cognitive processing and memory suggests that attitudinally-congruent misinformation creates automatic and strong affective responses (i.e., automatically and effortlessly activated), whereas attitudinally incongruent correction messages rarely produce such responses.
+Due to such asymmetrical nature, people have to rely on more deliberative, strategic processes (which require significant cognitive resources) to recall attitudinally inconsistent correction messages and incorporate them into relevant judgments \parencite{thorson_2016, Lewandowsky_2012PSPI, SwireEcker2018}.
+Also, since misinformations tend to form a coherent mental model of a relevant event based on their partisan schema and stereotypes \parencite[e.g.,][]{garrett2013undermining}, people tend to fill any gaps caused by corrections (that invalidate some parts of their existing mental model) with a flawed but attitudinally congruent misinformation that is still readily accessible in their memory \parencite{Lewandowsky_2012PSPI, SwireEcker2018}.
+Studies also find that this effect is much more likely when correction messages do not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017, SwireEcker2018}, when the perceived veracity of initial misinformation is high (due to fluency bias in one's cognitive processing) \parencite{SwireEcker2018, Lewandowsky_2012PSPI}, or when individuals can generate (counter-arguing) reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}.
+Most importantly, due to aforementioned limitations of strategic memory processes (which require effortful processing), people may still rely on negated misinformation in subsequent reasoning \emph{even when they remember such information is factually incorrect} \parencite{Lewandowsky_2012PSPI}.
+Therefore, even in the face of seemingly effective corrections, the effect of misperceptions lingers and continue to exert influence \parencite[e.g.,][]{thorson_2016}.
 
-      However, other studies also find that, under certain situations, citizens \emph{indeed} can adhere factual information based on correction messages despite of their perpetual partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013, weeks2015emotions}.
-Notably, \citeauthor{Wood2018}'s (\citeyear{Wood2018}) series of experiments document that
+        Under certain situations, it appears that citizens \emph{indeed} can adhere factual information based on correction messages despite of their perpetual partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013, weeks2015emotions}.
+Yet as \citeauthor{margolin2017} (\citeyear{margolin2017}) note, it appears that such effects often require special \emph{social context}.
+This observation is indeed much warranted, as most of the previous studies concerning misinformation and the effect of fact-checking messages are conducted in an experiment context with a single-shot, \emph{asocial} correction message from media professionals and fact-checking organizations \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining,weeks2015emotions}.
+Much of the literature on partisan selective exposure and political discussion networks already point that social contexts of which an individual is exposed to counter-attitudinal messages may have a powerful consequence on how such messages are interpreted and processed \parencite{messing2014selective, levitan2014seeking, levitan2008resistance}.
+There is also a suggestive evidence that fact-checking and corrective messages from one's peers in their social networks -- what we would call a \enquote{social correction} -- are more likely to, if not equally, be effective in reducing misperceptions \parencite[e.g.,][]{margolin2017, bode2017see}.
+In what follow, we review several theoretical accounts of such \emph{socially-based} correction messages on misinformation and fake news.
+
+\section{A \emph{Social} Context of Misperceptions and Corrections: Simple vs. Complex Contagion}
+
+  People's perceptions and behaviors are likely to be interdependent upon their social contacts \parencite{lazer2010coevolution, centola2007complex}, and therefore it is not surprising that such perceptions and behaviors may spread through social networks \parencite[e.g.,][]{christakis2007spread, bond_61million}.
+Indeed, a non-negligible number of prior accounts concerning the misperception and fake news in social networks connect this idea to possible mechanisms of \emph{spreading} of misinformation \parencite[e.g.,][]{del2016spreading, lazer2017combating, Bessi_2015}.
 

### 2018-02-14 manuscript_1.0.tex
update until: front part of section 3

--- 2018-02-07 manuscript_1.0.tex
@@
 % declare documents and packages
-\documentclass[man, 12pt, a4paper]{apa6}
+\documentclass[man, 12pt, a4paper, noextraspace]{apa6}
 \usepackage[T1]{fontenc}
@@
 \usepackage{graphicx}
-\usepackage{amsmath}
 \usepackage{url}
 \usepackage{times}
+\renewcommand{\footnotesize}{\normalsize} % use 12pt for footnotes
+\usepackage[doublespacing]{setspace} % single space for footnotes
+% this command put all footnotes to endnote at the end of the paper
 \usepackage{endnotes}
-% this command put all footnotes to endnote at the end of the paper
 \let\footnote\endnote
@@
 \usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,uniquename=false]{biblatex}
+% make in-text citations clickable
 \usepackage[colorlinks=true]{hyperref}
+% this removes annoying colors for in-text citation entries 
 \usepackage{xcolor}
@@
 
-\title{If you see something, say something (to others): A spread of misinformation and socially-contingent corrections within social networks}
+\title{If you see something, then say something to others: A simple contagion of misinformation and a complex contagion of socially-contingent corrections}
+
 \shorttitle{Socially-contingent corrections}
 
-\author{Hyunjin Song}
+\author{\addvspace{.25in} Hyunjin Song}
 
@@
 
+\keywords{Misinformation, fake news, correction, simple contagion, complex contagion, agent-based simulations}
+
 \authornote{Hyunjin (Jin) Song is currently an assistant professor ("Universitätsassistent, post-doc") in the Department of Communication at the University of Vienna, and also a member of the Vienna Computational Communication Science Lab.}
 
-\note{Word count: \quickwordcount \\
+\note{Word count: 3284 words %\quickwordcount \\
 	  Draft date: \today \\
+      \addvspace{.25in} 
       \textbf{Draft in progress. Please do not cite without permission.} \\
@@
 \begin{document}
+\setcounter{page}{0}
 \maketitle
@@
 One of the most dramatic changes in the news environment in recent decades involves the role social networking sites (SNS) such as Facebook and Twitter play as a primary source of news outlets.
-Not only citizens' news consumptions are increasingly driven by such online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination on those platforms by sharing news contents with their peers \parencite[e.g.,][]{weeks2013dissemination, lee2017people}.
+Not only citizens' news consumptions are increasingly driven by such online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination on those platforms by sharing news contents with their peers \parencite[e.g.,][]{shearer2017news, lee2017people}.
 
-	An effective deliberation among public is regarded as a keystone of thriving democracies, and modern political systems squarely depend  on  informed  decisions of citizens in that regard \parencite{carpini1996, stromback2005search}.
-Yet, a propagation of rumors, misinformation, and so-called \enquote{Fake news} on those platforms becomes an increasing concern for the public and policy makers alike \parencite{allcott2017social}.
-There are abundant, yet still fragmentary, evidence of viral spreads of unsubstantiated, often factually dubious (mis)information that potentially affecting millions of citizens across the globe -- as evidenced in recent 2016 U.S.
+	An effective deliberation among public is regarded as a keystone of thriving democracies, and modern political systems squarely depend  on  informed  decisions of citizens in that regard \parencite{carpini1996}.
+Yet, a propagation of rumors, misinformation, and so-called \enquote{fake news} on those platforms becomes an increasing concern for the public and policy makers alike \parencite{allcott2017social, lazer2017combating}, %There are abundant, yet still fragmentary, evidence of spreads of unsubstantiated, often factually dubious (mis)information through digital social networks that potentially affecting millions of citizens across the globe --
+    as evidenced in recent 2016 U.S.
 presidential election \parencite{guess2018selective, giglietto2016fakes, allcott2017social} and in Brexit votes \parencite{nyt_2017}.
-While a wide circulation of factually dubious information is not entirely new to politics, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{Fake news} phenomenon -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social, LEWANDOWSKY_JARMC2017}.
-Either based on unsubstantiated rumors or based on factually wrong beliefs, many of the misinformed behave differently than those who are accurately informed \parencite{kuklinski2000misinformation,Garrett_Weeks_2013}.
-They often disagree about basic facts about many political and public issues \parencite[e.g.,][]{nisbet2015partisan}, and continue to believe and rely on such false information when evaluating political matters \parencite{nyhan2010corrections,thorson_2016}.
+While a wide circulation of factually dubious information is not entirely new to political arena, a growing trend of digitally disseminated rumors and misinformations -- often termed as a \enquote{fake news} phenomenon -- is increasingly recognized as a serious threat to liberal democratic societies \parencite{allcott2017social, lazer2017combating}.
+Either based on unsubstantiated rumors or based on factually wrong beliefs, many of the misinformed behave differently than those who are accurately informed \parencite{kuklinski2000misinformation}.
+They often disagree about basic facts about many political and public issues \parencite[e.g.,][]{nisbet2015partisan}, and continue to believe and rely on such false information when making political judgments \parencite{nyhan2010corrections,thorson_2016}.
 
-	Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive and affective mechanisms \parencite{LEWANDOWSKY_JARMC2017, Lewandowsky_2012PSPI, kuklinski2000misinformation, garrett2016driving, weeks2015emotions}.
-These studies have generated a valuable insights of how individuals maintain false beliefs, and how corrections to such false beliefs are received and processed under various scenarios \parencite{LEWANDOWSKY_JARMC2017, thorson_2016}.
-However, despite growing interest and continued research effort to better understand the nature and its exact mechanism, what we know about the spread of misinformation and fake news on online social networks is largely based on limited evidence due to its complex nature of the problem.
+	Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive processes \parencite{Lewandowsky_2012PSPI, kuklinski2000misinformation, weeks2015emotions}.
+These studies have generated a valuable insights of how individuals often maintain factually false beliefs, and further, how corrections to false beliefs are received and processed \parencite{Lewandowsky_2012PSPI, thorson_2016, garrett2016driving}.
+However, despite growing interest and continued research effort to better understand the nature and its exact mechanism, what we know about the spread of misinformation and fake news specifically on online social networks is largely based on limited evidence due to its complex nature of the problem.
 
@@
 We argue that while \emph{exposure} to (mis)information is likely to follow a simple contagion process, \emph{changes} in one's beliefs regarding such (mis)information -- which ultimately \emph{the} goal of corrective messages -- is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where such changes require multiple sources of affirmation and reinforcement compared to simple contagion process.
-As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, yet the vast majority of prior studies have not considered this possibility to date \parencite{margolin2017}.
+As a result, the effects of fact-checking and corrective messages are likely to be highly \emph{socially} contingent, yet studies only now begin to consider this possibility more seriously \parencite{margolin2017, bode2017see}.
 
-	In what follows, we first review existing evidence regarding political misperceptions and the effect of fact-checking (i.e., corrective) messages.
-We advance our dynamic system perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which an exposure to misinformation and corrections are received.
-Based on a well-known class of an epidemic model of virus infection and recovery, we propose an integrated model of misinformation diffusion and socially-contingent corrections on social networks, with a special focus on the differences between simple contagion of misinformation and complex contagion of corrections.
-Relying on Agent-based simulations, we further explore boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public, as well as what factors facilitate or hinder such diffusion process.
+	In what follows, we first review existing evidence regarding political misperceptions and the effects of fact-checking (i.e., correction) messages.
+We advance our perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which misinformation and corrections are received.
+Based on a well-known class of an epidemic model of virus infection and recovery, we propose an integrated model of misinformation diffusion and socially-contingent corrections on social networks, with a special focus on the differences between a \emph{simple contagion} of misinformation and a \emph{complex contagion} of corrections and fact-checking messages.
+Relying on Agent-Based Model (ABM) simulations, we robustly explore boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public.
 
@@
 
-     Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define \emph{Fake news} as \enquote{distorted signals uncorrelated with the truth} (p.
+     Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define \emph{fake news} as \enquote{distorted signals uncorrelated with the truth} (p.
 212).
 This encompasses several related concepts, such as misinformation, rumors, and disinformation.
-Literature on this topic generally maintain loosely defined, but at the same time highly interrelated, definitions of those related terms.
+Literature on this topic generally maintain loosely defined, but at the same time highly interrelated, conceptualizations of those related terms.
 For instance, (political) rumors are often defined as \enquote{unsubstantiated claims about candidates and issues that are often false} \parencite[p.
@@
 While term \emph{fake news} often than not additionally entail specific pseudo-journalistic styles that mimic legitimate news sources to intentionally deceiving audiences \parencite{jana_sophie_fn}, we use term \enquote{fake news} somewhat loosely, denoting any type of misinformation -- information that is not supported by best-available evidence -- that is deliberatively circulated among publics.\footnote{	Often, the term \emph{fake news} is used as derogatory, rhetorical label to attack political opponents.
-While such use of the term as a \emph{label} is an important conceptual dimension to consider, this aspects of \emph{fake news} is beyond the scope of this manuscript.
+While such a use of the term as a \emph{label} is an important conceptual dimension to consider, this aspect of \emph{fake news} is beyond the scope of this manuscript.
 See \citeauthor{jana_sophie_fn} (\citeyear{jana_sophie_fn}) instead for a detailed conceptualization involving this distinction.}
@@
       Literature on misinformation and its persistence often converges to the observation that publics' exposure to and acceptance of misinformation are largely driven by one's motivated consistency needs.
-That is, people are more often than not likely to be disproportionately drawn by information that conforms to their partisan priors \parencite{guess2018selective, weeks2014electoral}, and also more likely to accept and endorse such messages \parencite{kunda1990,nyhan2010corrections}.
-A mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that citizens tend to evaluate attitudinally congruent information as more convincing and valid \emph{regardless of its truth-value}, while inconsistent information is likely to be perceived as weak and therefore likely to be rejected \parencite{taber2006,weeks2015emotions}.
-Therefore, it is perhaps not surprising to find that most of the prior studies based on motivated reasoning framework document that fact-checking messages (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process (politically) relevant information \parencite{thorson_2016, taber2006,flynn2017nature}.
-Or worse, often such corrective messages may backfire \parencite[i.e., more likely to increase than lower the endorsement of false beliefs:][]{nyhan2010corrections}.
+That is, people disproportionately gravitate toward information that conforms to their partisan priors \parencite{ weeks2014electoral, garrett2016driving}, and  more likely to accept and endorse such messages \parencite{nyhan2010corrections, guess2018selective}.
+A mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that citizens tend to evaluate attitudinally congruent information as more convincing and valid \emph{regardless of its veracity}, while attitudinally inconsistent information is likely to be perceived as weak and therefore likely to be rejected.
+Therefore, it is perhaps not surprising to find that most of the prior studies based on a motivated reasoning framework document that fact-checking messages (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process politically relevant information \parencite{thorson_2016, taber2006,flynn2017nature}.
+Even worse, corrective messages may backfire, may induce higher level of endorsements of false beliefs than actually lower them \parencites[e.g.,][]{nyhan2010corrections}[but see][]{Wood2018}.
 
-      Another line of studies focusing on an individual-level cognitive processing and memory suggests that while attitudinally-congruent misinformation creates automatic and strong affective responses (therefore more easily remembered and readily available in their memory), corrections rarely produce such responses, and therefore requires more resources to recall and incorporate into relevant judgments \parencite{thorson_2016, Lewandowsky_2012PSPI}.
-Also, since misinformations tend to form a coherent mental model of an relevant event based on their partisan schema or based on stereotypes \parencite[e.g.,][]{garrett2013undermining}, people tend to fill any gaps caused by corrections (that invalidates some parts of the mental model) with flawed but attitudinally congruent (mis)information available in memory \parencite{Lewandowsky_2012PSPI}, especially when correction messages does not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}.
-Studies also find that this effect is much likely when initial misinformation is more readily accessible due to fluency bias in one's cognitive processing \parencite{lazer2017combating, Lewandowsky_2012PSPI}, when individuals can generate (counter-arguing) reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}, and most importantly, \emph{even when they remember such information is factually incorrect} \parencite{Lewandowsky_2012PSPI}.
-Due to asymmetrical nature in one's cognitive processing fluency, people have to rely on more deliberative process to recall attitudinally inconsistent correction messages (which requires significant  resources), whereas misinformation is more easily processed and automatically activated.
-Therefore, even in the face of corrections, the effect of misperceptions linger and continue to exert influence on subsequent judgments via spontaneous (i.e., automatic) affective process \parencite[e.g.,][]{thorson_2016}.
+      Another line of studies based on a dual process theory of human cognitive processing and memory suggests that attitudinally-congruent misinformation creates automatic and strong affective responses -- therefore automatically and effortlessly activated in one's memory -- whereas attitudinally incongruent correction messages rarely produce such responses.
+Due to such asymmetrical nature, people have to rely on more deliberative, strategic search processes (which require significant cognitive resources) to recall attitudinally inconsistent correction messages and incorporate them into relevant judgments \parencite{thorson_2016, Lewandowsky_2012PSPI}.
+Also, since misinformation tends to form a coherent mental model based on one's partisan schema and stereotypes \parencite[e.g.,][]{garrett2013undermining}, people tend to fill any gaps caused by corrections (that invalidate some parts of the existing mental model) with flawed but attitudinally congruent misinformation that is still readily accessible in their memory \parencite{Lewandowsky_2012PSPI}.
+Studies also find that this effect is much more likely when correction messages do not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}, when the perceived veracity of initial misinformation is high \parencite[due to fluency bias in one's cognitive processing:][]{Lewandowsky_2012PSPI}, or when individuals can generate counter-arguing reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}.
+Most importantly, due to limitations of strategic memory search processes (i.e., it requires more effortful processing), people may still rely on negated misinformation in subsequent reasoning \emph{even when they remember such information is factually incorrect} \parencite{Lewandowsky_2012PSPI}.
+Therefore, even in the face of seemingly effective corrections, the effect of misperceptions lingers and continue to exert influence \parencite{thorson_2016}.
 
-      However, other studies also find that, under certain situations, citizens \emph{indeed} can adhere factual information based on correction messages despite of their perpetual partisan bias \parencite[e.g.,][]{Wood2018, Garrett_Weeks_2013, weeks2015emotions}.
-Notably, \citeauthor{Wood2018}'s (\citeyear{Wood2018}) series of experiments document that
+        Under certain situations, it seems that citizens \emph{indeed} can adhere factual information based on correction messages despite their perpetual partisan bias \parencite[e.g.,][]{Wood2018, nyhan2017taking}.
+Yet as \citeauthor{margolin2017} (\citeyear{margolin2017}) note, it appears that such effects often require special \emph{social context}.
+This observation is indeed much warranted, as most of the previous studies concerning misinformation and the effect of fact-checking messages are conducted in an experimental context with a single-shot, \emph{asocial} correction message from media professionals and fact-checking organizations \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining,weeks2015emotions}.
+Much of the literature on partisan selective exposure and political discussion networks already point that social contexts of which an individual is exposed to counter-attitudinal messages may have a powerful consequence on how such messages are interpreted and processed \parencite{messing2014selective, levitan2008resistance}.
+There is also a suggestive evidence that fact-checking and corrective messages from one's peers in their social networks -- what we would call a \enquote{social correction} -- are more likely to, if not equally, be effective in reducing misperceptions \parencite[e.g.,][]{margolin2017, bode2017see}.
+In what follow, we review several theoretical accounts of such \emph{socially-based} correction messages on misinformation and fake news.
+
+\section{A Social Context of Misperceptions and Corrections: Simple vs. Complex Contagion}
+
+	People's perceptions and behaviors are likely to be shaped by their social contacts \parencite{lazer2010coevolution, centola2007complex}, and therefore perceptions and behaviors may spread within social networks \parencite[e.g.,][]{bond_61million}.
+Indeed, a non-negligible number of prior accounts of partisan misperceptions and fake news on social networks connects this idea to possible mechanisms of misinformation \emph{spreading}  \parencite[e.g.,][]{del2016spreading, Bakshy_2012}.
+The most simplest form of those accounts posits that online social networks provide one of the ideal settings of a spread of partisan misinformation and fake news.
+Many of the partisan rumors and fake news tend to be richer in their \enquote{novelty} \parencite{wu2007novelty} regardless of its veracity and informational value.
+As \citeauthor{giglietto2016fakes}'s (\citeyear{giglietto2016fakes}) observation suggests, such non-redundant and \enquote{novel} information (false and unverified information being one of them) tend to be engaging, and spread faster via weaker ties \parencite{granovetter1977strength}.
+You can easily share and post such news with little to no effort, and your friends on your social networks are easily exposed to such information, in turn they also share such news to their own peers, and so on -- creating what is called a \emph{information cascade} of misinformation \parencite{del2016spreading}.
+Also, individuals maintain lots of weak ties in social network platforms, which is thought to diversify the information flow.
+This creates a particularly congenial scenario for a (mis)information propagation and dissemination \parencite{Bakshy_2012, granovetter1977strength}.
+Indeed, \citeauthor{guess2018selective}'s (\citeyear{guess2018selective}) investigation of fake news consumption during the 2016 U.S.
+presidential election suggests that Facebook was likely to be the focal gateway for visiting websites that propagates fake news, while \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) study also reveals that such dubious stories are indeed widely shared on Facebook during the election.
+
+    Often, this process of spreading (mis)information within a social network can be described as a \emph{simple contagion} process -- the process of which a single contact with an \enquote{infected} individual (in this case, those who spread misinformation to their peers) is sufficient for such misinformation to be spread to another individual \parencite{Monsted_plos2017, Centola2010Sience, siegel2009social}.
+While a spread of any human behavior requires a minimum threshold of one, for the diffusion of information itself -- much like communicable diseases -- \enquote{the threshold is almost always exactly one}  \parencites[][p.
+706]{centola2007complex}[also see][]{Centola2010Sience}.
+Once your peer shares news, you become (almost automatically) aware of such news, and you do not require someone else to keep asking about the same news in order to be \emph{aware} of it.
+
+    Moreover, due to inherent partisan motivated directionality, the threshold of actually \emph{adapting} such a false yet pro-attitudinal claim (i.e., believing attitudinally congruent misinformation) may also exhibit similar low-threshold properties, although the actual threshold for believing misinformation would be bit higher compared to that of mere exposure and awareness \parencite[e.g.,][]{Monsted_plos2017}, and also subject to some individual differences \parencite[e.g.,][]{weeks2015emotions}.
+As previously suggested, people tend to directionally process political information \parencite{taber2006}, and they tend to easily remember and recall attitudinally-consistent information than uncongenial ones.
+Therefore, at least for citizens who find a given misinformation to be congenial to their prior partisan identities, \emph{adapting} such false yet pro-attitudinal claims also does not require high number of repeated exposure nor independent, multiple exposure to different sources supporting such claims.
+Indeed, many of the prior empirical studies support this perspective \parencite[e.g.,][]{garrett2016driving, kuklinski2000misinformation, nisbet2015partisan, flynn2017nature}.
+
+    In contrast, there are reasons to believe why the effectiveness of fact-checking and corrective messages would be different from that of a simple contagion of (mis)information.
+An adoption of a new perspective that contradicts to one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion,} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple exposures}, in order to be accepted and further spread into a given network.
+This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2011dynamics, larson2016social, siegel2009social}.
+
+    Moreover, such complex contagion dynamics surrounding correction messages are also likely to be dependent upon the attitudinal composition of one's local network; the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{believe} misinformation) tend to discourages their neighbors to adopt corrections, whereas the number of one's neighbors who are already activated would increase one's susceptibility to adopt new perspective given exposure to correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}.
+Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by one's neighbors, therefore relative distribution of one's neighbors (in terms of supporters vs.
+opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2011dynamics, friedkin2001norm}.
+This further implies that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite{friedkin2001norm}.
+Indeed, there exits a considerable support for this perspective, showing that different network topologies \parencite[e.g.,][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{	Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs.
+opponents regarding a given attitude or a behavior being spread in a network.} \parencite[e.g.,][]{levitan2008resistance, larson2016social, gonzalez2011dynamics} may produce different attitudinal and behavioral consequences, further suggesting that some network structures are more prone to generating cascades and adoptions than others.
+
+	There are at least several other reasons why socially-based correction messages, especially from one's peers, might be more effective than a single-shot, \emph{asocial} correction message from more distanced sources (such as fact-checking organizations or mere strangers).
+First, people may evaluate information coming from their peers to be more credible and trustworthy \parencite[e.g.,][]{metzger2010social}, and more willing to deliberate with their close social contacts \parencite{morey2012matters}.
+Research suggests that while individuals rather maintain much flexible attitudes as long as their social affiliation goals are met \parencite{levitanspy2017}, reputational risks and social accountability of rejecting corrective messages run high for more close social contacts compared to more distant sources such as strangers \parencite{margolin2017}.
+
+    Second, previous studies concerning citizens' political discussion network suggest that an individual's network construction is not likely driven by overt partisan considerations \parencite{song2015uncovering,lazer2010coevolution}, therefore there exists a considerable degree of exposure to disagreement in citizens' everyday political interactions \parencite[e.g.,][]{Bakshy1130, morey2012matters}.
+Under such a situation, attitudinally heterogeneous networks trigger more systematic processing of available information, which make individuals to be more responsive to argument strengths \parencite{levitan2008resistance} or social utility \parencite{messing2014selective}, therefore makes them less resistant to corrective messages from their peers.
+
+	All in all, prior empirical evidence and theoretical perspectives convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level contagion dynamics.
+Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, while ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation.
+In contrast, an adoption of corrective message requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition -- similar to controversial innovations \parencite{centola2007complex, Centola2010Sience, gonzalez2011dynamics}.
+Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experiment contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.
+
+\section{Analytical Challenges in Studying (Mis)information Diffusion Within Social Networks}
+
+	If the diffusion of (mis)information and adoption of corrective messages may non-trivially dependent upon a structure of a given network and its attitudinal composition, then how a typical (online) social network is structured in terms of its topological features, and how pervasive is \enquote{attitudinal} homophily on such a social network?
+How such structural features affect the overall diffusion dynamics empirically?
+This is indeed an important question to ask, since the flow of information (either misinformation or its correction) and its adoption are ultimately structured by how individuals are connected with each other in a given network.
+
+    A frequent and recurring theme for (attitudinal) makeup of citizens' social networks and its consequences, among scholars and general publics alike, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulate themselves from competing viewpoints and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, Bessi_2015, del2016spreading}.
+Yet, as \citeauthor{Garrett2017distraction} (\citeyear{Garrett2017distraction}) puts it, \enquote{there is ample evidence that \emph{exposure} [emphasis added] echo chambers are not a typical part of Internet users' experience} (p.
+370).
+Most of citizens are appear to be embedded in sufficiently diverse social networks, either online \parencite[e.g.,][]{Bakshy1130, messing2014selective} or offline \parencite{song2015uncovering, lazer2010coevolution}, documenting a substantial level of exposure to political difference in citizen’s everyday political interactions.
+This suggests that popular claims of echo chambers or filter bubbles are less warranted than it is often assumed.\footnote{		Indeed, in a completely segregated network where cross-ideological links are not present, a simple diffusion of partisan misinformation is not likely to saturate the entire network, since at least some segments of populations are never exposed to such information due to the lack of cross-ideological exposure.
+In light of our discussion, an \enquote{exposure} echo chamber actually \emph{prohibits} global-scale (mis)information propagation.} However, one should also bear in mind that evidence of exposure to a counter-attitudinal messages does not provide enough evidence for how such messages are actually interpreted and adopted \parencite[e.g.,][]{nyhan2017taking, Garrett2017distraction}.
+Indeed, many of the prior studies on this topic relies on observational evidence regarding message \emph{exposure patterns} alone, either based on participants' self-reports or based on messages posted (sometimes along with engagement data such as \enquote{likes} or \enquote{shares}) in online social networks \parencite[e.g.,][]{Bakshy1130}, not based on how an individuals actually process and interpret such information.
+As suggested by elsewhere, attitudinal composition of one's network may fundamentally alter how (identical) messages are interpreted and received by an individual \parencite{Garrett2017distraction, levitan2008resistance}.
+As experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility that such exposure would promote more balanced judgments.
+In contrast, experimental evidence provide more detailed picture of how such (counter-attitudinal) messages are actually processed and adopted \parencite[e.g., ][]{messing2014selective, nyhan2017taking, Wood2018}.
+Yet as previously suggested, a typical experimental approach tends to be misspecified in terms of important social dynamics surrounding the simple vs.
+complex contagion of misinformation and (counter-attitudinal) corrective messages \parencite{margolin2017, Centola2010Sience}.
+In addition, designing a realistic experiment involving real-world social interactions often involves significant practical \parencite[e.g.,][]{bond_61million} and ethical challenges \parencite[e.g.,][]{Kramer8788} for researchers.
+
+    Similarly to attitudinal composition of citizen's social networks, the question of how exactly the structure of citizens' interaction exhibit certain topological properties have attracted considerable interests among scholars.
+Prior observations on this topic tend to suggests that large-scale online networks exhibit \enquote{small-world}-like properties \parencite{kumar2010structure, ugander2011anatomy}.
+A small world is characterized by high connectivity and relatively short average distance among most nodes -- most nodes can be reached from every other node by a small number of hops or steps -- compared to pure random graphs.
+This is due to the fact that a small minority of \enquote{hub} nodes concentrates a disproportionate number of links, providing a global bridge between smaller, more strongly interconnected local clusters \parencite{barabasi2004linked}.
+This structure is known for expediting simple information to be spread globally \parencite{granovetter1977strength, Bakshy_2012}, yet it also tends to facilitate complex contagion since the existence of tightly knit neighborhoods supports complex-type behavioral propagation that is difficult or considered to be run counter to prevalent norms and values \parencite{Centola2010Sience}.
+
+    %\enquote{Despite the scientific and practical importance...an empirical test of these predictions has not been possible, because it requires the ability to independently vary the topological structure of a social network}
+
+%\subsection{}    
+%    \enquote{While much of the literature on networks treats the topological features of social structure as given quantities, networks do not emerge \emph{ex nihilo}, but are endogenously formed}
 
@@
 \parindent 0pt
-\parskip 2ex
+\parskip 1ex
 \def\enotesize{\normalsize}

### 2018-02-14 manuscript_1.0.tex
probably the last update on section 3

@@
 \usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,uniquename=false]{biblatex}
+\AtEveryBibitem{%
+  \clearfield{issn} % Remove issn
+  \clearfield{doi} % Remove doi
+  }
 % make in-text citations clickable
@@
 
-\title{If you see something, then say something to others: A simple contagion of misinformation and a complex contagion of socially-contingent corrections}
+\title{If you see something, then say something to others: Complex contagions and the socially-contingent correction of misinformation}
 
@@
 
-\note{Word count: 3284 words %\quickwordcount \\
+\note{Word count: 3599 words \\ %\quickwordcount \\
     Draft date: \today \\
@@
   An effective deliberation among public is regarded as a keystone of thriving democracies, and modern political systems squarely depend  on  informed  decisions of citizens in that regard \parencite{carpini1996}.
-Yet, a propagation of rumors, misinformation, and so-called \enquote{fake news} on those platforms becomes an increasing concern for the public and policy makers alike \parencite{allcott2017social, lazer2017combating}, %There are abundant, yet still fragmentary, evidence of spreads of unsubstantiated, often factually dubious (mis)information through digital social networks that potentially affecting millions of citizens across the globe --
-    as evidenced in recent 2016 U.S.
+Yet, a propagation of rumors, misinformation, and so-called \enquote{fake news} on those platforms becomes an increasing concern for the public and policy makers alike \parencite{allcott2017social, lazer2017combating}, as evidenced in recent 2016 U.S.
 presidential election \parencite{guess2018selective, giglietto2016fakes, allcott2017social} and in Brexit votes \parencite{nyt_2017}.
@@
 Either based on unsubstantiated rumors or based on factually wrong beliefs, many of the misinformed behave differently than those who are accurately informed \parencite{kuklinski2000misinformation}.
-They often disagree about basic facts about many political and public issues \parencite[e.g.,][]{nisbet2015partisan}, and continue to believe and rely on such false information when making political judgments \parencite{nyhan2010corrections,thorson_2016}.
+They often disagree about basic facts about many public issues, and continue to believe and rely on such false information when making political judgments \parencite{nyhan2010corrections,thorson_2016}.
 
@@
 
-\section{A Psychology of Fake News, Misperceptions, and Corrections}
+\section{Psychological Underpinnings of Fake News, Misperceptions, and Corrections}
 
@@
 Therefore, at least for citizens who find a given misinformation to be congenial to their prior partisan identities, \emph{adapting} such false yet pro-attitudinal claims also does not require high number of repeated exposure nor independent, multiple exposure to different sources supporting such claims.
-Indeed, many of the prior empirical studies support this perspective \parencite[e.g.,][]{garrett2016driving, kuklinski2000misinformation, nisbet2015partisan, flynn2017nature}.
+Indeed, many of the prior empirical studies support this perspective \parencite[e.g.,][]{garrett2016driving, kuklinski2000misinformation, flynn2017nature}.
 
@@
 
-	There are at least several other reasons why socially-based correction messages, especially from one's peers, might be more effective than a single-shot, \emph{asocial} correction message from more distanced sources (such as fact-checking organizations or mere strangers).
+  There are also at least several other reasons why socially-based correction messages, especially from one's peers, might be more effective than a single-shot, \emph{asocial} correction message from more distanced sources (such as fact-checking organizations or mere strangers).
 First, people may evaluate information coming from their peers to be more credible and trustworthy \parencite[e.g.,][]{metzger2010social}, and more willing to deliberate with their close social contacts \parencite{morey2012matters}.
@@
 
-\section{Analytical Challenges in Studying (Mis)information Diffusion Within Social Networks}
+\section{Observational Challenges in Studying Misperception Within Social Networks}
 
@@
 How such structural features affect the overall diffusion dynamics empirically?
-This is indeed an important question to ask, since the flow of information (either misinformation or its correction) and its adoption are ultimately structured by how individuals are connected with each other in a given network.
+This is indeed important questions to ask, since the flow of information (either misinformation or its correction) and its adoption are ultimately structured by how individuals are connected with each other in a given network.
+However, it is surprisingly difficult to establish convincing evidence of the impact of structural properties of a given network and its attitudinal composition in complex contagion dynamics using purely observational and experimental approaches.
 
-    A frequent and recurring theme for (attitudinal) makeup of citizens' social networks and its consequences, among scholars and general publics alike, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulate themselves from competing viewpoints and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, Bessi_2015, del2016spreading}.
+    A frequent and recurring theme for (attitudinal) a makeup of citizens' social networks and its consequences, among scholars and general publics alike, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulate themselves from competing viewpoints and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, del2016spreading}.
 Yet, as \citeauthor{Garrett2017distraction} (\citeyear{Garrett2017distraction}) puts it, \enquote{there is ample evidence that \emph{exposure} [emphasis added] echo chambers are not a typical part of Internet users' experience} (p.
 370).
-Most of citizens are appear to be embedded in sufficiently diverse social networks, either online \parencite[e.g.,][]{Bakshy1130, messing2014selective} or offline \parencite{song2015uncovering, lazer2010coevolution}, documenting a substantial level of exposure to political difference in citizen’s everyday political interactions.
-This suggests that popular claims of echo chambers or filter bubbles are less warranted than it is often assumed.\footnote{		Indeed, in a completely segregated network where cross-ideological links are not present, a simple diffusion of partisan misinformation is not likely to saturate the entire network, since at least some segments of populations are never exposed to such information due to the lack of cross-ideological exposure.
-In light of our discussion, an \enquote{exposure} echo chamber actually \emph{prohibits} global-scale (mis)information propagation.} However, one should also bear in mind that evidence of exposure to a counter-attitudinal messages does not provide enough evidence for how such messages are actually interpreted and adopted \parencite[e.g.,][]{nyhan2017taking, Garrett2017distraction}.
-Indeed, many of the prior studies on this topic relies on observational evidence regarding message \emph{exposure patterns} alone, either based on participants' self-reports or based on messages posted (sometimes along with engagement data such as \enquote{likes} or \enquote{shares}) in online social networks \parencite[e.g.,][]{Bakshy1130}, not based on how an individuals actually process and interpret such information.
-As suggested by elsewhere, attitudinal composition of one's network may fundamentally alter how (identical) messages are interpreted and received by an individual \parencite{Garrett2017distraction, levitan2008resistance}.
-As experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility that such exposure would promote more balanced judgments.
-In contrast, experimental evidence provide more detailed picture of how such (counter-attitudinal) messages are actually processed and adopted \parencite[e.g., ][]{messing2014selective, nyhan2017taking, Wood2018}.
-Yet as previously suggested, a typical experimental approach tends to be misspecified in terms of important social dynamics surrounding the simple vs.
-complex contagion of misinformation and (counter-attitudinal) corrective messages \parencite{margolin2017, Centola2010Sience}.
-In addition, designing a realistic experiment involving real-world social interactions often involves significant practical \parencite[e.g.,][]{bond_61million} and ethical challenges \parencite[e.g.,][]{Kramer8788} for researchers.
+Most of citizens are appear to be embedded in sufficiently diverse social networks, showing a substantial level of exposure to political difference online \parencite[e.g.,][]{Bakshy1130, messing2014selective} and offline \parencite[e.g.,][]{huckfeldt2004disagreement}.
+More importantly, those studies do not find compelling evidence that ordinary citizens' network constructions are primarily driven by purposive political homophily that limit their exposure to only congenial political perspectives \parencite{song2015uncovering, lazer2010coevolution}.
+This suggests that popular claims of echo chambers or filter bubbles are often overstated.\footnote{    Indeed, in a completely segregated network where cross-ideological links are not present, a simple diffusion of partisan misinformation is not likely to saturate the entire network, since at least some segments of populations are never exposed to such information due to the lack of cross-ideological exposure.
+In light of our discussion, an \enquote{exposure} echo chamber actually \emph{prohibits} global-scale (mis)information propagation.}
 
-    Similarly to attitudinal composition of citizen's social networks, the question of how exactly the structure of citizens' interaction exhibit certain topological properties have attracted considerable interests among scholars.
-Prior observations on this topic tend to suggests that large-scale online networks exhibit \enquote{small-world}-like properties \parencite{kumar2010structure, ugander2011anatomy}.
-A small world is characterized by high connectivity and relatively short average distance among most nodes -- most nodes can be reached from every other node by a small number of hops or steps -- compared to pure random graphs.
-This is due to the fact that a small minority of \enquote{hub} nodes concentrates a disproportionate number of links, providing a global bridge between smaller, more strongly interconnected local clusters \parencite{barabasi2004linked}.
-This structure is known for expediting simple information to be spread globally \parencite{granovetter1977strength, Bakshy_2012}, yet it also tends to facilitate complex contagion since the existence of tightly knit neighborhoods supports complex-type behavioral propagation that is difficult or considered to be run counter to prevalent norms and values \parencite{Centola2010Sience}.
+    However, one should also bear in mind that the evidence concerning mere \emph{exposure} to counter-attitudinal messages does not provide enough indications of how such messages are actually cognitively processed and interpreted \parencite[e.g.,][]{nyhan2017taking, Garrett2017distraction}.
+What we know about citizens' exposure to disagreement in their social networks typically has relied on observational evidence, either based on participants' self-reports regarding their patterns of social interactions \parencite[e.g.,][]{song2015uncovering, lazer2010coevolution} or based on messages posted (sometimes along with engagement data such as \enquote{likes} or \enquote{shares}) in online social networks \parencite[e.g.,][]{Bakshy1130}.
+While such evidence \emph{do} suggests that citizens are indeed exposed to competing viewpoints in their daily lives, they are typically rather silent about how an individuals actually process and interpret such information at the time of exposure.\footnote{  Recent studies try to overcome problems of typical observational studies by relying on time-stamped, detailed digital footprint data \parencite[e.g.,][]{guess2018selective, margolin2017}, yet such studies also suffer from similar weakness, in that they cannot provide strong causal evidence concerning individuals' actual cognitive processing of counter-attitudinal messages beyond what is available in observational data.} As experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility of more balanced judgments.
+Experimental evidence in this regard can provide more detailed pictures of how such (counter-attitudinal) messages are actually selected, processed, and adopted by an individual given exposure settings \parencite[e.g., ][]{messing2014selective, nyhan2017taking, Wood2018}.
+Yet as previously suggested, a typical experimental approach tends to be misspecified in terms of crucial social dynamics surrounding simple vs.
+complex contagion of misinformation and correction messages within a naturally-occurring social network \parencite{margolin2017, Centola2010Sience}.
+Moreover, designing a realistic experiment involving real-world social interactions often involves significant practical \parencite[e.g.,][]{bond_61million} and ethical challenges \parencite[e.g.,][]{Kramer8788} for researchers.
 
-    %\enquote{Despite the scientific and practical importance...an empirical test of these predictions has not been possible, because it requires the ability to independently vary the topological structure of a social network}
+    Similarly to attitudinal composition of citizen's social networks, the question of how exactly the structure of citizens' social networks exhibits certain topological properties have attracted considerable interests among scholars.
+Prior observations on this topic suggests that large-scale (online) networks tend to exhibit \enquote{small-world} like properties \parencite{kumar2010structure, ugander2011anatomy}.
+A small world is characterized by its typical structure where most nodes can be reached from every other nodes by a small number of steps compared to a pure random graph of the same size.
+This is due to the fact that a small minority of \enquote{hub} nodes posses a disproportionate number of links, providing a global bridge between smaller, more strongly interconnected local clusters \parencite{barabasi2004linked}.
 
-%\subsection{}    
-%    \enquote{While much of the literature on networks treats the topological features of social structure as given quantities, networks do not emerge \emph{ex nihilo}, but are endogenously formed}
+    This structure has traditionally been known for information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal account of strength of weak ties.
+However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{banos2013diffusion, centola2007complex}.
+Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network.
+This is due to the fact that such hubs require a much higher number of active neighbors to adopt a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such controversial innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449}.
+Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.
+
+    Moreover, especially for the case of misinformation and its corrections, a simple contagion (of misinformation) and a complex contagion (of correction messages) may simultaneously affect a local-level attitudinal composition of one's neighbors \parencite[i.e., those who endorse and believe misinformation vs.
+those who do not: e.g.,][]{campbell2013complex}.
+Last but not least, all of aforementioned factors are endogenously determined through prior states of networks and their topological properties over time.
+As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and plausible counterfactuals.
+Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449}.
+For this reason, a rigorous empirical test of such factors is often practically impossible for observational studies despite its scientific and practical importance.
 

### 2018-02-15 manuscript_1.0.tex
started drafting method

@@
 
-\keywords{Misinformation, fake news, correction, simple contagion, complex contagion, agent-based simulations}
+\keywords{Misinformation, fake news, correction, simple contagion, complex contagion, exponential random graph model, agent-based simulations}
 
@@
 
-\note{Word count: 3599 words \\ %\quickwordcount \\
+\note{Word count: 4431 words \\ %\quickwordcount \\
     Draft date: \today \\
@@
 
-\section{A Social Context of Misperceptions and Corrections: Simple vs. Complex Contagion}
+\section{A Social Context of Misinformation and Corrections: Simple vs. Complex Contagions}
 
   People's perceptions and behaviors are likely to be shaped by their social contacts \parencite{lazer2010coevolution, centola2007complex}, and therefore perceptions and behaviors may spread within social networks \parencite[e.g.,][]{bond_61million}.
-Indeed, a non-negligible number of prior accounts of partisan misperceptions and fake news on social networks connects this idea to possible mechanisms of misinformation \emph{spreading}  \parencite[e.g.,][]{del2016spreading, Bakshy_2012}.
-The most simplest form of those accounts posits that online social networks provide one of the ideal settings of a spread of partisan misinformation and fake news.
+Indeed, a non-negligible number of prior accounts of partisan misinformation and fake news on social networks connects this idea to possible mechanisms of misinformation propagation and \emph{spreading}  \parencite[e.g.,][]{del2016spreading, Bakshy_2012}.
+The most simplest form of those accounts posits that online social networks provide one of the ideal settings for partisan misinformation and fake news to be spread within such networks.
 Many of the partisan rumors and fake news tend to be richer in their \enquote{novelty} \parencite{wu2007novelty} regardless of its veracity and informational value.
@@
 
-    Moreover, due to inherent partisan motivated directionality, the threshold of actually \emph{adapting} such a false yet pro-attitudinal claim (i.e., believing attitudinally congruent misinformation) may also exhibit similar low-threshold properties, although the actual threshold for believing misinformation would be bit higher compared to that of mere exposure and awareness \parencite[e.g.,][]{Monsted_plos2017}, and also subject to some individual differences \parencite[e.g.,][]{weeks2015emotions}.
+    Moreover, due to inherent partisan motivated directionality, the threshold of actually \emph{adapting} such a false yet pro-attitudinal claim (i.e., believing attitudinally congruent misinformation) may also exhibit similar low-threshold properties, although the actual threshold for believing misinformation would be bit higher compared to that of mere exposure and awareness \parencite[e.g.,][]{Monsted_plos2017}, and also subject to some individual differences \parencite[e.g.,][]{weeks2015emotions, flynn2017nature}.
 As previously suggested, people tend to directionally process political information \parencite{taber2006}, and they tend to easily remember and recall attitudinally-consistent information than uncongenial ones.
-Therefore, at least for citizens who find a given misinformation to be congenial to their prior partisan identities, \emph{adapting} such false yet pro-attitudinal claims also does not require high number of repeated exposure nor independent, multiple exposure to different sources supporting such claims.
+Therefore, at least for citizens who find given misinformation to be congenial to their partisan priors, \emph{adapting} such false yet pro-attitudinal claims also does not require high number of repeated exposure nor independent, multiple exposure to different sources supporting such claims.
 Indeed, many of the prior empirical studies support this perspective \parencite[e.g.,][]{garrett2016driving, kuklinski2000misinformation, flynn2017nature}.
 
-    In contrast, there are reasons to believe why the effectiveness of fact-checking and corrective messages would be different from that of a simple contagion of (mis)information.
-An adoption of a new perspective that contradicts to one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion,} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple exposures}, in order to be accepted and further spread into a given network.
+    In contrast, there are reasons to believe why the effectiveness of fact-checking and corrective messages would be different from that of a simple contagion of misinformation.
+An adoption of a new perspective that contradicts with one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple number of exposures}, endorsing such message in order to be accepted and further spread into a given network.
 This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2011dynamics, larson2016social, siegel2009social}.
 
-    Moreover, such complex contagion dynamics surrounding correction messages are also likely to be dependent upon the attitudinal composition of one's local network; the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{believe} misinformation) tend to discourages their neighbors to adopt corrections, whereas the number of one's neighbors who are already activated would increase one's susceptibility to adopt new perspective given exposure to correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}.
+    Moreover, such complex contagion dynamics surrounding correction messages are also likely to be dependent upon the attitudinal composition of one's local network.
+For the case of a adoption of fact-checking and corrective messages, the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{endorse} false belief based on misinformation) tend to discourages their neighbors to adopt a correction, whereas the number of one's neighbors who are already activated (e.g., those who do not believe misinformation anymore) would increase one's susceptibility to adopt the correction given exposure to such correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}.
 Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by one's neighbors, therefore relative distribution of one's neighbors (in terms of supporters vs.
 opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2011dynamics, friedkin2001norm}.
-This further implies that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite{friedkin2001norm}.
-Indeed, there exits a considerable support for this perspective, showing that different network topologies \parencite[e.g.,][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{  Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs.
-opponents regarding a given attitude or a behavior being spread in a network.} \parencite[e.g.,][]{levitan2008resistance, larson2016social, gonzalez2011dynamics} may produce different attitudinal and behavioral consequences, further suggesting that some network structures are more prone to generating cascades and adoptions than others.
+This further means that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite[e.g.,][]{friedkin2001norm}.
+Indeed, there exits a considerable support for this perspective, such that different network topologies \parencite[][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{  Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs.
+opponents regarding a given attitude or a behavior being spread in a network.} \parencite[][]{levitan2008resistance, larson2016social, gonzalez2011dynamics} may produce different attitudinal and behavioral consequences for social influence.
+This further implies that some network structures are more prone to generating cascades and adoptions than others.
 
@@
 
-  All in all, prior empirical evidence and theoretical perspectives convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level contagion dynamics.
+  All in all, prior empirical evidence and theoretical perspectives convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level propagation dynamics.
 Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, while ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation.
-In contrast, an adoption of corrective message requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition -- similar to controversial innovations \parencite{centola2007complex, Centola2010Sience, gonzalez2011dynamics}.
+In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2011dynamics}.
 Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experiment contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.
@@
 
-  If the diffusion of (mis)information and adoption of corrective messages may non-trivially dependent upon a structure of a given network and its attitudinal composition, then how a typical (online) social network is structured in terms of its topological features, and how pervasive is \enquote{attitudinal} homophily on such a social network?
+  If the diffusion of (mis)information and adoption of corrective messages may non-trivially dependent upon a structure of a given network and its attitudinal composition, then how a typical (online) social network is structured in terms of its topological features, and how pervasive is \enquote{attitudinal} homophily, as \emph{the} critical factor determining attitudinal compositions, on such a social network?
 How such structural features affect the overall diffusion dynamics empirically?
@@
 
-    A frequent and recurring theme for (attitudinal) a makeup of citizens' social networks and its consequences, among scholars and general publics alike, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulate themselves from competing viewpoints and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, del2016spreading}.
+    A frequent and recurring theme for an attitudinal makeup of citizens' social networks and its consequences, especially among general publics, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulate themselves from competing viewpoints and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, del2016spreading}.
 Yet, as \citeauthor{Garrett2017distraction} (\citeyear{Garrett2017distraction}) puts it, \enquote{there is ample evidence that \emph{exposure} [emphasis added] echo chambers are not a typical part of Internet users' experience} (p.
 370).
-Most of citizens are appear to be embedded in sufficiently diverse social networks, showing a substantial level of exposure to political difference online \parencite[e.g.,][]{Bakshy1130, messing2014selective} and offline \parencite[e.g.,][]{huckfeldt2004disagreement}.
+Most of citizens are appear to be embedded in sufficiently diverse social networks, showing a substantial level of exposure to political difference in online \parencite[e.g.,][]{Bakshy1130, messing2014selective} and in offline \parencite[e.g.,][]{huckfeldt2004disagreement}.
 More importantly, those studies do not find compelling evidence that ordinary citizens' network constructions are primarily driven by purposive political homophily that limit their exposure to only congenial political perspectives \parencite{song2015uncovering, lazer2010coevolution}.
@@
 
-    However, one should also bear in mind that the evidence concerning mere \emph{exposure} to counter-attitudinal messages does not provide enough indications of how such messages are actually cognitively processed and interpreted \parencite[e.g.,][]{nyhan2017taking, Garrett2017distraction}.
-What we know about citizens' exposure to disagreement in their social networks typically has relied on observational evidence, either based on participants' self-reports regarding their patterns of social interactions \parencite[e.g.,][]{song2015uncovering, lazer2010coevolution} or based on messages posted (sometimes along with engagement data such as \enquote{likes} or \enquote{shares}) in online social networks \parencite[e.g.,][]{Bakshy1130}.
-While such evidence \emph{do} suggests that citizens are indeed exposed to competing viewpoints in their daily lives, they are typically rather silent about how an individuals actually process and interpret such information at the time of exposure.\footnote{  Recent studies try to overcome problems of typical observational studies by relying on time-stamped, detailed digital footprint data \parencite[e.g.,][]{guess2018selective, margolin2017}, yet such studies also suffer from similar weakness, in that they cannot provide strong causal evidence concerning individuals' actual cognitive processing of counter-attitudinal messages beyond what is available in observational data.} As experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility of more balanced judgments.
+    However, one should also bear in mind that the evidence concerning \emph{exposure} to counter-attitudinal messages does not provide sufficient evidence of how such messages are actually cognitively processed and interpreted under such a situation \parencites[e.g., see "engagement echo chamber" discussion in][]{Garrett2017distraction}[also, see][]{nyhan2017taking}.
+What we know about citizens' exposure to disagreement in their social networks typically has relied on observational evidence, either based on participants' self-reports of their patterns of social interactions concerning their immediate social environment \parencite{huckfeldt2004disagreement} or based on a comprehensive mapping of their interactions in a well-defined, relatively closed social system \parencite[e.g.,][]{song2015uncovering, lazer2010coevolution}.
+Sometimes, scholars also rely on digitally available communication patterns such as messages posted in online social networks \parencite[e.g.,][]{margolin2017}, along with engagement indicators such as \enquote{likes} or \enquote{shares} \parencite[e.g.,][]{Bakshy1130} or based on a detailed digital footprint data such as website access data \parencite[e.g.,][]{guess2018selective}.
+While such evidence \emph{do} suggests that citizens are indeed frequently exposed to competing political perspectives in their daily lives, such evidence is typically rather silent about how individuals actually process and interpret such information given exposure.
+As experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility of more balanced judgments.
 Experimental evidence in this regard can provide more detailed pictures of how such (counter-attitudinal) messages are actually selected, processed, and adopted by an individual given exposure settings \parencite[e.g., ][]{messing2014selective, nyhan2017taking, Wood2018}.
@@
     Similarly to attitudinal composition of citizen's social networks, the question of how exactly the structure of citizens' social networks exhibits certain topological properties have attracted considerable interests among scholars.
-Prior observations on this topic suggests that large-scale (online) networks tend to exhibit \enquote{small-world} like properties \parencite{kumar2010structure, ugander2011anatomy}.
+Prior observations on this topic suggests that large-scale (online) social networks tend to exhibit \enquote{small-world} like properties \parencite{kumar2010structure, ugander2011anatomy}.
 A small world is characterized by its typical structure where most nodes can be reached from every other nodes by a small number of steps compared to a pure random graph of the same size.
@@
 Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network.
-This is due to the fact that such hubs require a much higher number of active neighbors to adopt a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such controversial innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449}.
-Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.
+This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449}.
+Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.
 
@@
 those who do not: e.g.,][]{campbell2013complex}.
-Last but not least, all of aforementioned factors are endogenously determined through prior states of networks and their topological properties over time.
-As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and plausible counterfactuals.
+Last but not least, all of aforementioned factors are endogenously determined through prior states of networks over time in evolving dynamic network.
+As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and a number of plausible counterfactuals.
 Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449}.
 For this reason, a rigorous empirical test of such factors is often practically impossible for observational studies despite its scientific and practical importance.
+
+\section{A Current Investigation: Mathematical Modeling of Complex Diffusion Dynamics}
+
+  Adopting a well-known class of an epidemic model of virus infection and recovery, this study used stochastic network-based mathematical models to simulate contagion dynamics of misinformation and its corrections.
+More detailed methods, including model parameterization, simulation, and more detailed analyses of simulation model results, are provided in the supplementary appendix.
+Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing sources of empirical data.
+Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics but rather conveniently chosen, it nevertheless provides reasonable starting point for formally model more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics.
+All simulation models were based on the \emph{EpiModel} R software package.
+
+    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new (CITE HERE).
+Yet prior studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems (CITE HERE).
+While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure.
+Our approach was to use exponential random graph models, or ERGM, to simulate a series of dynamically evolving networks of different topological properties (see also below section XXX for a more detail).
+The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles, and for simulation context, offers a convenient yet powerful tool for independently manipulating topological structures of a network based on such generative mechanisms.
+In our present application, we therefore simulated a baseline model (based on available empirical evidence) and several counterfactual models (that differ in some key parameters) of network evolution models, and further submit them to different stochastic models of misinformation propagations vs.
+corrective message adoptions.
+Our focus here is therefore on the role of varying level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs.
+complex contagion dynamics at population level in conjunction with network topologies.
+
+    Therefore, our approach differ from a number of prior studies that have used similar simulation-based approach in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
+complex contagions) interact to yield propagation dynamics at the population level.
+Arguably, this approach obviously still greatly simplifies the complexity of the real world.
+However, in doing so, it provides an analytical tool for identifying the effects topologies and attitudinal compositions of a network, and the resulting implications for the simple vs.
+complex diffusion dynamics of misinformation and corrections in a typical social network.
 

### 2018-02-17 EpiModel.R
refit network models
-also update on drafts until section "A Stochastic Dynamic Model of Networks"

@@ -80,19 +80,19 @@ formation[[1]] <- ~ edges + nodefactor("pid")
 formation[[2]] <- ~ edges + nodefactor("pid") + concurrent + degree1.5
 
 ## formation model for scale-free network
-formation[[3]] <- ~ edges + nodefactor("pid") + concurrent + degrange(2:8)
+formation[[3]] <- ~ edges + nodefactor("pid") + degrange(0) + concurrent + triangle
 
 ## formation model for more realistic network, conditioned by party identification
 ## crucial difference of this model is nodematch("pid"),
 ## which assumes partisan homophily in network formations
-formation[[4]] <- ~ edges + nodematch("pid") + nodefactor("pid") + concurrent + degrange(2:8)
+formation[[4]] <- ~ edges + nodematch("pid") + nodefactor("pid") + degrange(0) + concurrent + triangle
 
 ## for nodematch target statistics: from ANES 2008-2009 Panel Study
 ## see setups.R file for detail.
 
 ## target stats for formation statistics, each imply for
 ## edge (density 0.66 * n/2 = 1500),
-## nodefactor (mean degree of 0.3 vs 0.3 in Dem vs. Rep group = 0.3*nR),
+## nodefactor (mean degree of 0.66 vs 0.66 in Dem vs. Rep group = 0.3*nR),
 ## nodematch (assuming 70% within the same pid group,
 ## the product of the number of edges and the probability of a same-group edge = 1500*0.7 = 1050),
 ## for concurrent (separately by pid), assume 35% of ties would have more than two edges,
@@ -101,13 +101,10 @@ formation[[4]] <- ~ edges + nodematch("pid") + nodefactor("pid") + concurrent + 
 ## get.target.stats(nD, nR, 0.66, 0.73, 0.66, 0.26)
 target.stats[[1]] <- c(792, 753.72)
 target.stats[[2]] <- c(792, 753.72, 438, 2025)
-target.stats[[3]] <- c(792, 753.72, 285, 280, 72.675, 38.745, 27.605, 17.5, 11.38, 5.3)
-target.stats[[4]] <- c(792, 578.16, 799.4, 285, 280, 72.675, 38.745, 27.605, 17.5, 11.38, 5.3)
+target.stats[[3]] <- c(792, 753.72, 205.92, 518.76, 2)
+target.stats[[4]] <- c(792, 578.16, 753.72, 205.92, 518.76, 2)
 
 ## dissolution model
[…]

### 2018-02-17 dev/setups.R

@@ -7,7 +7,7 @@
 
 require(haven)
 require(data.table)
-anespanel0809 <- read_spss("anes2008_2009panel.sav")
+anespanel0809 <- read_spss("dev/anes2008_2009panel.sav")
 setDT(anespanel0809)
 
 ## "w9l1" and "w9l3" = ego partisanship

### 2018-02-17 manuscript_1.0.tex
more tweak on network topology
- Probably settle on this ones...
- Also updates on draft

@@
 \usepackage{microtype}
+\usepackage{caption}
+\usepackage{subcaption}
+
 \usepackage{graphicx}
@@
 \usepackage{times}
-\renewcommand{\footnotesize}{\normalsize} % use 12pt for footnotes
+\renewcommand{\footnotesize}{\small} % use 11pt for footnotes
 \usepackage[doublespacing]{setspace} % single space for footnotes
+\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
 % this command put all footnotes to endnote at the end of the paper
-\usepackage{endnotes}
-\let\footnote\endnote
+%\usepackage{endnotes}
+%\let\footnote\endnote
 
@@
 
-\note{Word count: 4431 words \\ %\quickwordcount \\
+\note{Word count: 5339 words \\ %\quickwordcount \\
     Draft date: \today \\
@@
 An adoption of a new perspective that contradicts with one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple number of exposures}, endorsing such message in order to be accepted and further spread into a given network.
-This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2011dynamics, larson2016social, siegel2009social}.
+This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2017decoding, larson2016social, siegel2009social}.
 
@@
 Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by one's neighbors, therefore relative distribution of one's neighbors (in terms of supporters vs.
-opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2011dynamics, friedkin2001norm}.
+opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2017decoding, friedkin2001norm}.
 This further means that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite[e.g.,][]{friedkin2001norm}.
 Indeed, there exits a considerable support for this perspective, such that different network topologies \parencite[][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{  Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs.
-opponents regarding a given attitude or a behavior being spread in a network.} \parencite[][]{levitan2008resistance, larson2016social, gonzalez2011dynamics} may produce different attitudinal and behavioral consequences for social influence.
+opponents regarding a given attitude or a behavior being spread in a network.} \parencite[][]{levitan2008resistance, larson2016social, gonzalez2017decoding} may produce different attitudinal and behavioral consequences for social influence.
 This further implies that some network structures are more prone to generating cascades and adoptions than others.
@@
 Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, while ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation.
-In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2011dynamics}.
+In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2017decoding}.
 Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experiment contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.
@@
     This structure has traditionally been known for information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal account of strength of weak ties.
-However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{banos2013diffusion, centola2007complex}.
+However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{banos2013diffusion, centola2007complex, zhao2010weak}.
 Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network.
-This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449}.
+This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449, zhao2010weak, gonzalez2017decoding}.
 Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.
@@
 As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and a number of plausible counterfactuals.
-Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449}.
+Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449, gonzalez2017decoding}.
 For this reason, a rigorous empirical test of such factors is often practically impossible for observational studies despite its scientific and practical importance.
@@
 More detailed methods, including model parameterization, simulation, and more detailed analyses of simulation model results, are provided in the supplementary appendix.
-Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing sources of empirical data.
-Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics but rather conveniently chosen, it nevertheless provides reasonable starting point for formally model more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics.
-All simulation models were based on the \emph{EpiModel} R software package.
+Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing nationwide representative surveys concerning citizen's social network \parencite[American National Election Study 2008–2009 Panel Survey:][]{ANES2009} and exposure to fake news during 2016 presidential election \parencite{pewfakenews}.
+Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics within a social network but rather conveniently chosen,\footnote{  It should be acknowledged that those sources of data is suboptimal in number of regards: (a) social network data is confined to cross-sectional, egocentric network data, and (b) they do not come from the identical data generating process covering the same periods of observations (e.g., networks recoded in 2009 has little or no bearing for fake news exposure in 2016).
+However, research indicates the structural compositions of citizens' core discussion network are reasonably stable over time, albeit actual responses in typical surveys are subject to a number of survey-context related factors \parencite{byungkyu2017important} or changes in one's life contexts \parencite{small2015stable}.
+Also, since most of the prior applications concerning fake news and misinformation from observational studies typically look at representative samples, we intentionally have chosen those data since these types of data are more commonly used in the social sciences, which provide best-available up-to-date relevant information for the current application.
+See also \textit{A Stochastic Dynamic Model of Networks} section below and supplemental appendix for a detail.} it nevertheless provides reasonable starting point for formally model more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics.
+All simulation models were based on the \emph{EpiModel} R software package \parencite{epimodel}.
 
-    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new (CITE HERE).
-Yet prior studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems (CITE HERE).
+    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, acemoglu2010spread, zhao2010weak}.
+Yet these studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems \parencite[e.g., see][]{zhao2010weak}.
 While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure.
-Our approach was to use exponential random graph models, or ERGM, to simulate a series of dynamically evolving networks of different topological properties (see also below section XXX for a more detail).
-The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles, and for simulation context, offers a convenient yet powerful tool for independently manipulating topological structures of a network based on such generative mechanisms.
+Our approach was to use an exponential random graph model, or ERGM framework \parencite{robins2007introduction, morris2008specification}, to simulate a series of dynamically evolving networks of different topological properties (see also below section XXX for a more detail).
+The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}.
 In our present application, we therefore simulated a baseline model (based on available empirical evidence) and several counterfactual models (that differ in some key parameters) of network evolution models, and further submit them to different stochastic models of misinformation propagations vs.
@@
 
-    Therefore, our approach differ from a number of prior studies that have used similar simulation-based approach in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
+    Therefore, our approach differs from prior studies that have used similar simulation-based approaches in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
 complex contagions) interact to yield propagation dynamics at the population level.
@@
 
+\subsection{A Stochastic Dynamic Model of Networks}
+
+  In order to explore role of network topologies in diffusion dynamic in evolving networks, we require to explicitly specify a network structure and how such structure evolves over time according to some underlying generative principles.
+To this end, we first model formation and dissolution of citizens' political discussion ties over time (through which misinformation and corrections are communicated) using separable temporal ERGMs (STERGMs), using \enquote{summary statistics} drawn from egocentric network samples \parencite{krivitsky2017inference}.
+That is, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of egocentrically sampled information from 2009 ANES data.\footnote{ Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties.
+See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or summary target statistics, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans excluding Independents (i.e., main effect of partisanship), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{  In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
+Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners.
+Since in 2009 ANES respondents theoretically name up to three alters, this translate into egonetwork density of 0.66 (=1.975/3).
+For the main effect of partisanship, the marginal distribution of number of named alters by egos did not differ by partisanship, meaning that the expected mean degree for each partisan group is proportional to observed density and the size of each group.
+For political homophily, data indicate that 23\% of reported discussion ties exist across Democrats and Republicans.
+For degree distribution statistic, we supply a range of plausible yet arbitrary values since 2009 ANES does not have summary network size measure.
+See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, which consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans.
+In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks.
+We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective "unfriending":][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties.
+    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several counterfactual models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{  This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model.
+Below Figure \ref{fig:Figure1} shows the simulated cross-sectional networks from each of the network topologies, and Table \ref{tab:Table1} reports some key descriptive statistics from each of the networks.
+\begin{center} -- Table \ref{tab:Table1} and Figure \ref{fig:Figure1} about here -- \end{center}
+
+% Table 1.
+\begin{table}[!htbp] \centering 
+  \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
+  \label{tab:Table1} 
+\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \textbf{E-R} & \textbf{Chain} &  \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
+\hline \\[-1.8ex] 
+Density & 0.000272 & 0.000275 & 0.000274 & 0.000268 \\ 
+Mean degree & 1.305 & 1.318 & 1.315 & 1.287 \\ 
+Max degree & 10.0 & 4.0 & 10.0 & 10.0 \\ 
+Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
+Mean distance & 3.0 & 2.4 & 3.6 & 3.4 \\ 
+Homophilous ties & 50.7\% & 47.3\% & 51.2\% & 74.6\% \\ 
+Heterophilous ties & 49.3\% & 52.7\% & 48.8\% & 25.4\% \\ 
+\hline \\[-1.8ex]  
+\end{tabular} 
+\begin{tablenotes}[para,flushleft]
+\small \vspace{0.15in}
+\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily. 
+\end{tablenotes}
+\end{table}
+
+% Figure 1: Plots of static (cross-sectional) networks from simulations    
+\begin{figure}
+\captionsetup[figure]{labelfont={bf,it}}
+\captionsetup[subfigure]{labelfont=bf,textfont=normalfont,singlelinecheck=on}
+    \centering
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots1.pdf} 
+        \caption{Erdos-Renyi random network}
+        \label{fig1:random}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots2.pdf} 
+        \caption{Chain network} \label{fig1:tree}
+    \end{subfigure}
+
+    \vspace{1cm}
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots3.pdf} 
+        \caption{Small-world network absent homophily} \label{fig1:nohomophily}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots4.pdf} 
+        \caption{Baseline small-world network} \label{fig1:smallworld}
+    \end{subfigure}
+
+    \vspace{1cm}
+    \captionsetup{format=hang}
+    \caption{A cross-sectional view of simulated networks from different network topologies.
+Colored nodes represent nodes that have at least one connection with their neighbor (Red = Republicans, Blue = Democrats) while isolates at given time point was suppressed in visualization.
+A Erdos-Renyi (ER) random network (a) assumes a homogeneous probability of creating and dropping ties across all nodes conditional on observed density.
+A chain-like network (b) has more longer chains than the ER random network while lacks triangle-like structure due to constrains on degrees (less than three).
+While two small-world network has more star-like structure than others, our baseline small-world network (d) is more homophilous than competing specification in (c), as can be seen in Table \ref{tab:Table1}.} \label{fig:Figure1}
+\end{figure}
+
+\subsection{Misinformation Transmission and Progression}
+
+\subsection{Corrective Message Exposure and a Recovery from Misperception}
+
 \printbibliography
-\newpage
-\begingroup
-\parindent 0pt
-\parskip 1ex
-\def\enotesize{\normalsize}
-\theendnotes
-\endgroup
+%\newpage
+%\begingroup
+%\parindent 0pt
+%\parskip 1ex
+%\def\enotesize{\normalsize}
+%\theendnotes
+%\endgroup
 \end{document}

### 2018-02-17 EpiModel.R

@@ -31,8 +31,13 @@ ncores <- parallel::detectCores(logical = F)
 
 ### Step 1: Construct network ###
 # Construct a random network
+require(igraph)
 set.seed(12345)
-sw.net <- network.initialize(n = n, directed = FALSE) ## or as.network(rgraph(n, 1, 0.5, mode = "graph"), directed = F)
+sw.net <- list()
+sw.net[[1]] <- igraph::sample_gnm(n = n, m = 792) %>%  intergraph::asNetwork(.) ## n = node, m = edge
+sw.net[[2]] <- igraph::sample_smallworld(1, n, p = 0, nei = 1, loops = FALSE, multiple = FALSE) %>%  intergraph::asNetwork(.) ## lattice network, since rewiring prob is zero
+sw.net[[3]] <- igraph::sample_smallworld(1, n, p = .3, nei = 2, loops = FALSE, multiple = FALSE) %>%  intergraph::asNetwork(.) ## small-world
+sw.net[[4]] <- igraph::sample_smallworld(1, n, p = .3, nei = 2, loops = FALSE, multiple = FALSE) %>%  intergraph::asNetwork(.) ## small-world
 
 # set some initial attributes
 ## partisanship -- one of the core mechanisms of directional motivation
@@ -61,9 +66,11 @@ accuracy_motive <- rescale(accuracy_motive, to = c(0,1))
 sophistication <- rescale(sophistication, to = c(0,1))
 
 ## set network attributes
-sw.net <- network::set.vertex.attribute(sw.net, "pid", pid)
-sw.net <- network::set.vertex.attribute(sw.net, "accuracy_motive", accuracy_motive)
-sw.net <- network::set.vertex.attribute(sw.net, "sophistication", sophistication)
+for (i in 1:4) {
+  sw.net[[i]] <- network::set.vertex.attribute(sw.net[[i]], "pid", pid)
+  sw.net[[i]] <- network::set.vertex.attribute(sw.net[[i]], "accuracy_motive", accuracy_motive)
+  sw.net[[i]] <- network::set.vertex.attribute(sw.net[[i]], "sophistication", sophistication)
+}
 
 ## ---------------------------- ##
 ## Step 1: fit network dynamics ##
@@ -77,15 +84,15 @@ coef.diss <- list()
 formation[[1]] <- ~ edges + nodefactor("pid")
 
 ## formation model for tree-like network (absence of triangles)
[…]

### 2018-02-28 manuscript_1.0.tex
Revised networks and codes, working on SEIR dynamic codes
- draft updates until EI progression module

@@
 % declare documents and packages
-\documentclass[man, 12pt, a4paper, noextraspace]{apa6}
+\documentclass[man, 12pt, a4paper, nolmodern, noextraspace]{apa6}
 \usepackage[T1]{fontenc}
@@
 \usepackage{subcaption}
-
 \usepackage{graphicx}
@@
 \usepackage[doublespacing]{setspace} % single space for footnotes
-\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
+%\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
 % this command put all footnotes to endnote at the end of the paper
-%\usepackage{endnotes}
-%\let\footnote\endnote
+\usepackage{endnotes}
+\let\footnote\endnote
 
@@
 
-\note{Word count: 5339 words \\ %\quickwordcount \\
+\note{Word count: 5183 words \\ %\quickwordcount \\
     Draft date: \today \\
@@
 One of the most dramatic changes in the news environment in recent decades involves the role social networking sites (SNS) such as Facebook and Twitter play as a primary source of news outlets.
-Not only citizens' news consumptions are increasingly driven by such online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination on those platforms by sharing news contents with their peers \parencite[e.g.,][]{shearer2017news, lee2017people}.
+Not only citizens' news consumptions are increasingly driven by such online sources \parencite{shearer2017news}, but it also appears that citizens themselves are actively participating in news dissemination on those platforms by sharing news with their peers \parencite[e.g.,][]{shearer2017news, lee2017people}.
 
@@
 
-      Another line of studies based on a dual process theory of human cognitive processing and memory suggests that attitudinally-congruent misinformation creates automatic and strong affective responses -- therefore automatically and effortlessly activated in one's memory -- whereas attitudinally incongruent correction messages rarely produce such responses.
-Due to such asymmetrical nature, people have to rely on more deliberative, strategic search processes (which require significant cognitive resources) to recall attitudinally inconsistent correction messages and incorporate them into relevant judgments \parencite{thorson_2016, Lewandowsky_2012PSPI}.
-Also, since misinformation tends to form a coherent mental model based on one's partisan schema and stereotypes \parencite[e.g.,][]{garrett2013undermining}, people tend to fill any gaps caused by corrections (that invalidate some parts of the existing mental model) with flawed but attitudinally congruent misinformation that is still readily accessible in their memory \parencite{Lewandowsky_2012PSPI}.
+      Another line of studies based on a dual process theory of human cognitive processing and memory suggests that attitudinally-congruent misinformation tends to form a coherent mental model based on one's partisan schema and stereotypes \parencite[e.g.,][]{garrett2013undermining, Lewandowsky_2012PSPI}.
+Therefore, people tend to fill any gaps caused by corrections (that invalidate some parts of the existing mental model) with flawed but attitudinally congruent misinformation that is still readily accessible in their memory \parencite{Lewandowsky_2012PSPI}.
 Studies also find that this effect is much more likely when correction messages do not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}, when the perceived veracity of initial misinformation is high \parencite[due to fluency bias in one's cognitive processing:][]{Lewandowsky_2012PSPI}, or when individuals can generate counter-arguing reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}.
@@
 This observation is indeed much warranted, as most of the previous studies concerning misinformation and the effect of fact-checking messages are conducted in an experimental context with a single-shot, \emph{asocial} correction message from media professionals and fact-checking organizations \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining,weeks2015emotions}.
-Much of the literature on partisan selective exposure and political discussion networks already point that social contexts of which an individual is exposed to counter-attitudinal messages may have a powerful consequence on how such messages are interpreted and processed \parencite{messing2014selective, levitan2008resistance}.
-There is also a suggestive evidence that fact-checking and corrective messages from one's peers in their social networks -- what we would call a \enquote{social correction} -- are more likely to, if not equally, be effective in reducing misperceptions \parencite[e.g.,][]{margolin2017, bode2017see}.
+There is also a suggestive evidence that fact-checking and corrective messages from one's peers in their social networks -- what we would call a \enquote{social correction} -- are more likely to be effective in reducing misperceptions \parencite[e.g.,][]{margolin2017, bode2017see}.
 In what follow, we review several theoretical accounts of such \emph{socially-based} correction messages on misinformation and fake news.
@@
 
-  If the diffusion of (mis)information and adoption of corrective messages may non-trivially dependent upon a structure of a given network and its attitudinal composition, then how a typical (online) social network is structured in terms of its topological features, and how pervasive is \enquote{attitudinal} homophily, as \emph{the} critical factor determining attitudinal compositions, on such a social network?
+  If the diffusion of (mis)information and adoption of corrective messages may non-trivially dependent upon a structure of a given network and its attitudinal composition, then how a typical (online) social network is structured in terms of its topological features, and how pervasive is \enquote{attitudinal} homophily, as \emph{the} critical factor determining attitudinal compositions of one's social network?
 How such structural features affect the overall diffusion dynamics empirically?
-This is indeed important questions to ask, since the flow of information (either misinformation or its correction) and its adoption are ultimately structured by how individuals are connected with each other in a given network.
-However, it is surprisingly difficult to establish convincing evidence of the impact of structural properties of a given network and its attitudinal composition in complex contagion dynamics using purely observational and experimental approaches.
+This is indeed important questions to ask, yet it is surprisingly difficult to establish convincing evidence of the impact of such factors in complex contagion dynamics using purely observational and experimental approaches.
 
@@
     Similarly to attitudinal composition of citizen's social networks, the question of how exactly the structure of citizens' social networks exhibits certain topological properties have attracted considerable interests among scholars.
-Prior observations on this topic suggests that large-scale (online) social networks tend to exhibit \enquote{small-world} like properties \parencite{kumar2010structure, ugander2011anatomy}.
-A small world is characterized by its typical structure where most nodes can be reached from every other nodes by a small number of steps compared to a pure random graph of the same size.
+Prior observations on this topic suggests that (online) social networks tend to exhibit \enquote{small-world} like properties \parencite{kumar2010structure, ugander2011anatomy}, where most nodes can be reached from every other nodes by a small number of steps.
 This is due to the fact that a small minority of \enquote{hub} nodes posses a disproportionate number of links, providing a global bridge between smaller, more strongly interconnected local clusters \parencite{barabasi2004linked}.
-
 This structure has traditionally been known for information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal account of strength of weak ties.
-However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{banos2013diffusion, centola2007complex, zhao2010weak}.
+However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{gonzalez2017decoding, centola2007complex, zhao2010weak}.
 Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network.
 This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449, zhao2010weak, gonzalez2017decoding}.
+
     Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.
-
-    Moreover, especially for the case of misinformation and its corrections, a simple contagion (of misinformation) and a complex contagion (of correction messages) may simultaneously affect a local-level attitudinal composition of one's neighbors \parencite[i.e., those who endorse and believe misinformation vs.
+Moreover, especially for the case of misinformation and its corrections, a simple contagion and a complex contagion may simultaneously affect a local-level attitudinal composition of one's neighbors \parencite[i.e., those who endorse and believe misinformation vs.
 those who do not: e.g.,][]{campbell2013complex}.
-Last but not least, all of aforementioned factors are endogenously determined through prior states of networks over time in evolving dynamic network.
-As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of an given network often necessitates systematic comparisons between the observed network and a number of plausible counterfactuals.
-Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, Centola2007449, gonzalez2017decoding}.
-For this reason, a rigorous empirical test of such factors is often practically impossible for observational studies despite its scientific and practical importance.
+Last but not least, all of aforementioned factors are endogenously determined over time in evolving dynamic network.
+As a consequence, a proper identification regarding the exact impacts of its attitudinal composition and structural properties of a given network often necessitates systematic comparisons between the observed network and a number of plausible counterfactuals.
+Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, gonzalez2017decoding}.
+For this reason, a rigorous empirical test of such factors is often impossible for observational studies despite its scientific and practical importance.
 
@@
 More detailed methods, including model parameterization, simulation, and more detailed analyses of simulation model results, are provided in the supplementary appendix.
-Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing nationwide representative surveys concerning citizen's social network \parencite[American National Election Study 2008–2009 Panel Survey:][]{ANES2009} and exposure to fake news during 2016 presidential election \parencite{pewfakenews}.
-Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics within a social network but rather conveniently chosen,\footnote{  It should be acknowledged that those sources of data is suboptimal in number of regards: (a) social network data is confined to cross-sectional, egocentric network data, and (b) they do not come from the identical data generating process covering the same periods of observations (e.g., networks recoded in 2009 has little or no bearing for fake news exposure in 2016).
+Behavioral parameters governing the network structure and misinformation propagation dynamics were estimated from several best-available existing nationwide representative surveys concerning citizen's social networks \parencite[American National Election Study 2008–2009 Panel Survey:][]{ANES2009} and exposure to fake news during 2016 presidential election \parencite{pewfakenews,guess2018selective,allcott2017social}.
+Although these data sources were not specifically designed for obtaining the impact of (mis)information diffusion dynamics within a social network, it nevertheless provides a reasonable starting point for formally modeling more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics.\footnote{ It should be acknowledged that those sources of data is suboptimal in number of regards: (a) social network data is confined to cross-sectional, egocentric network data, and (b) they do not come from the identical data generating process covering the same periods of observations (e.g., networks recoded in 2009 has little or no bearing for fake news exposure in 2016).
 However, research indicates the structural compositions of citizens' core discussion network are reasonably stable over time, albeit actual responses in typical surveys are subject to a number of survey-context related factors \parencite{byungkyu2017important} or changes in one's life contexts \parencite{small2015stable}.
-Also, since most of the prior applications concerning fake news and misinformation from observational studies typically look at representative samples, we intentionally have chosen those data since these types of data are more commonly used in the social sciences, which provide best-available up-to-date relevant information for the current application.
-See also \textit{A Stochastic Dynamic Model of Networks} section below and supplemental appendix for a detail.} it nevertheless provides reasonable starting point for formally model more realistic network structures, on which we later further parameterizing the assumptions and mechanisms postulated in the previous discussions of complex diffusion dynamics.
-All simulation models were based on the \emph{EpiModel} R software package \parencite{epimodel}.
+Also, since most of the prior applications concerning fake news and misinformation from observational studies typically look at representative samples, we intentionally have chosen those data since these types of data are more commonly used in the social sciences, and provide best-available up-to-date relevant information for the current application.
+See also \textit{A Stochastic Dynamic Model of Networks} section below and supplemental appendix for a detail.} All simulation models were based on the \emph{EpiModel} R software package \parencite{epimodel}.
 
-    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, acemoglu2010spread, zhao2010weak}.
+    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, zhao2010weak}.
 Yet these studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems \parencite[e.g., see][]{zhao2010weak}.
 While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure.
-Our approach was to use an exponential random graph model, or ERGM framework \parencite{robins2007introduction, morris2008specification}, to simulate a series of dynamically evolving networks of different topological properties (see also below section XXX for a more detail).
-The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}.
-In our present application, we therefore simulated a baseline model (based on available empirical evidence) and several counterfactual models (that differ in some key parameters) of network evolution models, and further submit them to different stochastic models of misinformation propagations vs.
+Our approach was to use an exponential random graph model (ERGM) framework \parencite{robins2007introduction, morris2008specification} to simulate a series of dynamically evolving networks of different topological properties (see also below section \textit{A Stochastic Dynamic Model of Networks} for a more detail).
+The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a evolving network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}.
+In our present application, we simulated a baseline network evolution model based on available empirical evidence along with several counterfactual models that differ in their structural characteristics, and further submit them to different stochastic models of misinformation propagations vs.
 corrective message adoptions.
-Our focus here is therefore on the role of varying level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs.
+Our focus here is therefore on the role of varying network topologies and level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs.
 complex contagion dynamics at population level in conjunction with network topologies.
 
-    Therefore, our approach differs from prior studies that have used similar simulation-based approaches in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
+    Therefore, our approach differs from prior studies that have used similar simulation-based approaches in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values, where available, based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
 complex contagions) interact to yield propagation dynamics at the population level.
@@
 
-  In order to explore role of network topologies in diffusion dynamic in evolving networks, we require to explicitly specify a network structure and how such structure evolves over time according to some underlying generative principles.
-To this end, we first model formation and dissolution of citizens' political discussion ties over time (through which misinformation and corrections are communicated) using separable temporal ERGMs (STERGMs), using \enquote{summary statistics} drawn from egocentric network samples \parencite{krivitsky2017inference}.
-That is, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of egocentrically sampled information from 2009 ANES data.\footnote{ Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties.
-See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or summary target statistics, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans excluding Independents (i.e., main effect of partisanship), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{  In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
+  In order to explore role of network topologies in diffusion dynamic in evolving networks, we require to explicitly specify a generative principle of network structure and how such structure evolves over time.
+To this end, we first model formation and dissolution of citizens' political discussion ties over time through which misinformation and corrections are communicated.
+Using separable temporal ERGMs \parencite{krivitsky2017inference}, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of \enquote{summary statistics} drawn from egocentric network from 2009 ANES data.\footnote{  Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties.
+See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or summary target statistics, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{\label{note6}  In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
 Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners.
@@
 In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks.
-We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective "unfriending":][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties.
+We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective \enquote{unfriending}:][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties.
     In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several counterfactual models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{  This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model.
-Below Figure \ref{fig:Figure1} shows the simulated cross-sectional networks from each of the network topologies, and Table \ref{tab:Table1} reports some key descriptive statistics from each of the networks.
-\begin{center} -- Table \ref{tab:Table1} and Figure \ref{fig:Figure1} about here -- \end{center}
+Below Figure \ref{fig:Figure1} shows the simulated cross-sectional views of networks, and Table \ref{tab:Table1} reports key descriptive statistics for each of the networks in terms of their topological properties.
+\centerline{ -- Table \ref{tab:Table1} and Figure \ref{fig:Figure1} about here -- }
 
@@
 \hline \\[-1.8ex] 
-Density & 0.000272 & 0.000275 & 0.000274 & 0.000268 \\ 
-Mean degree & 1.305 & 1.318 & 1.315 & 1.287 \\ 
-Max degree & 10.0 & 4.0 & 10.0 & 10.0 \\ 
+Graph density & 0.000269 & 0.000268 & 0.000277 & 0.000272 \\ 
+Mean degree & 1.292 & 1.287 & 1.327 & 1.303 \\ 
+Max degree & 10.0 & 4.0 & 12.0 & 12.0 \\ 
 Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
-Mean distance & 3.0 & 2.4 & 3.6 & 3.4 \\ 
-Homophilous ties & 50.7\% & 47.3\% & 51.2\% & 74.6\% \\ 
-Heterophilous ties & 49.3\% & 52.7\% & 48.8\% & 25.4\% \\ 
+Mean distance & 2.2 & 2.2 & 4.5 & 3.4 \\ 
+Homophilous ties & 49.4\% & 50.5\% & 52.3\% & 68.5\% \\ 
+Heterophilous ties & 50.6\% & 49.5\% & 47.7\% & 31.5\% \\ 
 \hline \\[-1.8ex]  
@@
 
-\subsection{Misinformation Transmission and Progression}
+  Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models.
+We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamcics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies.
+We fit a series of SEIR (\enquote{suseptable - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.
 
-\subsection{Corrective Message Exposure and a Recovery from Misperception}
+\subsection{Misinformation Transmission}
+
+    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public.
+However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times per month on average, and among them 41.8\% of all visits originate from social media traffics.
+Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% inidivduals who visited fake news websites, 22.1\% of all visites originate from social media.
+
+  We start by setting our baseline prevalence, of which we arbitrary set 15\% of partisans are initially affected by misinformation and fake news.
+We then set our baseline \enquote{act rate} (i.e., the average number of transmissible acts per unit time per discussion tie) by taking the average of estimates from \citeauthor{allcott2017social} (\citeyear{allcott2017social}) and from \citeauthor{guess2018selective} (\citeyear{guess2018selective}), which yields 0.164 times per hour per discussion tie.\footnote{ \citeauthor{allcott2017social} report 0.64 $\times$ 41.8\% = 0.268 shares per unit time, while \citeauthor{guess2018selective} report 0.274 $\times$ 22.1\% = 0.060 shares per unit time.
+This averages to 0.164 times per unit time.
+We additionally assume all fake news website visits are driven by information sharing on social media.} We further assume 15\% of those who initially affected are only Republicans, given that the vast majority of identified fake news articles during 2016 U.S.
+presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}.
+Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their suseptable peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformaiton flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
+
+    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below).
+Following PEW data \parencite{pewfakenews} which suggests approximately 16\% of all partisans have had \emph{shared} fake news stories on their social network, we assume the risk of transmission of those who are already infected to share misinformation (i.e., infection probability per act) to be .16 in our simulations.
+Given those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs.
+In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S.
+presidential election were overwhelmingly pro-Trump).
+
+\subsection{Progression from Exposed to Infectious States}
+    Progression from \emph{being exposed} to \emph{being infected} (i.e., transition between exposed to infectious states) was modeled as individual-level stochastic processes, in which there is a differential hazard of transition across partisans following a Bernoulli distribution with the transition rate parameter.
+Consistent with partisan motivated reasoning accounts \parencite{taber2006, nyhan2010corrections}, we set Republicans to have higher transition rates overall (= .30) than Democrats (= .07) given pro-republican misinformation exposure when they are at their mean level of accuracy motivations.
+We set these rate parameters based on results reported in \citeauthor{garrett2016driving} (\citeyear{garrett2016driving}), where they show that online partisan news use increases the chance of incorrectly answering the given factual knowledge question by approximately 30\% points for Republicans and 7\% point for Democrats compared to those who do not exposed to such information (see their Table S6 for a detail).
+Also, we assume those who score high in their accuracy motivations to have a lower transition rate regardless of their partisanship (see the online appendix for a detail), effectively treating one's partisanship and accuracy motivations as individual-level moderators of misinformation adoption process.
+
+\subsection{Corrective Message Exposure and a Recovery from Misperceptions}
+
+%First, consistent with our prior discussion of simple vs.
+complex contagion dynamics, we assume that once exposed, individuals progress to \enquote{recovery} stage when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages debunking misinformation.
+We systematically vary the threshold value of $\rho$ to explore range of plausible values.
+
+\section{Results}
+\subsection{Simple Contagion of Misinformation Exposure}
 
 \printbibliography
-%\newpage
-%\begingroup
-%\parindent 0pt
-%\parskip 1ex
-%\def\enotesize{\normalsize}
-%\theendnotes
-%\endgroup
+\newpage
+\begingroup
+\parindent 0pt
+\parskip 1ex
+\def\enotesize{\normalsize}
+\theendnotes
+\endgroup
 \end{document}

### 2018-02-28 EpiModel.R

@@ -22,7 +22,6 @@ source("dev/helper-functions.R")
 # nD <- 1258
 # nR <- 1142
 # n <- nD + nR
-# tau <- 2 / 3
 # max.time <- 1000 ## time unit is a day
 # nsims <- 100 ## no. of replicated simulations
 
@@ -41,35 +40,28 @@ sw.net[[4]] <- igraph::sample_smallworld(1, n, p = .3, nei = 2, loops = FALSE, m
 
 # set some initial attributes
 ## partisanship -- one of the core mechanisms of directional motivation
-pid <- c(rep("D", nD), rep("R", nR)) ## D == Democrats (50%), R == Republicans (50%)
-#pid <- sample(pid, n, replace = F) ## randomly distribute pid values
+source_lines("dev/setups.R", 1:100)
+pid <- anespanel0809[pid %in% c(1,2), ifelse(pid == 1, "D", "R")]
+pidst <- as.vector(anespanel0809[pid %in% c(1,2), pidst])
 
-## accuracy motivation
-## accuracy_motive is ranged from 1 to 5
-accuracy_motive <- sample(1:5, n, replace = T)
+## accuracy motivation: NFC
+## NFC is ranged from -2 to 2
+## with mean and sd by pid is:
+## Dem: mean = 0.3526269, sd = 0.9299722
+## Rep: mean = 0.3240918, sd = 0.8939632
+nfc <- anespanel0809[pid %in% c(1,2), nfc]
+nfc[is.na(nfc)] <- 0
+## normalize the nfc values
+nfc <- as.vector(range01(nfc))
 
-## Political sophistication
-## important moderator: high sophistication tend to exhibit more direcitonal reasoning
-
-## we set correlation of 0.5 for this sophistication vector
-sophistication <- corr.vector(accuracy_motive, rho = 0.5)
-## since there's some negative values, we round them to nearest integers
-## and convert them to positive integers
-sophistication <- round(sophistication, digits = 0)
-sophistication <- sophistication - min(sophistication)
-## check correlation (r = 0.49)
-cor(accuracy_motive,sophistication)
-
-## scale them to 0 - 1 range
-library("scales")
-accuracy_motive <- rescale(accuracy_motive, to = c(0,1))
-sophistication <- rescale(sophistication, to = c(0,1))
+attr <- data.frame(pid = pid, pidst = pidst, nfc = nfc)
+attr <- attr[order(attr$pid), ]
 
 ## set network attributes
 for (i in 1:4) {
[…]

### 2018-02-28 dev/helper-functions.R

@@ -29,9 +29,14 @@ corr.vector <- function(y, rho, x = NULL) {
   return(z)
 }
 
+## function to normalize the range to 0 - 1
+range01 <- function(x){
+  normx <- (x-min(x)) / (max(x) - min(x))
+  normx
+  }
+
 
 ## function to derive target statistics
-
 get.target.stats <- function(nD, nR, target.gden,
                              target.nodematch,
                              target.nodefactor.nR,

### 2018-02-28 dev/setups.R

@@ -64,37 +64,40 @@ pid_mixing.prob <- pid_mixing/sum(pid_mixing)
 ## proportion of cross-partisan ties ( = .23)
 sum(pid_mixing.prob[lower.tri(pid_mixing.prob)|upper.tri(pid_mixing.prob)])
 
-## this number is similar to Eveland et al (2017) where
-## they report 19.5% of respondents reporting exposure to difference in standard name generator
-## yet their data suggests that this number might underestimate the true exposure
-## see http://www.sciencedirect.com/science/article/pii/S0378873317302113#bib0215
-## if we assume we just add one more alter for those who report no cross-partisan discussion ties,
-## and additional 39% of ties are cross-partisan ties (by their calculation),
-## this would increase the observed proportion a bit.
-## there are a total of 2400 individuals either R or D.
-anespanel0809[pid %in% c(1,2), .N]
-## among them, 1258 are democrats and 1142 are republicans
-anespanel0809[pid %in% c(1:2), table(pid)]
+# ## this number is similar to Eveland et al (2017) where
+# ## they report 19.5% of respondents reporting exposure to difference in standard name generator
+# ## yet their data suggests that this number might underestimate the true exposure
+# ## see http://www.sciencedirect.com/science/article/pii/S0378873317302113#bib0215
+# ## if we assume we just add one more alter for those who report no cross-partisan discussion ties,
+# ## and additional 39% of ties are cross-partisan ties (by their calculation),
+# ## this would increase the observed proportion a bit.
+# ## there are a total of 2400 individuals either R or D.
+# anespanel0809[pid %in% c(1,2), .N]
+# ## among them, 1258 are democrats and 1142 are republicans
+# anespanel0809[pid %in% c(1:2), table(pid)]
+#
+# ## among 2400, 626 individuals do not have any R or D discussants as their primary discussants (first alter)
+# ## (that does not facter into pid_mixing matrix above)
+# anespanel0809[pid %in% c(1,2) & is.na(alter1pid), .N] ## 626
+# ## among 1774 individuals who have at least one of either D or R alters,
+# ## 148 have only one discussants with the same preference
+# anespanel0809[pid == alter1pid & is.na(alter2pid), .N] ## 148
+# ## 110 have two discussants with same preferences
[…]

### 2018-03-26 EpiModel.R
code updates for recovery by social correction models

@@ -11,6 +11,7 @@ library("sna")
 library('magrittr')
 require(data.table)
 source("dev/helper-functions.R")
+require(stargazer)
 
 # In this case, we will focus on a "complex contagion", meaning something you
 # have to hear about from multiple people before you will adopt it.
@@ -161,7 +162,7 @@ dev.off()
 require(intergraph)
 
 netstats <- vector(mode = "list", length = 4)
-net.title <- list("E-R", "Chain", " SW No-Homophily", "SW Homophily")
+net.title <- list("E-R", "Chain", "SW No-Homophily", "SW Homophily")
 names(netstats) <- net.title
 
 table1 <- matrix(NA, ncol = 4, nrow = 7)
@@ -543,22 +544,22 @@ control2 <- control.net(type = "SI", nsteps = max.time, nsims = nsims, epi.by = 
 RNGkind("L'Ecuyer-CMRG")
 set.seed(542435)
 sim2.SEI.model1 <- netsim(est.list[[1]], param2, init, control2)
-save(sim3.SEI.model1, file = "results/sim2.SEI.model1.rda")
+save(sim2.SEI.model1, file = "results/sim2.SEI.model1.rda")
 
 RNGkind("L'Ecuyer-CMRG")
 set.seed(542435)
 sim2.SEI.model2 <- netsim(est.list[[2]], param2, init, control2)
-save(sim3.SEI.model2, file = "results/sim2.SEI.model2.rda")
+save(sim2.SEI.model2, file = "results/sim2.SEI.model2.rda")
 
 RNGkind("L'Ecuyer-CMRG")
 set.seed(542435)
 sim2.SEI.model3 <- netsim(est.list[[3]], param2, init, control2)
-save(sim3.SEI.model3, file = "results/sim2.SEI.model3.rda")
+save(sim2.SEI.model3, file = "results/sim2.SEI.model3.rda")
 
 RNGkind("L'Ecuyer-CMRG")
 set.seed(542435)
 sim2.SEI.model4 <- netsim(est.list[[4]], param2, init, control2)
-save(sim3.SEI.model4, file = "results/sim2.SEI.model4.rda")
+save(sim2.SEI.model4, file = "results/sim2.SEI.model4.rda")
 
 
 
@@ -601,12 +602,185 @@ print.plots.pdf(sim2.SEI.model2, "tree", "Prevalence_SEI.model2", include.expose
 print.plots.pdf(sim2.SEI.model3, "small-world", "Prevalence_SEI.model3", include.exposed = T)
[…]

### 2018-03-26 dev/observednet.R

@@ -1,137 +1,161 @@
 
-## EpiModel with observed social network
+##
+### TO DO LIST : FITTING EPIDEMIC MODELS ON OBSERVED NETWORK
+## SEE http://statnet.github.io/gal/empnet.html
+## and SEE
+## http://statnet.csde.washington.edu/workshops/SUNBELT/current/ndtv/ndtv_workshop.html#importing-data-and-constructing-networkdynamic-objects
 
-## we first need a panel of observations, and convert them to a networkDynamic object.
-## after converting them to a list of static network objects,
+source("observednet.R")
 
-library(foreign)
-library(plyr)
+# The first module that must be updated is the initialization module.
+# The default module contained in the function initialize.net serves as our starting point for writing our own new module, net.init.mod.
+# The default module does lots of work, such as simulating an initial network from the model fit,
+# that we do not need to do with an observed network.
+# Here, there are three key steps for the initialization module:
+#   set up the master data list, dat, including its core data structures;
+#   initialize infection among the nodes in the network;
+#   and use the get_prev.net function to record summary epidemiological statistics.
+# With this modules, whereas x would ordinarily be the fitted network model from netest,
+# now it will just be the networkDynamic object detailed above.
 
-if(!("haven" %in% installed.packages()[,"Package"])) install.packages("haven")
-if(!("data.table" %in% installed.packages()[,"Package"])) install.packages("data.table")
-library(haven)
-library(data.table)
-require(igraph)
-require(sna)
-require(car)
-require(parallel)
+net.init.mod <- function(x, param, init, control, s) {
 
-file_path <- "/Users/songh95/Dropbox/GitHub/Korean2012ElectionProject"
+  # Master Data List
+  dat <- list()
+  dat$param <- param
+  dat$init <- init
+  dat$control <- control
 
-## load the dataset from SPSS and set as data.table object
-dat <- haven::read_spss(paste(file_path, "/Dat/DiscussionForumThreeWavePanel(N=341).sav", sep = ""))
-setDT(dat)
+  dat$attr <- list()
+  dat$stats <- list()
+  dat$temp <- list()
 
-## load the node dataset for subsetting the network
[…]

### 2018-03-26 manuscript_1.0.tex
draft update until simple misinformation exposure results

@@
 \usepackage{times}
+\usepackage{multirow} % multirow tables
+\usepackage{arydshln} % dashline in tabular 
 \renewcommand{\footnotesize}{\small} % use 11pt for footnotes
@@
 
-\note{Word count: 5183 words \\ %\quickwordcount \\
+\note{Word count: 6695 words \\ %\quickwordcount \\
     Draft date: \today \\
@@
 
-% Table 1.
+% Table 1 and 2.
 \begin{table}[!htbp] \centering 
+	\begin{minipage}{\textwidth}
+    \centering
   \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
@@
 \small \vspace{0.15in}
-\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily. 
+\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily.\\ 
 \end{tablenotes}
+ 	\end{minipage}
+\bigbreak
+\vspace{0.5in}
+ 	\begin{minipage}{\textwidth}
+    \centering
+\caption{\\ Misperception Recovery Scenarios by Network Topologies and Thresholds for Adopting Corrections} 
+  \label{tab:Table2}
+
+  \begin{tabular}{ ccccc}
+\toprule
+      \multicolumn{1}{c}{} &
+      \multicolumn{1}{c}{Scenario I} &
+      \multicolumn{3}{c}{Scenario II - Thresholds} \\
+\cline{3-5}
+ & \textbf{Asocial} & \textbf{0.25} & \textbf{0.5} & \textbf{0.75} \\
+\hline \\[-1.8ex] 
+              E-R & Model 1 & Model 2 & Model 3 & Model 4 \\ 
+            Chain & Model 5 & Model 6 & Model 7 & Model 8 \\ 
+  SW No-Homophily & Model 9 & Model 10 & Model 11 & Model 12 \\ 
+  	 SW Homophily & Model 13 & Model 14 & Model 15 & Model 16 \\ 
+\hline \\[-1.8ex]  
+	\end{tabular}
+ 	\end{minipage}
 \end{table}
@@
         \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots1.pdf} 
-        \caption{Erdos-Renyi random network}
+        \caption*{A. Erdos-Renyi random network}
         \label{fig1:random}
@@
         \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots2.pdf} 
-        \caption{Chain network} \label{fig1:tree}
+        \caption*{B. Chain network} \label{fig1:tree}
     \end{subfigure}
@@
         \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots3.pdf} 
-        \caption{Small-world network absent homophily} \label{fig1:nohomophily}
+        \caption*{C. Small-world network absent homophily} \label{fig1:nohomophily}
     \end{subfigure}
@@
         \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots4.pdf} 
-        \caption{Baseline small-world network} \label{fig1:smallworld}
+        \caption*{D. Baseline small-world network} \label{fig1:smallworld}
     \end{subfigure}
@@
     \captionsetup{format=hang}
-    \caption{A cross-sectional view of simulated networks from different network topologies.
-Colored nodes represent nodes that have at least one connection with their neighbor (Red = Republicans, Blue = Democrats) while isolates at given time point was suppressed in visualization.
-A Erdos-Renyi (ER) random network (a) assumes a homogeneous probability of creating and dropping ties across all nodes conditional on observed density.
-A chain-like network (b) has more longer chains than the ER random network while lacks triangle-like structure due to constrains on degrees (less than three).
-While two small-world network has more star-like structure than others, our baseline small-world network (d) is more homophilous than competing specification in (c), as can be seen in Table \ref{tab:Table1}.} \label{fig:Figure1}
+    \caption{A cross-sectional view of simulated networks from different network topologies.} 
+    \label{fig:Figure1}
+    \captionsetup{font=small}
+    \caption*{Note: Colored nodes represent nodes that have at least one connection with their neighbor (Red = Republicans, Blue = Democrats) while isolates at given time point was suppressed in visualization.
+A Erdos-Renyi (ER) random network ( = A) assumes a homogeneous probability of creating and dropping ties across all nodes conditional on observed density.
+A chain-like network ( = B) has more longer chains than the ER random network while lacks triangle-like structure due to constrains on degrees (less than three).
+While two small-world network has more star-like structure than others, our baseline small-world network (= D) is more homophilous than competing specification in its counterpart without homophily (= C), as can be seen in Table \ref{tab:Table1}.}
 \end{figure}
@@
 	Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models.
-We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamcics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies.
-We fit a series of SEIR (\enquote{suseptable - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.
+We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies.
+We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.
 
@@
 However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times per month on average, and among them 41.8\% of all visits originate from social media traffics.
-Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% inidivduals who visited fake news websites, 22.1\% of all visites originate from social media.
+Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% individuals who visited fake news websites, 22.1\% of all visits originate from social media.
 
@@
 presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}.
-Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their suseptable peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformaiton flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
+Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformation flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
 
@@
 Given those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs.
-In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S.
+In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (=.04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S.
 presidential election were overwhelmingly pro-Trump).
@@
 \subsection{Corrective Message Exposure and a Recovery from Misperceptions}
-
-%First, consistent with our prior discussion of simple vs.
-complex contagion dynamics, we assume that once exposed, individuals progress to \enquote{recovery} stage when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages debunking misinformation.
-We systematically vary the threshold value of $\rho$ to explore range of plausible values.
+	For corrective message exposure and subsequent progression from \emph{being infected} to \emph{being recovered}, we examine two possible scenarios -- the first model closely approximate a single-shot, \emph{asocial} correction, in that the model assumes  corrections are randomly received for infected individuals, following individual-level stochastic process of adopting such corrections given exposure.
+This model therefore assumes no social-dynamics surrounding the misinformation correction, as typically assumed in extant experimental literature.
+Our second, more realistic model is more consistent with our prior discussion of simple vs.
+complex contagion dynamics, in that once exposed, individuals progress to recovery state when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages that debunking misinformation.
+We systematically vary the threshold value of $\rho$ to explore system-level consequences of social dynamics surrounding misinformation corrections.
+Below Table \ref{tab:Table2} lists all scenarios for the combination of network topological structure and the threshold value of $\rho$ in misperception recovery.
 
@@
 \subsection{Simple Contagion of Misinformation Exposure}
+	We first look at the simple contagion dynamics of misinformation exposure (assuming no recovery by corrections throughout the simulated time periods) and propagation rates across different network typologies over time, as depicted in Figure \ref{fig:Figure2} and in Table \ref{tab:Table3} below.
+The results reveal that network structures have somewhat non-trivial effects on the dynamics of misinformation propagation at population level.
+It seems that our baseline network model (i.e., small-world network with partisan homophily) appears to be bit better in terms of disseminating given misinformation more faster than other network structures -- that is, we do find some modest evidence that spread of simple misinformation spreads faster in our small world networks (red lines in Panel A of Figure \ref{fig:Figure2}) than in random networks (black lines in Panel A of Figure \ref{fig:Figure2}) when misinformation is spread via simple contagion (i.e., a single contact with those who are infected) followed by a individual-level stochastic progression to being infected given exposure to misinformation.
+
+    Although differences among the cumulative exposure fractions in different network structures were not appear to be vastly different from each other (as their confidence intervals of cumulative exposure fractions significantly overlap with each other: see online supplementary materials for a detail), their exposure rates (as measured by the number of newly exposed individuals at given time point) do differ with each other as can be seen in Figure \ref{fig:Figure2} below.
+This was especially true between our baseline network (red lines) and random networks (black lines) as indicated in Table \ref{tab:Table4}.
+We used the Wilcoxon Rank Sum Test (a nonparametric test of differences of two population distributions) to test whether the two proportions of newly exposed to misinformation among the susceptible (= no.
+of SI flow divided by no.
+of susceptible per each time point) significantly differ from each other between different network topologies.
+The cell entries of Table \ref{tab:Table4} refer to the range of simulated time points in which two distributions of adoption rates statistically different from each other based on Wilcoxon Rank Sum Test.
+For instance, Table \ref{tab:Table4} indicates that from 58 to 901 time points, the distribution of the fraction of newly exposed to misinformation from ER random network and that from our baseline small-world homophily network statistically different from zero (less than .05).
+The results shows that across range of time points excluding the very initial stage of misinformation propagation, network structure induces statistically different adoption rates over time.
+
+\begin{figure}
+\captionsetup[figure]{labelfont={bf,it}}
+    \centering
+
+    \begin{subfigure}[t]{0.8\textwidth}
+        \centering
+        \includegraphics[clip, width=\linewidth, page = 1]{draft/Figure_2__Prevalence.pdf} 
+        \captionsetup{font=small}
+        \caption*{Panel A. Overall Cumulative Prevalence of Misinformation.}
+    \end{subfigure}
+
+    \begin{subfigure}[t]{0.8\textwidth}
+        \centering
+        \includegraphics[clip, width=\linewidth, page = 2]{draft/Figure_2__Prevalence.pdf} 
+        \captionsetup{font=small}
+        \caption*{Panel B. Susceptible - Exposed Flow, measured as the number of newly exposed to misinformation}
+    \end{subfigure}
+
+    \captionsetup{format=hang}
+    \caption{Prevalence and Exposed - Infected Flow of Misinformation Over Time (Assuming No Recoveries) by Network Topologies, Averaged Over 100 Simulations.} 
+    \label{fig:Figure2}
+    \captionsetup{font=small}
+    \caption*{Note: Straight lines in Panel A represent fraction of those who are being exposed to misinformation, whereas dotted lines represent fraction of those who are susceptible.
+X-axis represents simulated times (in hours) and Y-axis represents the fraction exposed to misinformation (in panel A) or rates of misinformation exposure (in panel B).
+Black = Erdos-Renyi random network, Grey = Chain network, Blue = Small-world absent homophily, and Red = baseline small-world homophily network.}
+\end{figure}
+
+\begin{table}[!htbp] 
+	\begin{minipage}{\textwidth}
+    \centering
+  \caption{\\ Overall Prevalence of Misinformation Over Time by Network Topologies (Cumulative Exposure, No Recovery Scenarios)} 
+  \label{tab:Table3} 
+\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \textbf{E-R} & \textbf{Chain} & \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
+\hline \\[-1.8ex] 
+\textbf{Overall} & .594 & .584 & .605 & .640 \\ 
+(95\% CIs) & [.564, .624] & [.558, .609] & [.574, .635] & [.608, .669] \\ 
+\hdashline
+\textbf{Among Dem} & .295 & .290 & .301 & .312 \\ 
+(95\% CIs) & [.274, .316] & [.271, .308] & [.279, .322] & [.287, .332] \\ 
+\hdashline
+\textbf{Among Rep} & .299 & .295 & .305 & .330 \\ 
+(95\% CIs) & [.285, .313] & [.282, .307] & [.290, .319] & [.315, .343] \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\begin{tablenotes}[para,flushleft]
+\small \vspace{0.15in}
+\textbf{Note:} E-R: Erdos Renyi random network.
+Chain: Chain network.
+SW No-Homophily: Small-world network absent of homophily.
+SW Homophily: Small-world network with partisan homophily.
+All statistics are based on 100 random simulations over 1000 time points from the same setup per network topologies.
+\\
+\end{tablenotes}
+\end{minipage}
+\bigbreak
+\vspace{0.5in}
+ 	\begin{minipage}{\textwidth}
+    \centering
+  \caption{\\Time Durations Within Which WRS Test of Differences on Fraction of Newly Exposed of Misinformation Over Time are Significantly Different From Each Other Across Topologies} 
+  \label{tab:Table4} 
+  \begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \textbf{E-R} & \textbf{Chain} & \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
+\hline \\[-1.8ex] 
+\textbf{Chain} & 106 : 278 & - &  &  \\ 
+\textbf{SW No-Homophily} &  68 : 1000 &  70 : 585 & - &  \\ 
+\textbf{SW Homophily} &  58 : 901 &  63 : 942 & 151 : 1000 & - \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\begin{tablenotes}[para,flushleft]
+\small \vspace{0.15in}
+\textbf{Note:} E-R: Erdos Renyi random network.
+Chain: Chain network.
+SW No-Homophily: Small-world network absent of homophily.
+SW Homophily: Small-world network with partisan homophily.
+Cell entries denote the range of time points in which Wilcoxon Rank Sum test indicates the adoption rates from two network topologies statistically different from each other (p < 0.05).
+\\
+\end{tablenotes}
+\end{minipage}
+\end{table}
 

### 2018-03-26 EpiModel.R

@@ -1291,27 +1291,26 @@ PIA.stats <- lapply(seq_len(length(files)), function(i) {
   load(paste0(getwd(), "/results/", fl))
   fl <- get(gsub(".rda", "", fl)) ## pointer to a loaded file
 
-  # if (i %in% c(1:4)) {
-  #   cf <- counterfactuals[1]
-  # } else if (i %in% c(5:8)) {
-  #   cf <- counterfactuals[2]
-  # } else if (i %in% c(9:12)) {
-  #   cf <- counterfactuals[3]
-  # } else {
-  #   cf <- counterfactuals[4]
-  # }
-  #
-  # ## get counterfactual model (no recovery model)
-  # load(paste0(getwd(), "/results/", cf))
-  # cf <- get(gsub(".rda", "", cf))
+  if (i %in% c(1:4)) {
+    cf <- counterfactuals[1]
+  } else if (i %in% c(5:8)) {
+    cf <- counterfactuals[2]
+  } else if (i %in% c(9:12)) {
+    cf <- counterfactuals[3]
+  } else {
+    cf <- counterfactuals[4]
+  }
+
+  ## get counterfactual model (no recovery model)
+  load(paste0(getwd(), "/results/", cf))
+  cf <- get(gsub(".rda", "", cf))
 
   ## without intervensions minus with intervensions, divided by baseline (so proportion), over time by models
-  out.overall <- sapply(1:1000, function(j) fl$epi$r.num[j,]/(fl$epi$r.num[j,] + fl$epi$i.num[j,]), simplify = T)
-  out.dem <- sapply(1:1000, function(j) fl$epi$r.num.pidD[j,]/(fl$epi$r.num.pidD[j,] + fl$epi$i.num.pidD[j,]), simplify = T)
-  out.rep <- sapply(1:1000, function(j) fl$epi$r.num.pidR[j,]/(fl$epi$r.num.pidR[j,] + fl$epi$i.num.pidR[j,]), simplify = T)
+  out.overall <- sapply(1:1000, function(j) fl$epi$i.num[j,]/cf$epi$i.num[j,], simplify = T)
+  out.dem <- sapply(1:1000, function(j) fl$epi$i.num.pidD[j,]/cf$epi$i.num.pidD[j,], simplify = T)
+  out.rep <- sapply(1:1000, function(j) fl$epi$i.num.pidR[j,]/cf$epi$i.num.pidR[j,], simplify = T)
 
[…]

### 2018-03-29 manuscript_1.0.tex
finished up sensitivity analysis, draft updates

@@
 \usepackage{times}
+\usepackage{booktabs}
 \usepackage{multirow} % multirow tables
 \usepackage{arydshln} % dashline in tabular 
+\usepackage{rotating} % vertical tables
+\usepackage{pdflscape} % landscape pages
 \renewcommand{\footnotesize}{\small} % use 11pt for footnotes
@@
 
-\note{Word count: 6695 words \\ %\quickwordcount \\
+\note{Word count: 6630 words \\ %\quickwordcount \\
     Draft date: \today \\
@@
 corrective message adoptions.
-Our focus here is therefore on the role of varying network topologies and level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs.
+Our focus here is therefore on the role of varying network topologies and resulting level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs.
 complex contagion dynamics at population level in conjunction with network topologies.
@@
 Using separable temporal ERGMs \parencite{krivitsky2017inference}, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of \enquote{summary statistics} drawn from egocentric network from 2009 ANES data.\footnote{  Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties.
-See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or summary target statistics, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{\label{note6}	In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
+See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or \emph{summary target statistics}, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{\label{note6} In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
 Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners.
@@
 For degree distribution statistic, we supply a range of plausible yet arbitrary values since 2009 ANES does not have summary network size measure.
-See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, which consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans.
+See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans, that closely approximate the properties of social networks documented in ANES data.
 In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks.
 We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective \enquote{unfriending}:][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties.
-    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several counterfactual models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{	This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model.
-Below Figure \ref{fig:Figure1} shows the simulated cross-sectional views of networks, and Table \ref{tab:Table1} reports key descriptive statistics for each of the networks in terms of their topological properties.
+    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several competing models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{ This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model.
+Below Figure \ref{fig:Figure1} shows the simulated cross-sectional views of networks, and Table \ref{tab:Table1} reports key descriptive statistics for each of the simulated networks from each network evolution model specification in terms of their topological properties.
 \centerline{ -- Table \ref{tab:Table1} and Figure \ref{fig:Figure1} about here -- }
@@
     \centering
-\caption{\\ Misperception Recovery Scenarios by Network Topologies and Thresholds for Adopting Corrections} 
+\caption{\\ Misperception Recovery Scenarios by Network Topologies and Thresholds for Adopting Corrections, Correction Probability = 0.5} 
   \label{tab:Table2}
@@
   Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models.
-We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies.
+We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations.
 We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.
@@
     To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public.
-However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times per month on average, and among them 41.8\% of all visits originate from social media traffics.
+However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times on average, and among them 41.8\% of all visits originate from social media traffics.
 Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% individuals who visited fake news websites, 22.1\% of all visits originate from social media.
@@
 presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}.
-Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformation flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
+Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being merely exposed to do not contribute to misinformation flow and propagation (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
 
-    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below).
+    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold value of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below).
 Following PEW data \parencite{pewfakenews} which suggests approximately 16\% of all partisans have had \emph{shared} fake news stories on their social network, we assume the risk of transmission of those who are already infected to share misinformation (i.e., infection probability per act) to be .16 in our simulations.
-Given those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs.
+Combining those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs stochastically.
 In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (=.04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S.
-presidential election were overwhelmingly pro-Trump).
+presidential election were overwhelmingly pro-Republican).
 
@@
     Progression from \emph{being exposed} to \emph{being infected} (i.e., transition between exposed to infectious states) was modeled as individual-level stochastic processes, in which there is a differential hazard of transition across partisans following a Bernoulli distribution with the transition rate parameter.
-Consistent with partisan motivated reasoning accounts \parencite{taber2006, nyhan2010corrections}, we set Republicans to have higher transition rates overall (= .30) than Democrats (= .07) given pro-republican misinformation exposure when they are at their mean level of accuracy motivations.
+Consistent with partisan motivated reasoning accounts \parencite{taber2006, nyhan2010corrections}, we set Republicans to have higher transition rates overall (= .30) than Democrats (= .07) given pro-republican misinformation exposure when they are at their mean level of accuracy motivations, where accuracy motivations are assumed to be normally distributed among population.
 We set these rate parameters based on results reported in \citeauthor{garrett2016driving} (\citeyear{garrett2016driving}), where they show that online partisan news use increases the chance of incorrectly answering the given factual knowledge question by approximately 30\% points for Republicans and 7\% point for Democrats compared to those who do not exposed to such information (see their Table S6 for a detail).
@@
 complex contagion dynamics, in that once exposed, individuals progress to recovery state when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages that debunking misinformation.
+In these scenarios, we assume approximately half of one's immediate neighbors (\enquote{alters}) who are not yet affected and/or already being recovered from misinformation send correction messages to the infected ego.
 We systematically vary the threshold value of $\rho$ to explore system-level consequences of social dynamics surrounding misinformation corrections.
 Below Table \ref{tab:Table2} lists all scenarios for the combination of network topological structure and the threshold value of $\rho$ in misperception recovery.
+\centerline{ -- Table \ref{tab:Table2} about here -- }
 
 \section{Results}
-\subsection{Simple Contagion of Misinformation Exposure}
+\subsection{Simple Contagions of Misinformation Exposure}
   We first look at the simple contagion dynamics of misinformation exposure (assuming no recovery by corrections throughout the simulated time periods) and propagation rates across different network typologies over time, as depicted in Figure \ref{fig:Figure2} and in Table \ref{tab:Table3} below.
@@
 It seems that our baseline network model (i.e., small-world network with partisan homophily) appears to be bit better in terms of disseminating given misinformation more faster than other network structures -- that is, we do find some modest evidence that spread of simple misinformation spreads faster in our small world networks (red lines in Panel A of Figure \ref{fig:Figure2}) than in random networks (black lines in Panel A of Figure \ref{fig:Figure2}) when misinformation is spread via simple contagion (i.e., a single contact with those who are infected) followed by a individual-level stochastic progression to being infected given exposure to misinformation.
+\centerline{ -- Table \ref{tab:Table3} and Figure \ref{fig:Figure2} about here -- }
 
@@
 The results shows that across range of time points excluding the very initial stage of misinformation propagation, network structure induces statistically different adoption rates over time.
+\centerline{ -- Table \ref{tab:Table4} about here -- }
 
@@
         \captionsetup{font=small}
-        \caption*{Panel B. Susceptible - Exposed Flow, measured as the number of newly exposed to misinformation}
+        \caption*{Panel B. Incidence Rates of New Exposure to Misinformation (the number of newly exposed to misinformation)}
     \end{subfigure}
@@
     \captionsetup{format=hang}
-    \caption{Prevalence and Exposed - Infected Flow of Misinformation Over Time (Assuming No Recoveries) by Network Topologies, Averaged Over 100 Simulations.} 
+    \caption{Prevalence and Incidence Rates of Misinformation Over Time by Network Topologies (Assuming No Recoveries, Averaged Over 100 Simulations).} 
     \label{fig:Figure2}
@@
 X-axis represents simulated times (in hours) and Y-axis represents the fraction exposed to misinformation (in panel A) or rates of misinformation exposure (in panel B).
-Black = Erdos-Renyi random network, Grey = Chain network, Blue = Small-world absent homophily, and Red = baseline small-world homophily network.}
+Red = Erdos-Renyi random network, Blue = Chain network, Green = Small-world absent homophily, and Violet = baseline small-world homophily network.}
 \end{figure}
 
+% Table 3 and Table 4
 \begin{table}[!htbp] 
@@
     \centering
-  \caption{\\ Overall Prevalence of Misinformation Over Time by Network Topologies (Cumulative Exposure, No Recovery Scenarios)} 
+  \caption{\\ Misinformation Exposure Prevalence Per 100 Individuals Over Time by Network Topologies (Cumulative Exposure, No Recovery Scenarios)} 
   \label{tab:Table3} 
@@
 
+\subsection{Complex Contagions of Misinformation Corrections}
+  We now examine complex contagion dynamics of corrective message adoption and its impacts on population-level dynamics of misinformation propagation (detailed recovery scenarios are described in Table \ref{tab:Table2}).
+Table \ref{tab:Table5} lists results for all scenarios in terms of prevalence of misinformation and number of those who are newly being recovered per hour, and Panel A to Panel D in Figure \ref{fig:Figure3} graphically depicts these results.
+\centerline{ -- Table \ref{tab:Table5} and Figure \ref{fig:Figure3} about here -- }
+
+% Table 5    
+\begin{sidewaystable}[ht]
+  \centering
+    \caption{\\ Asocial vs. Thresholds Recovery Model Results} 
+  \label{tab:Table5} 
+\begin{tabular}{cccccc}
+ \toprule
+       \multicolumn{1}{c}{} &  \multicolumn{1}{c}{} & 
+      \multicolumn{1}{c}{Scenario I} &
+      \multicolumn{3}{c}{Scenario II - Thresholds} \\
+\cline{4-6}
+ &   & \textbf{Asocial} & \textbf{0.25} & \textbf{0.5} & \textbf{0.75} \\
+  \midrule
+               \textbf{E-R} & I Prevalence & 23.484 [20.663, 26.037] & 3.661 [3.070, 4.406] & 3.722 [3.031, 4.503] & 5.398 [4.383, 6.844] \\ 
+                            & R Incidence & 1.262 [.000, 3.716] & .429 [.150, 1.350] & .423 [.130, 1.383] & .520 [.0433, 1.944] \\ 
+             \textbf{Chain} & I Prevalence & 22.746 [20.051, 25.492] & 3.581 [2.983, 4.286] & 3.581 [2.983, 4.286] & 5.260 [4.259, 6.399] \\ 
+                            & R Incidence & 1.196 [.000, 3.625] & .405 [0.138, 1.339] & .405 [0.138, 1.339] & .483 [.0372, 1.843] \\ 
+   \textbf{SW No-Homophily} & I Prevalence & 24.107 [21.220, 27.047] & 3.926 [3.266, 4.693] & 4.016 [3.347, 4.821] & 6.107 [4.951, 7.639] \\ 
+                  & R Incidence & 1.329 [.000, 3.797] & .452 [.176, 1.465] & .457 [.150, 1.483] & .599 [.050, 2.150] \\ 
+      \textbf{SW Homophily} & I Prevalence & 26.039 [23.029, 29.007] & 3.863 [3.148, 4.724] & 3.983 [3.295, 4.884] & 6.014 [4.935, 7.423] \\ 
+                  & R Incidence & 1.420 [.003, 4.003] & .495 [.188, 1.461] & .494 [.168, 1.508] & .656 [.0771, 2.127] \\ 
+   \bottomrule
+\end{tabular}
+\begin{tablenotes}[para,flushleft]
+\small \vspace{0.15in}
+\textbf{Note:} E-R: Erdos Renyi random network.
+Chain: Chain network.
+SW No-Homophily: Small-world network absent of homophily.
+SW Homophily: Small-world network with partisan homophily.
+I Prevalence: Infection prevalence per 100 individuals over time.
+R Incidence: Recovery incidence per time.
+\\
+\end{tablenotes}
+\end{sidewaystable}
+
+% Figure 3
+\begin{sidewaysfigure}
+\captionsetup[figure]{labelfont={bf,it}}
+\captionsetup[subfigure]{labelfont=bf,textfont=normalfont,singlelinecheck=on}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[trim={1.5cm 2.7cm 2cm 5cm}, clip, width=\linewidth]{draft/Fig3a.pdf} 
+        \caption*{A. Erdos-Renyi random network}
+        \label{fig3:random}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[trim={1.5cm 2.7cm 2cm 5cm}, clip, width=\linewidth]{draft/Fig3b.pdf} 
+        \caption*{B. Chain network} \label{fig3:chain}
+    \end{subfigure}
+
+    \vspace{1cm}
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[trim={1.5cm 2.7cm 2cm 5cm}, clip, width=\linewidth]{draft/Fig3c.pdf} 
+        \caption*{C. Small-world network absent homophily} \label{fig3:nohomophily}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+        \includegraphics[trim={1.5cm 2.7cm 2cm 5cm}, clip, width=\linewidth]{draft/Fig3d.pdf} 
+        \caption*{D. Baseline small-world network} \label{fig3:smallworld}
+    \end{subfigure}
+
+    \vspace{1cm}
+    \captionsetup{format=hang}
+    \caption{Proportion of Being Recovered from Infection Status, by Network Topologies} 
+    \label{fig:Figure3}
+    \captionsetup{font=small}
+    \caption*{Note: Red: Asocial random correction, Blue: Thresholds = 0.25, Green: Thresholds = 0.50, and Violet: Thresholds = 0.75.} 
+\end{sidewaysfigure}
+
+  As can be seen in Figure \ref{fig:Figure3}, all of the social-based correction models produced more effective results in deterring misinformation propagation in the onset of correction intervention.
+As time progresses, however, across all of the network topologies we instead see asocial random correction models tend to produce more number of being recovered from misinformation infection.
+However, this is due to the fact that in such scenarios, the number of those who are being \emph{infected} are also larger than threshold-based correction scenarios -- since the number of being recovered is dependent upon the number of being infected at previous time point, even seemingly effective correction settings may produce much fewer cases of being recovered if it had averted new infection at the first place.
+Therefore, instead of looking at cumulative mean \emph{prevalences} over time, Figure \ref{fig:Figure4} below alternatively present Proportions of infections being averted (PIA) relative to no-recovery scenarios reported in Table \ref{tab:Table3}.
+For this metric, we derive the proportion of those who otherwise being infected if no recovery had been taken place at each simulated time point as follow:
+\[ PIA_{t} = \frac{I_{t}^{baseline} - I_{t}^{recover}}{I_{t}^{baseline}} \] where $\mathit{I}$ is the number of those who are infected in each of the recovery scenarios $I^{recover}$ (as in Table \ref{tab:Table2}) vs.
+no-recovery scenarios $I^{baseline}$ (as in Table \ref{tab:Table3}) at each simulated hours $\mathit{t}$.
+Since no-recovery scenarios reported in Table \ref{tab:Table3} are based on the same network typologies and model specifications \emph{except} infection recovery settings, this allow us to empirically identify counterfactuals without hypothetically assuming number of those who stay being infected.
+We first derive PIA values for each simulated time points (from time 1 to time 1000), and then take the mean across all time points, then replicate this estimate across 100 simulations per model, as plotted in Figure \ref{fig:Figure4}.
+
+  As can be seen in Figure \ref{fig:Figure4}, our results reveal that in all of the network topologies, socially-contingent corrections  produce much more effective intervention results than compared to asocial corrections typically considered in extant literature.
+All of the asocial correction scenarios yield on average PIA values of .46 to .47, whereas all thresholds-based models typically yield PIA values of .74 to .80, meaning on average across all time points, 74 to 80\% of those who otherwise being stay infected and/or newly infected can be prevented based on social-based correction messages exposure and complex contagion of such messages.
+This appears to be the function of the fact that, in earlier onset of correction message exposure, thresholds values required to adopt correction messages are likely to be easily met due to the scarcity of misinformation in one's immediate environments, therefore attitudinal compositions surrounding simple contagion of misinformation vs.
+complex contagion of corrective messages tends to favor complex contagion dynamics.
+This is also evident in Figure \ref{fig:Figure4}, where models with much higher threshold value (=.75, in recovery model 4, model 8, model 12 and model 16) are slightly less effective than other threshold-based models.
+However, it is indeed interesting to observe that even relatively low threshold (=.25) and moderate threshold (=.50) values all social correction models greatly enhance the effectiveness of corrective message exposure and their adoption.
+
+% Figure 4
+\begin{sidewaysfigure}
+\captionsetup[figure]{labelfont={bf,it}}
+    \centering
+        \includegraphics[clip, width=\linewidth]{draft/Fig4.pdf}
+
+    \captionsetup{format=hang}
+    \caption{Proportions Infections Averted, Across Recovery Model Thresholds.} 
+    \label{fig:Figure4}
+    \captionsetup{font=small}
+    \caption*{Note: Y-axis denotes Proportions of Infections being Averted (PIA) relative to the no-recovery scenarios.
+We present overall (=green boxplots), among Democrats (=orange boxplots) and among Republicans (=blue boxplots) PIA estimates.}
+\end{sidewaysfigure}
+
+\subsection{Sensitivity Analysis}
+  Since we simply assumed the probability of alters sending corrections messages to an infected ego to be .5 in our main results, a series of sensitivity analysis were conducted in order to evaluate the influence of this parameter on the level of PIA metric.
+In the analyses, probabilities of alters sending corrections to an infected ego were varied to be 0.25 vs.
+0.5 vs.
+0.75.
+Figure \ref{fig:Figure5} below reports the results of this sensitivity analysis.
+Both factors appear to have some impact on PIA estimates, yet at the low to average thresholds models (i.e., models that assume thresholds of adopting corrective messages to be 0.25 or 0.5), the probability of alters sending correction messages did not greatly alter the reported findings in Figure \ref{fig:Figure4}.
+In the high thresholds models (=0.75, blue plots in Figure \ref{fig:Figure5}), we see the the increased thresholds specification marginally decreases the PIA, yet the higher value of probability of sending corrections appeared to mitigate the effect of higher threshold parameters, especially in our baseline small-world homophily network models (model 14 to model 16 in Table \ref{tab:Table2}).
+In all of the models, however, PIA metrics are still substantially higher than single-shot, asocial correction scenarios (typically from .46 to .47).
+
+% Figure 5
+\begin{sidewaysfigure}
+\captionsetup[figure]{labelfont={bf,it}}
+    \centering
+        \includegraphics[clip, width=0.9\linewidth, height=0.55\textwidth]{draft/Fig5.pdf}
+
+    \captionsetup{format=hang}
+    \caption{Sensitivity Analysis of Alter Probability of Sending Correction Messages, Across Different Recovery Model Thresholds.} 
+    \label{fig:Figure5}
+    \captionsetup{font=small}
+    \caption*{Note: Y-axis denotes Proportions of Infections being Averted (PIA) relative to the no-recovery scenarios.
+We present different PIA values per each recovery scenario assuming probabilities of alters sending correction messages to infected ego equal to 0.25 (= red boxplots), 0.5 (= green boxplots) and 0.75 (=blue boxplots).
+Main results reported in \ref{fig:Figure4} assumed probability of alter sending corrections to be 0.5 (= green boxplots).}
+\end{sidewaysfigure}
+
+\section{Discussion}
+  TBA
+
 \printbibliography

### 2018-03-29 EpiModel.R

@@ -19,16 +19,6 @@ require(stargazer)
 # (so individuals may transition back and forth between the susceptible and infected states)
 
 
-# ### Set parameters in advance ###
-# nD <- 1258
-# nR <- 1142
-# n <- nD + nR
-# max.time <- 1000 ## time unit is a day
-# nsims <- 100 ## no. of replicated simulations
-
-## set no. of cores
-ncores <- parallel::detectCores(logical = F)
-
 ### Step 1: Construct network ###
 # Construct a random network
 require(igraph)
@@ -213,77 +203,6 @@ stargazer(table1, title = "Descriptive statistics of cross-sectional network fro
 save(est.list, dx.list, netstats, file = "results/net_and_dx_list.rda", compress = "bzip2")
 
 
-# ## ------------------------- ##
-# ## Step 2: Standard SI model ##
-# ## ------------------------- ##
-#
-# # load("results/net_and_dx_list.rda")
-# # rm(dx.list, netstats)
-#
-# ## set number of those who infected at the start
-# ## For initial conditions, one can use the i.num to set the initial number infected at the start,
-# ## or pass in a vector with a disease status for each of the nodes in the network.
-# ## EpiModel stores the individual-level disease status as a vector of lower-case letters:
-# ## “s” for susceptible, “i” for infected, and “r” for recovered.
-# ## we assume random 15% of Republicans are initially infected (n = 184)
-# status.vector <- c(rep(0, nD), rbinom(nR, 1, 0.15))
-# status.vector <- ifelse(status.vector == 1, "i", "s")
-# table(status.vector, pid)
-# init <- init.net(status.vector = status.vector)
-#
-# ## infection probability (risk of transmission), act rate (mean number of acts)
-# ## PEW data suggests approximately 16% of all partisans share FN news stories on their social networks,
-# ## while Guess et al. and Allcott & Gentzkow report 0.060 / 0.268 shares per unit time
-# ## (0.060 + 0.268) / 2 = 0.164
-# param1 <- param.net(inf.prob = 0.16, act.rate = 0.164)
-#
-# ## set control param. (model type and no of stpes, with n of replications)
-# control1 <- control.net(type = "SI", nsteps = max.time, nsims = nsims, epi.by = "pid",
[…]

### 2018-03-29 dev/helper-functions.R

@@ -8,6 +8,10 @@ tau <- 0.5
 max.time <- 1000 ## time unit is a day
 nsims <- 100 ## no. of replicated simulations
 
+## initial status
+status.vector <- c(rep(0, nD), rbinom(nR, 1, 0.15))
+status.vector <- ifelse(status.vector == 1, "i", "s")
+
 ## set no. of cores
 ncores <- parallel::detectCores(logical = F)
 
@@ -260,4 +264,541 @@ get.summary.stats <- function(netsim, qvals = c(0.025, 0.5, 0.975)) {
 ## sourcing specific lines from the .R syntax
 source_lines <- function(file, lines){
   source(textConnection(readLines(file)[lines]))
+}
+
+## W Rank-Sum test
+WRS.test <- function(dat1, dat2) {
+
+  ## find min of distribution that do not different from each other
+  test.min <- sapply(1:1000, function(i) {
+    index <- seq(1, i)
+    test <- suppressWarnings(wilcox.test(dat1[index, se.flow.mean/s.num.mean], dat2[index, se.flow.mean/s.num.mean]))
+    test$p.value
+  }, simplify = T)
+
+  min <- min(which(test.min < 0.05))
+
+  test.max <- sapply(min:1000, function(i) {
+    index <- seq(min, i)
+    test <- suppressWarnings(wilcox.test(dat1[index, se.flow.mean/s.num.mean], dat2[index, se.flow.mean/s.num.mean]))
+    test$p.value
+  }, simplify = T)
+
+  max <- min + max(which(test.max < 0.05)) - 1
+
+  return(c(min = min, max = max))
+}
+
+## ---------------------- FUNCTIONS FOR SIMULATIONS ----------------- ##
+
+## infection module
+
+infect <- function(dat, at) {
+
+  active <- dat$attr$active
+  status <- dat$attr$status
+  tea.status <- dat$control$tea.status
+  nw <- dat$nw
+
+  idsSus <- which(active == 1 & status == "s")
+  idsInf <- which(active == 1 & status == "i")
+  nActive <- sum(active == 1)
+
+  nElig <- length(idsInf)
+  nInf <- 0
+
+  if(!is.null(dat$param$pid.diff.rate)) {
+    individual.diff.rate <- (dat$param$pid.diff.rate)/2
+  } else {
+    individual.diff.rate <- NULL
+  }
+
+  if (nElig > 0 && nElig < nActive) {
+    del <- discord_edgelist(dat, at)
[…]

### 2018-05-02 manuscript_1.0.tex
ICA draft complete
- need to check discussion section once again
- need to draft online supplement appendix
- get feedback?

@@
 
-\authornote{Hyunjin (Jin) Song is currently an assistant professor ("Universitätsassistent, post-doc") in the Department of Communication at the University of Vienna, and also a member of the Vienna Computational Communication Science Lab.}
+\authornote{ Hyunjin (Jin) Song is currently an assistant professor ("Universitätsassistent, post-doc") in the Department of Communication at the University of Vienna, and also a member of the Vienna Computational Communication Science Lab.
+Please direct any questions and inquiries concerning this manuscript to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
 
-\note{Word count: 6630 words \\ %\quickwordcount \\
+\note{\addvspace{.25in} 
+Word count: 8908 words \\
 Draft date: \today \\
+\addvspace{1in} 
+Paper prepared for presentation at the 2018 Annual Conference of the International Communication Association (ICA), Prague, Czech Republic, May 24 -- 28, 2018 \\
 \addvspace{.25in} 
       \textbf{Draft in progress. Please do not cite without permission.} \\
-      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}
+      }
 
@@
 
-  Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least factually dubious) information from the perspectives of an individual's cognitive processes \parencite{Lewandowsky_2012PSPI, kuklinski2000misinformation, weeks2015emotions}.
-These studies have generated a valuable insights of how individuals often maintain factually false beliefs, and further, how corrections to false beliefs are received and processed \parencite{Lewandowsky_2012PSPI, thorson_2016, garrett2016driving}.
-However, despite growing interest and continued research effort to better understand the nature and its exact mechanism, what we know about the spread of misinformation and fake news specifically on online social networks is largely based on limited evidence due to its complex nature of the problem.
+  Along with these trends, there has been an growing interest among scholars on how people process and maintain factually false (or at least dubious) information from an individual's cognitive processing perspectives \parencite{Lewandowsky_2012PSPI, kuklinski2000misinformation, weeks2015emotions}.
+These studies have generated a valuable insights of how individuals often maintain factually false beliefs, and further, how corrections to such false beliefs are received and processed \parencite{Lewandowsky_2012PSPI, thorson_2016, garrett2016driving}.
+However, despite growing interest and continued research effort to better understand the nature and its exact mechanism, what we know about the spread of misinformation specifically on online social networks is largely based on limited evidence due to its complex nature of the problem.
 
@@
   In what follows, we first review existing evidence regarding political misperceptions and the effects of fact-checking (i.e., correction) messages.
-We advance our perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context of which misinformation and corrections are received.
-Based on a well-known class of an epidemic model of virus infection and recovery, we propose an integrated model of misinformation diffusion and socially-contingent corrections on social networks, with a special focus on the differences between a \emph{simple contagion} of misinformation and a \emph{complex contagion} of corrections and fact-checking messages.
+We advance our perspective by combining an individual-level cognitive and affective basis of adopting such misinformation with a social context in which such misinformation and corrections are received.
+Next, based on a well-known class of an epidemic model of virus infection and recovery, we propose an integrated model of misinformation diffusion and socially-contingent corrections on social networks, with a special focus on the differences between a \emph{simple contagion} of misinformation and a \emph{complex contagion} of corrections and fact-checking messages.
 Relying on Agent-Based Model (ABM) simulations, we robustly explore boundary conditions of such dynamics, aiming to uncover how and when such misinformation propagates into the public.
@@
 
-     Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define \emph{fake news} as \enquote{distorted signals uncorrelated with the truth} (p.
+     Following \citeauthor{allcott2017social}'s (\citeyear{allcott2017social}) definition, we define a broad category of \emph{fake news} as \enquote{distorted signals uncorrelated with the truth} (p.
 212).
@@
 128]{flynn2017nature}.
-In relation to this, \emph{dis}information campaigns often denote organized, strategic efforts that trying to sway public opinion using rumors and misinformation \parencite{Garrett2017distraction, Lewandowsky_2012PSPI}.
+Relatedly, \emph{dis}information campaigns often denote organized, strategic efforts that trying to sway public opinion using rumors and misinformation \parencite{Garrett2017distraction, Lewandowsky_2012PSPI}.
 Understood in this way, fake news often exclude unintentional reporting mistakes, parodies and satires, or unverifiable conspiracy theories \parencite{allcott2017social}.
@@
 That is, people disproportionately gravitate toward information that conforms to their partisan priors \parencite{ weeks2014electoral, garrett2016driving}, and  more likely to accept and endorse such messages \parencite{nyhan2010corrections, guess2018selective}.
-A mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that citizens tend to evaluate attitudinally congruent information as more convincing and valid \emph{regardless of its veracity}, while attitudinally inconsistent information is likely to be perceived as weak and therefore likely to be rejected.
-Therefore, it is perhaps not surprising to find that most of the prior studies based on a motivated reasoning framework document that fact-checking messages (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to inherent tendency of humans to directionally process politically relevant information \parencite{thorson_2016, taber2006,flynn2017nature}.
-Even worse, corrective messages may backfire, may induce higher level of endorsements of false beliefs than actually lower them \parencites[e.g.,][]{nyhan2010corrections}[but see][]{Wood2018}.
+Not surprisingly, a mounting evidence -- largely based on \citeauthor{kunda1990}'s (\citeyear{kunda1990}) or on \citeauthor{taber2006}'s (\citeyear{taber2006}) motivated reasoning framework -- suggests that citizens tend to evaluate attitudinally congruent information as more convincing and valid \emph{regardless of its veracity}, while they likely to perceive attitudinally inconsistent information as weak in their argument strengths, therefore likely to  reject such attitudinally inconsistent information.
+Therefore, it is perhaps not surprising to find that most of the prior studies based on a motivated reasoning framework document that fact-checking messages (sometimes denoted as \enquote{corrective} or \enquote{debunking} messages in the literature) have only limited effects due to an inherent human tendency to directionally process politically relevant information \parencite{thorson_2016, taber2006,flynn2017nature}.
+Even worse, corrective messages may sometimes backfire, inducing higher level of endorsements of false beliefs than actually lower them \parencites[e.g.,][]{nyhan2010corrections}[but see][]{Wood2018}.
 
       Another line of studies based on a dual process theory of human cognitive processing and memory suggests that attitudinally-congruent misinformation tends to form a coherent mental model based on one's partisan schema and stereotypes \parencite[e.g.,][]{garrett2013undermining, Lewandowsky_2012PSPI}.
-Therefore, people tend to fill any gaps caused by corrections (that invalidate some parts of the existing mental model) with flawed but attitudinally congruent misinformation that is still readily accessible in their memory \parencite{Lewandowsky_2012PSPI}.
-Studies also find that this effect is much more likely when correction messages do not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}, when the perceived veracity of initial misinformation is high \parencite[due to fluency bias in one's cognitive processing:][]{Lewandowsky_2012PSPI}, or when individuals can generate counter-arguing reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}.
-Most importantly, due to limitations of strategic memory search processes (i.e., it requires more effortful processing), people may still rely on negated misinformation in subsequent reasoning \emph{even when they remember such information is factually incorrect} \parencite{Lewandowsky_2012PSPI}.
+Therefore, people tend to fill any gaps caused by corrections (that invalidate some parts of the existing mental models) with flawed but attitudinally congruent misinformation that is still readily accessible in their memory \parencite{Lewandowsky_2012PSPI}.
+Studies find that this effect is much more likely when correction messages do not update the initial mental model that justifies misinformation \parencite{Chan_debunking_meta_2017}, when the perceived veracity of initial misinformation is high \parencite[due to fluency bias in one's cognitive processing:][]{Lewandowsky_2012PSPI}, or when individuals can generate counter-arguing reasons in support for initial misperceptions \parencite{garrett2013undermining, Chan_debunking_meta_2017}.
+Most importantly, due to inherent limitations of strategic memory searching process (i.e., requires more effortful processing), people may still rely on negated misinformation in subsequent reasoning even when they \emph{do remember} such information is factually incorrect \parencite{Lewandowsky_2012PSPI}.
 Therefore, even in the face of seemingly effective corrections, the effect of misperceptions lingers and continue to exert influence \parencite{thorson_2016}.
 
-  Under certain situations, it seems that citizens \emph{indeed} can adhere factual information based on correction messages despite their perpetual partisan bias \parencite[e.g.,][]{Wood2018, nyhan2017taking}.
+  Under certain situations, it seems that citizens \emph{indeed} can adhere factual information based on correction messages despite their perpetual partisan biases \parencite[e.g.,][]{Wood2018, nyhan2017taking}.
 Yet as \citeauthor{margolin2017} (\citeyear{margolin2017}) note, it appears that such effects often require special \emph{social context}.
-This observation is indeed much warranted, as most of the previous studies concerning misinformation and the effect of fact-checking messages are conducted in an experimental context with a single-shot, \emph{asocial} correction message from media professionals and fact-checking organizations \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining,weeks2015emotions}.
+This observation is indeed much warranted, as most of the previous studies concerning misinformation and the effect of fact-checking messages are conducted in an experimental context with a single-shot, \emph{asocial} correction message mostly from media professionals and fact-checking organizations \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining,weeks2015emotions}.
 There is also a suggestive evidence that fact-checking and corrective messages from one's peers in their social networks -- what we would call a \enquote{social correction} -- are more likely to be effective in reducing misperceptions \parencite[e.g.,][]{margolin2017, bode2017see}.
-In what follow, we review several theoretical accounts of such \emph{socially-based} correction messages on misinformation and fake news.
+In what follow, we review several theoretical accounts of such \emph{socially-based} correction messages on misinformation.
 
@@
 Many of the partisan rumors and fake news tend to be richer in their \enquote{novelty} \parencite{wu2007novelty} regardless of its veracity and informational value.
-As \citeauthor{giglietto2016fakes}'s (\citeyear{giglietto2016fakes}) observation suggests, such non-redundant and \enquote{novel} information (false and unverified information being one of them) tend to be engaging, and spread faster via weaker ties \parencite{granovetter1977strength}.
+As \citeauthor{giglietto2016fakes}'s (\citeyear{giglietto2016fakes}) observations suggest, such non-redundant and \enquote{novel} information (false and unverified information being one of them) tend to be engaging, and spread faster via weaker ties \parencite{granovetter1977strength}.
 You can easily share and post such news with little to no effort, and your friends on your social networks are easily exposed to such information, in turn they also share such news to their own peers, and so on -- creating what is called a \emph{information cascade} of misinformation \parencite{del2016spreading}.
@@
 
-    Moreover, due to inherent partisan motivated directionality, the threshold of actually \emph{adapting} such a false yet pro-attitudinal claim (i.e., believing attitudinally congruent misinformation) may also exhibit similar low-threshold properties, although the actual threshold for believing misinformation would be bit higher compared to that of mere exposure and awareness \parencite[e.g.,][]{Monsted_plos2017}, and also subject to some individual differences \parencite[e.g.,][]{weeks2015emotions, flynn2017nature}.
-As previously suggested, people tend to directionally process political information \parencite{taber2006}, and they tend to easily remember and recall attitudinally-consistent information than uncongenial ones.
+    Moreover, due to inherent partisan motivated directionality, the threshold of actually \emph{adapting} such a false yet pro-attitudinal claim (i.e., believing attitudinally congruent misinformation) may also exhibit similar low-threshold properties, although the actual threshold for believing misinformation would be somewhat higher compared to that of mere exposure and awareness \parencite[e.g.,][]{Monsted_plos2017}, let alone it may further subject to some individual differences \parencite[e.g.,][]{weeks2015emotions, flynn2017nature}.
+Yet as previously suggested, people tend to directionally process political information \parencite{taber2006}, and they tend to easily remember and recall attitudinally-consistent information than uncongenial ones.
 Therefore, at least for citizens who find given misinformation to be congenial to their partisan priors, \emph{adapting} such false yet pro-attitudinal claims also does not require high number of repeated exposure nor independent, multiple exposure to different sources supporting such claims.
@@
     In contrast, there are reasons to believe why the effectiveness of fact-checking and corrective messages would be different from that of a simple contagion of misinformation.
-An adoption of a new perspective that contradicts with one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where it requires \emph{exposure to multiple sources}, rather than \emph{multiple number of exposures}, endorsing such message in order to be accepted and further spread into a given network.
-This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changes in one's political beliefs and attitudes require multiple sources of affirmation and reinforcement from multiple \emph{contacts} compared to simple contagion cases \parencite[e.g.,][]{gonzalez2017decoding, larson2016social, siegel2009social}.
+An adoption of a new perspective that contradicts with one's priors (such as an adoption of counter-attitudinal fact-checking messages) is likely to be, in \citeauthor{centola2007complex}'s (\citeyear{centola2007complex}) term, a \enquote{complex contagion} where it requires exposure to multiple \enquote{sources}, rather than multiple number of exposures, endorsing a given (counter-attitudinal) message in order to be accepted by an individual and further being spread into a given network.
+This is because many political attitudes and subsequent actions (such as politically motivated misperceptions) are likely to be deeply rooted in one’s social identities and values, therefore changing one's political beliefs and attitudes require multiple sources of affirmations and reinforcements from multiple \emph{contacts} compared to simple contagions \parencite[e.g.,][]{gonzalez2017decoding, larson2016social, siegel2009social}.
 
     Moreover, such complex contagion dynamics surrounding correction messages are also likely to be dependent upon the attitudinal composition of one's local network.
-For the case of a adoption of fact-checking and corrective messages, the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{endorse} false belief based on misinformation) tend to discourages their neighbors to adopt a correction, whereas the number of one's neighbors who are already activated (e.g., those who do not believe misinformation anymore) would increase one's susceptibility to adopt the correction given exposure to such correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}.
-Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by one's neighbors, therefore relative distribution of one's neighbors (in terms of supporters vs.
-opponents of the adoption) critically influence one's decision to adopt a controversial innovation \parencite{larson2016social, gonzalez2017decoding, friedkin2001norm}.
-This further means that locally-defined social dynamics may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would non-trivially interact with a structure and its attitudinal composition of a given network \parencite[e.g.,][]{friedkin2001norm}.
+For the case of adopting fact-checking and corrective messages (i.e., misinformation correction), the number of one's neighbors who are \emph{not} activated (e.g., those who still \emph{endorse} false belief based on misinformation) tend to discourages their neighbors to adopt a correction, whereas the number of one's neighbors who are already activated (e.g., those who do not believe misinformation anymore) would increase one's likelihood of adopting the correction \parencites[i.e., a \enquote{\emph{contested}} contagion:][]{centola2007complex}[also see][]{friedkin2001norm}.
+Indeed, many social contagions are often perceived to be lack of credibility and legitimacy until adopted by many of one's neighbors, therefore relative distributions of one's neighbors in terms of supporters vs.
+opponents of the adoption critically influence one's adoption of a controversial innovation \parencite{larson2016social, gonzalez2017decoding, friedkin2001norm}.
+This discussion further suggests that locally-defined attitudinal compositions of one's network may drive specific adoption behaviors of counter-attitudinal information, and consequently, such process would nontrivially interact with a structure of a given network \parencite[e.g.,][]{friedkin2001norm}.
 Indeed, there exits a considerable support for this perspective, such that different network topologies \parencite[][]{Centola2010Sience, siegel2009social} or attitudinal makeup of social networks\footnote{  Here, we use the term \enquote{attitudinal composition} to denote a relative distribution of supporters vs.
@@
 
-  There are also at least several other reasons why socially-based correction messages, especially from one's peers, might be more effective than a single-shot, \emph{asocial} correction message from more distanced sources (such as fact-checking organizations or mere strangers).
-First, people may evaluate information coming from their peers to be more credible and trustworthy \parencite[e.g.,][]{metzger2010social}, and more willing to deliberate with their close social contacts \parencite{morey2012matters}.
+  There are also several other reasons why socially-based correction messages, especially from one's peers, might be more effective than a single-shot, \emph{asocial} correction message from more distanced sources (such as messages from fact-checking organizations or mere strangers).
+First, people may evaluate information coming from their close social contacts to be more credible and trustworthy \parencite[e.g.,][]{metzger2010social}, and more willing to deliberate with them \parencite{morey2012matters}.
 Research suggests that while individuals rather maintain much flexible attitudes as long as their social affiliation goals are met \parencite{levitanspy2017}, reputational risks and social accountability of rejecting corrective messages run high for more close social contacts compared to more distant sources such as strangers \parencite{margolin2017}.
 
-    Second, previous studies concerning citizens' political discussion network suggest that an individual's network construction is not likely driven by overt partisan considerations \parencite{song2015uncovering,lazer2010coevolution}, therefore there exists a considerable degree of exposure to disagreement in citizens' everyday political interactions \parencite[e.g.,][]{Bakshy1130, morey2012matters}.
+    Second, previous studies concerning citizens' political discussion network suggest that an individual's network construction is not likely driven by overt partisan considerations \parencite{song2015uncovering,lazer2010coevolution}, and there is a considerable degree of cross-cutting exposure in citizens' everyday political interactions \parencite[e.g.,][]{Bakshy1130, morey2012matters, huckfeldt2004disagreement}.
 Under such a situation, attitudinally heterogeneous networks trigger more systematic processing of available information, which make individuals to be more responsive to argument strengths \parencite{levitan2008resistance} or social utility \parencite{messing2014selective}, therefore makes them less resistant to corrective messages from their peers.
 
-  All in all, prior empirical evidence and theoretical perspectives convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level propagation dynamics.
-Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, while ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation.
-In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2017decoding}.
-Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experiment contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.
+ In sum, prior theoretical perspectives and available empirical evidences convincingly suggest that a \emph{simple} contagion of misinformation and a \emph{complex} contagion of corrective messages would exhibit different properties for population-level propagation dynamics.
+Structurally weak, but bridging ties such as distant contacts in social networks may provide sufficient means for a simple (mis)information -- much like communicable disease -- to be spread, and ideologically-driven directionally motivated reasoning may provide sufficient psychological grounds for partisans to easily adopt and believe such misinformation.
+In contrast, an adoption of corrective message -- similar to controversial innovations -- requires independent and multiple reinforcements from many social contacts due to its counter-attitudinal and \enquote{contested} nature, and this is critically dependent upon a structure of network and its attitudinal composition \parencite{centola2007complex, Centola2010Sience, gonzalez2017decoding}.
+Aforementioned perspectives therefore undoubtedly point to the possibility that adoptions of fact-checking messages are likely to be highly socially-contingent, and under certain cases, a social correction would be much more effective than an isolated correction message as typically have been considered in previous experimental contexts \parencite[e.g.,][]{nyhan2010corrections,garrett2013undermining}.
 
@@
 How such structural features affect the overall diffusion dynamics empirically?
-This is indeed important questions to ask, yet it is surprisingly difficult to establish convincing evidence of the impact of such factors in complex contagion dynamics using purely observational and experimental approaches.
+This is indeed important questions to ask, yet it is surprisingly difficult to establish convincing evidence of the impact of such factors using purely observational and experimental approaches.
 
-    A frequent and recurring theme for an attitudinal makeup of citizens' social networks and its consequences, especially among general publics, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulate themselves from competing viewpoints and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, del2016spreading}.
+    A frequent and recurring theme for an attitudinal makeup of citizens' social networks and their consequences, especially among general publics, is that most of the citizens today are put into a \enquote{echo chamber} or a \enquote{filter bubble} that insulates themselves from competing perspectives and attitude-discrepant information \parencite[e.g.,][]{lewandowsky2017beyond, del2016spreading}.
 Yet, as \citeauthor{Garrett2017distraction} (\citeyear{Garrett2017distraction}) puts it, \enquote{there is ample evidence that \emph{exposure} [emphasis added] echo chambers are not a typical part of Internet users' experience} (p.
@@
 
-    However, one should also bear in mind that the evidence concerning \emph{exposure} to counter-attitudinal messages does not provide sufficient evidence of how such messages are actually cognitively processed and interpreted under such a situation \parencites[e.g., see "engagement echo chamber" discussion in][]{Garrett2017distraction}[also, see][]{nyhan2017taking}.
+    However, one should also bear in mind that the evidence concerning \emph{exposure} to counter-attitudinal messages does not provide sufficient evidence of how such messages are actually cognitively processed and interpreted under such a situation \parencites[e.g., see ``engagement echo chamber'' discussion in][]{Garrett2017distraction}[also see][]{nyhan2017taking}.
 What we know about citizens' exposure to disagreement in their social networks typically has relied on observational evidence, either based on participants' self-reports of their patterns of social interactions concerning their immediate social environment \parencite{huckfeldt2004disagreement} or based on a comprehensive mapping of their interactions in a well-defined, relatively closed social system \parencite[e.g.,][]{song2015uncovering, lazer2010coevolution}.
 Sometimes, scholars also rely on digitally available communication patterns such as messages posted in online social networks \parencite[e.g.,][]{margolin2017}, along with engagement indicators such as \enquote{likes} or \enquote{shares} \parencite[e.g.,][]{Bakshy1130} or based on a detailed digital footprint data such as website access data \parencite[e.g.,][]{guess2018selective}.
-While such evidence \emph{do} suggests that citizens are indeed frequently exposed to competing political perspectives in their daily lives, such evidence is typically rather silent about how individuals actually process and interpret such information given exposure.
-As experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility of more balanced judgments.
-Experimental evidence in this regard can provide more detailed pictures of how such (counter-attitudinal) messages are actually selected, processed, and adopted by an individual given exposure settings \parencite[e.g., ][]{messing2014selective, nyhan2017taking, Wood2018}.
+While such evidences \emph{do} suggest that citizens are indeed frequently exposed to competing political perspectives in their daily lives, they are typically rather silent about how individuals actually process and interpret such information given exposure.
+As the experimental evidence to date suggests, the mere presence of ideologically diverse \emph{exposure} does not automatically translate into the possibility of a more balanced judgment.
+Experimental evidence in this regard can provide more detailed pictures of how such (counter-attitudinal) messages are actually selected, processed, and adopted by an individual given certain exposure settings \parencite[e.g., ][]{messing2014selective, nyhan2017taking, Wood2018}.
 Yet as previously suggested, a typical experimental approach tends to be misspecified in terms of crucial social dynamics surrounding simple vs.
 complex contagion of misinformation and correction messages within a naturally-occurring social network \parencite{margolin2017, Centola2010Sience}.
-Moreover, designing a realistic experiment involving real-world social interactions often involves significant practical \parencite[e.g.,][]{bond_61million} and ethical challenges \parencite[e.g.,][]{Kramer8788} for researchers.
+Moreover, designing a realistic yet rigorous experiment involving real-world social interactions often involves significant practical \parencite[e.g.,][]{bond_61million} and ethical challenges \parencite[e.g.,][]{Kramer8788} for researchers.
 
@@
 This is due to the fact that a small minority of \enquote{hub} nodes posses a disproportionate number of links, providing a global bridge between smaller, more strongly interconnected local clusters \parencite{barabasi2004linked}.
-This structure has traditionally been known for information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal account of strength of weak ties.
-However, emerging evidence suggests that such a small-world structure may hinder a given diffusion process to globally saturate the network, since such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{gonzalez2017decoding, centola2007complex, zhao2010weak}.
-Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor complex contagion to be globally propagated into a given network.
-This is due to the fact that such hubs require a much higher number of active neighbors to meet the threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt such  innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449, zhao2010weak, gonzalez2017decoding}.
+This structure has traditionally been known for its affinity of information to be spread globally through such hubs \parencite[e.g.,][]{Bakshy_2012}, following \citeauthor{granovetter1977strength}'s (\citeyear{granovetter1977strength}) seminal discussion of strength of weak ties.
+However, emerging evidence suggests that such a small-world structure may hinder a given diffusion to globally saturate the network; such hubs can serve as a \enquote{bottleneck} of a contagion process, therefore diffusions are stay localized and compartmentalized \parencite[e.g.,][]{gonzalez2017decoding, centola2007complex, zhao2010weak}.
+Similarly, while the existence of tightly-knit neighborhoods in a typical small-world network supports a complex-type behavioral propagation \parencite[i.e., an innovation that runs counter to prevalent norms and values:][]{Centola2010Sience}, the existence of hubs may not favor a complex contagion-type innovation to be globally propagated into a given network.
+This is due to the fact that such hubs require a much more number of active neighbors to meet a threshold of adopting a controversial innovation (i.e., complex contagions), and even if such hubs are activated, they alone cannot further activate their immediate neighbors to adopt innovations in the absence of other local nodes that provide multiple independent reinforcements \parencite{Centola2007449, zhao2010weak, gonzalez2017decoding}.
 
-    Therefore, whether topological properties of a given network actually hinder or facilitate a contagion process may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}, which is often hard to be tractable empirically.
+    Consequently, the question of whether topological properties of a given network actually hinder or facilitate a contagion process is often hard to be tractable empirically since it may critically dependent upon specific thresholds values for complex contagions and its interaction with the structure of network \parencite[e.g.,][]{Centola2007449}.
 Moreover, especially for the case of misinformation and its corrections, a simple contagion and a complex contagion may simultaneously affect a local-level attitudinal composition of one's neighbors \parencite[i.e., those who endorse and believe misinformation vs.
@@
 Doing so further requires (a) the ability to compared different thresholds values for complex contagions, and (b) the ability to independently manipulate topological structures of a social network \parencite[e.g.,][]{Centola2010Sience, gonzalez2017decoding}.
-For this reason, a rigorous empirical test of such factors is often impossible for observational studies despite its scientific and practical importance.
+For this reason, a rigorous empirical test of such factors is often seen impossible for observational studies despite its scientific and practical importance.
 
@@
 
-    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, zhao2010weak}.
+    Utilizing simulation-based approaches in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, zhao2010weak}.
 Yet these studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems \parencite[e.g., see][]{zhao2010weak}.
-While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure.
-Our approach was to use an exponential random graph model (ERGM) framework \parencite{robins2007introduction, morris2008specification} to simulate a series of dynamically evolving networks of different topological properties (see also below section \textit{A Stochastic Dynamic Model of Networks} for a more detail).
-The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a evolving network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}.
-In our present application, we simulated a baseline network evolution model based on available empirical evidence along with several counterfactual models that differ in their structural characteristics, and further submit them to different stochastic models of misinformation propagations vs.
+While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks upon which information and behaviors are spread conditional on network structures.
+Our approach was to use an exponential random graph model (ERGM) framework \parencite{robins2007introduction, morris2008specification} to simulate a series of dynamically evolving networks with different topological properties (see also below section \textit{A Stochastic Dynamic Model of Networks} for a more detail).
+The ERGM framework is now regarded as the most versatile yet flexible method for identifying how a given network is formed and evolves over time based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}.
+For a simulation context, it also offers a convenient yet powerful tool for independently manipulating topological structures of a evolving network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}.
+In our present application, we simulated a baseline network evolution model based on available empirical evidence along with several counterfactual models that differ in their structural characteristics, and submit them further to different stochastic models of misinformation propagations vs.
 corrective message adoptions.
 Our focus here is therefore on the role of varying network topologies and resulting level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs.
-complex contagion dynamics at population level in conjunction with network topologies.
+complex contagion dynamics at population level.
 
-    Therefore, our approach differs from prior studies that have used similar simulation-based approaches in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our model by supplying more realistic parameter values, where available, based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
+    Therefore, our approach differs from prior studies that have used similar simulation-based approaches in three critical aspects: (a) instead of relying on purely hypothetical scenarios and parameter values, we augment our models by supplying more realistic parameter values, where available, based on existing empirical evidence; (b) our model explicitly takes into account the stochastic nature of network evolution and its endogenous influence over time; and finally, (c) we explicitly model how attitudinal compositions of one's immediate neighbors and local-level contagion dynamics (i.e., simple vs.
 complex contagions) interact to yield propagation dynamics at the population level.
@@
 To this end, we first model formation and dissolution of citizens' political discussion ties over time through which misinformation and corrections are communicated.
-Using separable temporal ERGMs \parencite{krivitsky2017inference}, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of \enquote{summary statistics} drawn from egocentric network from 2009 ANES data.\footnote{  Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties.
-See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or \emph{summary target statistics}, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{\label{note6} In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
+Using separable temporal ERGMs \parencite{krivitsky2017inference}, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of \enquote{summary statistics} drawn from egocentric network data from 2009 ANES panel.\footnote{  Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties.
+See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or \emph{summary target statistics}, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who possess multiple contacts (i.e., degree distributions).\footnote{\label{note6}  In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents.
 Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners.
-Since in 2009 ANES respondents theoretically name up to three alters, this translate into egonetwork density of 0.66 (=1.975/3).
+Since in 2009 ANES respondents theoretically name up to three alters, this translate into egocentric network density of 0.66 (=1.975/3).
 For the main effect of partisanship, the marginal distribution of number of named alters by egos did not differ by partisanship, meaning that the expected mean degree for each partisan group is proportional to observed density and the size of each group.
@@
 For degree distribution statistic, we supply a range of plausible yet arbitrary values since 2009 ANES does not have summary network size measure.
-See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans, that closely approximate the properties of social networks documented in ANES data.
+See supplemental appendix for a detail.}
+    Based on those information, we establish our (a) baseline small-world with political homophily network model, consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans, that closely approximate the properties of social networks documented in ANES data.
 In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks.
-We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective \enquote{unfriending}:][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties.
-    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several competing models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{ This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model.
+We also specify a differential relationship dissolution model conditional on partisan homophily of a tie \parencite[e.g., selective \enquote{unfriending}:][]{noel2011unfriending, yang2017politics}, such that any co-partisan discussion tie is expected to last longer approximately twice than a cross-partisan discussion tie.
+    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several competing specifications of network structures: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{  This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model.
 Below Figure \ref{fig:Figure1} shows the simulated cross-sectional views of networks, and Table \ref{tab:Table1} reports key descriptive statistics for each of the simulated networks from each network evolution model specification in terms of their topological properties.
@@
   Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models.
-We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations.
-We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.
+We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per scenario.
+We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on adoption of corrective messages from their peers following complex contagion logics.
 
@@
 
-    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public.
+    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet well known to public.
 However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times on average, and among them 41.8\% of all visits originate from social media traffics.
@@
 presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}.
-Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being merely exposed to do not contribute to misinformation flow and propagation (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
+Here, we assume misinformation ``always'' flows from the \enquote{infected} (i.e., those who believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed), but those who are being merely exposed do not contribute to misinformation flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.
 
@@
 Combining those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs stochastically.
-In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (=.04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S.
+In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (= .04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S.
 presidential election were overwhelmingly pro-Republican).
@@
     \centering
-        \includegraphics[clip, width=\linewidth]{draft/Fig4.pdf}
+        \includegraphics[clip, width=\linewidth]{draft/Fig4.eps}
 
@@
     \caption*{Note: Y-axis denotes Proportions of Infections being Averted (PIA) relative to the no-recovery scenarios.
-We present overall (=green boxplots), among Democrats (=orange boxplots) and among Republicans (=blue boxplots) PIA estimates.}
+We present overall (= green boxplots), among Democrats (= blue boxplots) and among Republicans (= red boxplots) PIA estimates.}
 \end{sidewaysfigure}
@@
     \centering
-        \includegraphics[clip, width=0.9\linewidth, height=0.55\textwidth]{draft/Fig5.pdf}
+        \includegraphics[clip, width=0.9\linewidth, height=0.55\textwidth]{draft/Fig5.eps}
 
@@
     \caption*{Note: Y-axis denotes Proportions of Infections being Averted (PIA) relative to the no-recovery scenarios.
-We present different PIA values per each recovery scenario assuming probabilities of alters sending correction messages to infected ego equal to 0.25 (= red boxplots), 0.5 (= green boxplots) and 0.75 (=blue boxplots).
-Main results reported in \ref{fig:Figure4} assumed probability of alter sending corrections to be 0.5 (= green boxplots).}
+We present different PIA values per each recovery scenario assuming probabilities of alters sending correction messages to infected ego equal to 0.25 (= light gray boxplots), 0.5 (= gray boxplots) and 0.75 (= dark gray boxplots).
+Main results reported in \ref{fig:Figure4} assumed probability of alter sending corrections to be 0.5 (= gray boxplots).}
 \end{sidewaysfigure}
 
-\section{Discussion}
-  TBA
+\section{Discussion and Conclusion}
+  Within the context of a misinformation propagation and the adoption of correction messages in social networks, the present study attempted to examine system-level consequences of simple vs.
+complex contagion dynamics, focusing on the differences between a simple contagion of misinformation and a complex contagion of fact-checking and corrective messages.
+We further explore boundary conditions that may affect such complex contagion dynamics, focusing different threshold values of adopting corrective messages and its consequences of misinformation propagation at system level outcomes.
+Utilizing ABM simulations with stochastic network evolution models, this study further highlights the utility of computational social science approaches in robustly exploring various theoretical conditions that otherwise empirically intractable, overcoming the limitations of typical experimental and observations studies concerning complex social phenomena.
+
+\subsection{Limitations}
+  Before discussing possible implications of our findings, few limitations should be acknowledged.
+First, due to limitations of available data, our results are bounded by few pure hypothetical (yet still plausible) parameter specifications assumed in simulations, although where available, we have augmented our several key parameter specifications with best-available empirical evidence to date.
+While more thorough empirical investigation on this topic may further illuminate many aspects of misinformation propagation, our thought-experiment using agent-based simulation further clarifies potential blind spots that need of further research on this topic.
+Relatedly, our current specifications of simple vs.
+complex contagion dynamics do not consider how individuals actually process such messages (as would be in controlled experiments) due to much abstract nature of mathematical simulations.
+
+    Second, it should be acknowledged that during our simulations, we treated individuals social network ``links'' as a relatively stable conduit in which specific misinformations and corrections are communicated.
+Due to such conceptualization, we did not consider the possibility that individuals may end up terminate ties due to misinformation and correction itself -- what we would call ``unfriending'' \parencite{yang2017politics, noel2011unfriending} -- but only considered the possibility of tie dissolution based on more general partisanship (e.g., ties between democrats and republicans are less durable than ties between copartisans).
+Although such politically motivated, misinformation-based unfriending is somewhat likely, we do not know much about such phenomena in question, let alone its prevalence and mechanisms that enable us to consider such factors in our simulation specifications.
+
+    Lastly, the generalizability of these models is partially subject to the underlying behavioral data sources (i.e., 2009 ANES) upon which the baseline models were calibrated.
+In particular, the level of partisan homogeneity, one of the key theoretical factor of which influence population-level propagation dynamics both in a simple contagion of misinformation and a complex contagion of correction messages, might have been pan out differently had we been able to use a large-scale online social network data that is specifically designed to assess the impact of contagion dynamics concerning misinformation and its correction.
+While recent contributions on this topic increasingly attempt to directly utilize a large-scale online network data in this regard \parencite[e.g.,][]{Bakshy_2012, del2016spreading}, they typically do not observe propagation of misinformation directly.
+Such data, typically from Twitter retweet relations or from Facebook Graph API, only provide information between visibly connected dyads (i.e., post-reply relations between actors i and j).
+Thus, exposure to a message is observed only when actor i ``replies'' or ``follows'' \emph{after} reading actor j’s message.
+In contrast, unobtrusively tracked behavioral data regarding one's ``exposure'' to specific misinformation (or its correction) is often not available to researchers due to proprietary nature of such data, let alone obtaining such data involves many ethical concerns for researchers \parencite[e.g.,][]{Kramer8788}.
+
+\subsection{Implications}
+     Overall, our simulation results confirm our initial expectation that socially-contingent corrections are substantially more, if not equally, effective in preventing a given misinformation to further propagate into public.
+Following discussions of complex and ``contested'' contagion dynamics \parencite{centola2007complex, Centola2010Sience, Centola2007449, gonzalez2017decoding}, we argued that individuals are more likely to accept socially-provided correction messages \parencite[e.g.,][]{margolin2017, bode2017see}, and as a consequence, social correction scenarios would be more effective than a single-shot, asocial correction that typically have been considered in extant literature.
+Although in a realistically defined, baseline network misinformation appear to be spread more faster than pure random networks or than non-homophilic network (Figure \ref{fig:Figure2}), once corrections are introduced into the network, the baseline topology was indeed capable of deterring the spread of misinformation more effectively (measured by proportions of infections being averted) than any other counterfactual network topologies (Figure \ref{fig:Figure4}).
+This appears due to the fact that socially-contingent correction dynamics are more effective in preventing a small number of existing misinformation infection at the earlier stage of the misinformation propagation.
+
+    Our results also reveal that currently specified social correction models are relatively robust against potential variations in specific threshold values of adopting complex (contested) contagions (0.25 vs.
+0.5 vs.
+0.75) and probabilities of one's alters actually sending corrections to infected individuals (again, 0.25 vs.
+0.5 vs.
+0.75: see our results in ``Sensitivity Analysis'', Figure \ref{fig:Figure5}).
+We observed that largely equivalent proportions of infections being averted due to corrections even in models with relatively high-adoption thresholds coupled with low probability of alters sending actual corrections to an infected ego.
+This may further be seen as implying that the social cost of sending corrective messages to one's peers play a rather limited role in complex contagion dynamics at least in the current framework.
+Yet considering the fact that friend-friend corrections may entail certain relational costs when in comes to sending (misinformation) correction messages -- such as topic avoidance \parencite{morey2012matters} or even political unfriending \parencite{yang2017politics, noel2011unfriending}, these findings does not necessarily imply the unimportance of social costs of sending corrections and how frequent such corrections are received by misinformed individuals.
+Quite contrary, our results imply \emph{as long as individuals keep maintain} some degree of attitudinally diverse social connections, the effectiveness of socially-contingent corrections would remain robust to such factors.
+
+    Now there are good reasons to believe that individuals do not selectively construct their political environments simply based on their partisan similarity \parencite{morey2012matters, lazer2010coevolution, song2015uncovering}.
+Even in online settings one may be exposed to nontrivial degree of counter-attitudinal information \parencite[e.g.,][]{Bakshy_2012, messing2014selective}.
+Under such conditions, the social network relations -- as opposed to asocial corrections from strangers -- may stimulate more effective individual- and population-level outcomes of fact-checking messages \parencite[e.g.,][]{margolin2017, bode2017see}.
+Yet at the same time, these findings might be unexpected if individuals indeed form their social relations purposively through their political and ideological similarities, therefore limiting the possibility of receiving independent, multiple reinforcements of corrective messages targeting misinformation.
+While a real-world replication with much more detailed data, beyond this particular simulation context, would provide firm evidence on the generalizability of our findings, it is our hope that the current investigation would illuminate further scholarly effort of investigating when and how corrections to misinformations can contribute to the ideals of informed citizenly.
 

### 2018-05-02 EpiModel.R

@@ -825,7 +825,7 @@ for (i in 1:16) {
 }
 
 fig4.dat <- melt(out.overall)
-fig4.dat$type <- "overall"
+fig4.dat$type <- "Overall"
 colnames(fig4.dat) <- c("sim", "Model", "PIA", "type")
 
 fig4.dat <- rbind(fig4.dat, data.frame(
@@ -843,9 +843,13 @@ fig4.dat <- rbind(fig4.dat, data.frame(
 ))
 
 setDT(fig4.dat)
+fig4.dat$Model <- paste0("Model", fig4.dat$Model)
+fig4.dat$Model <- factor(fig4.dat$Model, levels = mixedsort(unique(fig4.dat$Model)))
+
 ## In E-R network
 p4_1 <- ggplot(fig4.dat[Model %in% c("Model1", "Model2", "Model3", "Model4"), ],
                aes(x = Model, y = PIA, fill = factor(type))) + geom_boxplot() + ## across all simulations, plot medians
+  scale_fill_manual(values = c("#619CFF", "#00BA38", "#F8766D")) +
   xlab("") + ylab("Proportion Infections Averted") +
   theme_bw() + scale_x_discrete(labels = c("Model1" = "Model 1 \n(Asocial)",
                                            "Model2" = "Model 2 \n(Thresholds = 0.25)",
@@ -859,6 +863,7 @@ p4_1 <- ggplot(fig4.dat[Model %in% c("Model1", "Model2", "Model3", "Model4"), ],
 ## in Chain network
 p4_2 <- ggplot(fig4.dat[Model %in% c("Model5", "Model6", "Model7", "Model8"), ],
                aes(x = Model, y = PIA, fill = factor(type))) + geom_boxplot() + ## across all simulations, plot medians
+  scale_fill_manual(values = c("#619CFF", "#00BA38", "#F8766D")) +
   xlab("") + ylab("Proportion Infections Averted") +
   theme_bw() + scale_x_discrete(labels = c("Model5" = "Model 5 \n(Asocial)",
                                            "Model6" = "Model 6 \n(Thresholds = 0.25)",
@@ -873,6 +878,7 @@ p4_2 <- ggplot(fig4.dat[Model %in% c("Model5", "Model6", "Model7", "Model8"), ],
 ## in SW Network without homophily
 p4_3 <- ggplot(fig4.dat[Model %in% c("Model9", "Model10", "Model11", "Model12"), ],
[…]
